### 2018-11-08 Paper1.tex
Initial ShareLaTeX Import

%%
%% Beginning of file 'sample62.tex'
%%
%% Modified 2018 January
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.2 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
%% All of these external packages should already be present in the modern TeX 
%% distributions.  If not they can also be obtained at www.ctan.org.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass{aastex62}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figures/}}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{January 1, 2018}
\revised{January 7, 2018}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

%% Mark up commands to limit the number of authors on the front page.
%% Note that in AASTeX v6.2 a \collaboration call (see below) counts as
%% an author in this case.
%
%\AuthorCollaborationLimit=3
%
%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
%% collaboration" on the front page of this example manuscript.
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{Sample article}
\shortauthors{Schwarz et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{An Example Article using \aastex v6.2\footnote{Released on January, 8th, 2018}}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.2 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affilations. The change was necessary to implement 
%% autoindexing of affilations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% arguement which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.2 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.2 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

\correspondingauthor{August Muench}
\email{greg.schwarz@aas.org, gus.muench@aas.org}

\author[0000-0002-0786-7307]{Greg J. Schwarz}
\affil{American Astronomical Society \\
2000 Florida Ave., NW, Suite 300 \\
Washington, DC 20009-1231, USA}

\author{August Muench}
\affiliation{American Astronomical Society \\
2000 Florida Ave., NW, Suite 300 \\
Washington, DC 20009-1231, USA}
\collaboration{(AAS Journals Data Scientists collaboration)}

\author{Butler Burton}
\affiliation{National Radio Astronomy Observatory}
\affiliation{AAS Journals Associate Editor-in-Chief}
\nocollaboration

\author{Amy Hendrickson}
\altaffiliation{Creator of AASTeX v6.2}
\affiliation{TeXnology Inc.}
\collaboration{(LaTeX collaboration)}

\author{Julie Steffen}
\affiliation{AAS Director of Publishing}
\affiliation{American Astronomical Society \\
2000 Florida Ave., NW, Suite 300 \\
Washington, DC 20009-1231, USA}

\author{Jeff Lewandowski}
\affiliation{IOP Senior Publisher for the AAS Journals}
\affiliation{IOP Publishing, Washington, DC 20005}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.2 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}

This example manuscript is intended to serve as a tutorial and template for
authors to use when writing their own AAS Journal articles. The manuscript
includes a history of \aastex\ and documents the new features in the
previous versions as well as the new features in version 6.2. This
manuscript includes many figure and table examples to illustrate these new
features.  Information on features not explicitly mentioned in the article
can be viewed in the manuscript comments or more extensive online
documentation. Authors are welcome replace the text, tables, figures, and
bibliography with their own and submit the resulting manuscript to the AAS
Journals peer review system.  The first lesson in the tutorial is to remind
authors that the AAS Journals, the Astrophysical Journal (ApJ), the
Astrophysical Journal Letters (ApJL), and Astronomical Journal (AJ), all
have a 250 word limit for the abstract\footnote{Note that manuscripts 
submitted to the new Research Notes of the American Astronomical Society 
(RNAAS) do \textbf{not} have abstracts.}.  If you exceed this length the
Editorial office will ask you to shorten it.

\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{editorials, notices --- 
miscellaneous --- catalogs --- surveys}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.
%%
%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

\section{Introduction} \label{sec:intro}

\latex\ \footnote{\url{http://www.latex-project.org/}} is a document markup
language that is particularly well suited for the publication of
mathematical and scientific articles \citep{lamport94}. \latex\ was written
in 1985 by Leslie Lamport who based it on the \TeX\ typesetting language
which itself was created by Donald E. Knuth in 1978.  In 1988 a suite of
\latex\ macros were developed to investigate electronic submission and
publication of AAS Journal articles \citep{1989BAAS...21..780H}.  Shortly
afterwards, Chris Biemesdefer merged these macros and more into a \latex\
2.08 style file called \aastex.  These early \aastex\ versions introduced
many common commands and practices that authors take for granted today.
Substantial revisions
were made by Lee Brotzman and Pierre Landau when the package was updated to
v4.0.  AASTeX v5.0, written in 1995 by Arthur Ogawa, upgraded to \latex\ 2e
which uses the document class in lieu of a style file.  Other improvements
to version 5 included hypertext support, landscape deluxetables and
improved figure support to facilitate electronic submission.  
\aastex\ v5.2 was released in 2005 and introduced additional graphics
support plus new mark up to identifier astronomical objects, datasets and
facilities.

In 1996 Maxim Markevitch modified the AAS preprint style file, aaspp4.sty,
to closely emulate the very tight, two column style of a typeset
Astrophysical Journal article.  The result was emulateapj.sty.  A year
later Alexey Vikhlinin took over development and maintenance.  In 2001 he
converted emulateapj into a class file in \latex\ 2e and in 2003 Vikhlinin
completely rewrote emulateapj based on the APS Journal's RevTEX class.

During this time emulateapj gained growing acceptance in the astronomical
community as it filled an author need to obtain an approximate number of
manuscript pages prior to submission for cost and length estimates. The
tighter typeset also had the added advantage of saving paper when printing
out hard copies.

Even though author publication charges are no longer based on print pages
\footnote{see Section \ref{sec:pubcharge} in the Appendix for more details
about how current article costs are calculated.} the emulateapj class file
has proven to be extremely popular with AAS Journal authors.  An informal
analysis of submitted \latex\ manuscripts in 2015 revealed that $\sim$65\%
either called emulateapj or have a commented emulateapj classfile call
indicating it was used at some stage of the manuscript construction.
Clearly authors want to have access to a tightly typeset version of the
article when corresponding with co-authors and for preprint submissions.

When planning the next \aastex\ release the popularity of emulateapj played
an important roll in the decision to drop the old base code and adopt and
modify emulateapj for \aastex\ v6.+ instead.  The change brings \aastex\
inline with what the majority of authors are already using while still
delivering new and improved features.  \aastex\ v6.0 through v6.2 were written
by Amy Hendrickson and released in January 2016 (v6.0), October 2016 (v6.1),
and January 2018 (v6.2), respectively.  Some of the new features in v6.0 
included:

\begin{enumerate}
\item improved citations for third party data repositories and software,
\item easier construction of matrix figures consisting of multiple 
encapsulated postscript (EPS) or portable document format (PDF) files,
\item figure set mark up for large collections of similar figures,
\item color mark up to easily enable/disable revised text highlighting,
\item improved url support, and
\item numerous table options such as the ability to hide columns, column 
decimal alignment, automatic column math mode and numbering, plus splitting of
wide tables.
\end{enumerate}

The features in v6.1 were:

\begin{enumerate}
\item ORCID support for preprints,
\item improved author, affiliation and collaboration mark up,
\item reintroduced the old AASTeX v5.2 {\tt\string\received}, 
      {\tt\string\revised}, {\tt\string\accepted}, and
      {\tt\string\published} commands plus
      added the new {\tt\string\submitjournal} command to document
      which AAS Journal the manuscript was submitted to, plus
\item new typeset style options.
\end{enumerate}

The new features in v6.2 are:

\begin{enumerate}
\item A new RNAAS style option for Research Note manuscripts,
\item Titles no longer put in all caps,
\item No page skip between the title page and article body,
\item re-introduce RevTeX's widetext environment for long lines in
      two column style formats, and
\item upgrade to the {\tt\string\doi} command.
\end{enumerate}

The rest of this article provides information and examples on how to create
your own AAS Journal manuscript with v6.2.  Special emphasis is placed on
how to use the full potential of \aastex\ v6+.  The next section describes
the different manuscript styles available and how they differ from past
releases.  Section \ref{sec:floats} describes how tables and figures are
placed in a \latex\ document. Specific examples of tables, Section
\ref{subsec:tables}, and figures, Section \ref{subsec:figures}, are also
provided.  Section \ref{sec:displaymath} discusses how to display math and
incorporate equations in a manuscript while Section \ref{sec:highlight}
discuss how to use the new revision mark up.  The last section,
\ref{sec:cite}, shows how recognize software and external data as first
class references in the manuscript bibliography.  An appendix is included
to show how to construct one and provide some information on how article
charges are calculated.  Additional information is available both embedded
in the comments of this \latex\ file and in the online documentation at
\url{http://journals.aas.org/authors/aastex.html}.

\section{Manuscript styles} \label{sec:style}

The default style in \aastex\ v6.2 is a tight single column style, e.g.  10
point font, single spaced.  The single column style is very useful for
article with wide equations. It is also the easiest to style to work with
since figures and tables, see Section \ref{sec:floats}, will span the
entire page, reducing the need for address float sizing.

To invoke a two column style similar to the what is produced in
the published PDF copy use \\

\noindent {\tt\string\documentclass[twocolumn]\{aastex62\}}. \\

\noindent Note that in the two column style figures and tables will only
span one column unless specifically ordered across both with the ``*'' flag,
e.g. \\

\noindent{\tt\string\begin\{figure*\}} ... {\tt\string\end\{figure*\}}, \\
\noindent{\tt\string\begin\{table*\}} ... {\tt\string\end\{table*\}}, and \\
\noindent{\tt\string\begin\{deluxetable*\}} ... {\tt\string\end\{deluxetable*\}}. \\

\noindent This option is ignored in the onecolumn style.

Some other style options are outlined in the commented sections of this 
article.  Any combination of style options can be used.

Two style options that are needed to fully use the new revision tracking
feature, see Section \ref{sec:highlight}, are {\tt\string linenumbers} which 
uses the lineno style file to number each article line in the left margin and 
{\tt\string trackchanges} which controls the revision and commenting highlight
output.

There is also a new {\tt\string modern} option that uses a Daniel
Foreman-Mackey and David Hogg design to produce stylish, single column
output that has wider left and right margins. It is designed to have fewer
words per line to improve reader retention. It also looks better on devices
with smaller displays such as smart phones.

For a Research Note use the {\tt\string RNAAS} option which will produce a
manuscript with no abstract and in the {\tt\string modern} style.

\section{Floats} \label{sec:floats}

Floats are non-text items that generally can not be split over a page.
They also have captions and can be numbered for reference.  Primarily these
are figures and tables but authors can define their own. \latex\ tries to
place a float where indicated in the manuscript but will move it later if
there is not enough room at that location, hence the term ``float''.

Authors are encouraged to embed their tables and figures within the text as
they are mentioned.  Please do not place the figures and text at the end of
the article as was the old practice.  Editors and the vast majority of
referees find it much easier to read a manuscript with embedded figures and
tables.

Depending on the number of floats and the particular amount of text and
equations present in a manuscript the ultimate location of any specific
float can be hard to predict prior to compilation. It is recommended that
authors textbf{not} spend significant time trying to get float placement
perfect for peer review.  The AAS Journal's publisher has sophisticated
typesetting software that will produce the optimal layout during
production.

Note that authors of Research Notes are only allowed one float, either one
table or one figure.

\startlongtable
\begin{deluxetable}{c|cc}
\tablecaption{ApJ costs from 1991 to 2013\tablenotemark{a} \label{tab:table}}
\tablehead{
\colhead{Year} & \colhead{Subscription} & \colhead{Publication} \\
\colhead{} & \colhead{cost} & \colhead{charges\tablenotemark{b}}\\
\colhead{} & \colhead{(\$)} & \colhead{(\$/page)}
}
\colnumbers
\startdata
1991 & 600 & 100 \\
1992 & 650 & 105 \\
1993 & 550 & 103 \\
1994 & 450 & 110 \\
1995 & 410 & 112 \\
1996 & 400 & 114 \\
1997 & 525 & 115 \\
1998 & 590 & 116 \\
1999 & 575 & 115 \\
2000 & 450 & 103 \\
2001 & 490 &  90 \\
2002 & 500 &  88 \\
2003 & 450 &  90 \\
2004 & 460 &  88 \\
2005 & 440 &  79 \\
2006 & 350 &  77 \\
2007 & 325 &  70 \\
2008 & 320 &  65 \\
2009 & 190 &  68 \\
2010 & 280 &  70 \\
2011 & 275 &  68 \\
2012 & 150 &  56 \\
2013 & 140 &  55 \\
\enddata
\tablenotetext{a}{Adjusted for inflation}
\tablenotetext{b}{Accounts for the change from page charges to digital quanta in April, 2011}
\tablecomments{Note that {\tt \string \colnumbers} does not work with the 
vertical line alignment token. If you want vertical lines in the headers you
can not use this command at this time.}
\end{deluxetable}

For authors that do want to take the time to optimize the locations of
their floats there are some techniques that can be used.  The simplest
solution is to placing a float earlier in the text to get the position
right but this option will break down if the manuscript is altered, see
Table \ref{tab:table}.  A better method is to force \latex\ to place a
float in a general area with the use of the optional {\tt\string [placement
specifier]} parameter for figures and tables. This parameter goes after
{\tt\string \begin\{figure\}}, {\tt\string \begin\{table\}}, and
{\tt\string \begin\{deluxetable\}}.  The main arguments the specifier takes
are ``h'', ``t'', ``b'', and ``!''.  These tell \latex\ to place the float
\underline{h}ere (or as close as possible to this location as possible), at
the \underline{t}op of the page, and at the \underline{b}ottom of the page.
The last argument, ``!'', tells \latex\ to override its internal method of
calculating the float position.  A sequence of rules can be created by
using multiple arguments.  For example, {\tt\string \begin\{figure\}[htb!]}
tells \latex\ to try the current location first, then the top of the page
and finally the bottom of the page without regard to what it thinks the
proper position should be.  Many of the tables and figures in this article
use a placement specifier to set their positions.

Note that the \latex\ {\tt\string tabular} environment is not a float.  Only
when a {\tt\string tabular} is surrounded by {\tt\string\begin\{table\}} ...
{\tt\string\end\{table\}} is it a true float and the rules and suggestions
above apply.

In AASTeX v6.2 all deluxetables are float tables and thus if they are
longer than a page will spill off the bottom. Long deluxetables should
begin with the {\tt\string\startlongtable} command. This initiates a
longtable environment.  Authors might have to use {\tt\string\clearpage} to
isolate a long table or optimally place it within the surrounding text.

\begin{deluxetable*}{ccCrlc}[b!]
\tablecaption{Column math mode in an observation log \label{tab:mathmode}}
\tablecolumns{6}
\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{UT start time\tablenotemark{a}} &
\colhead{MJD start time\tablenotemark{a}} &
\colhead{Seeing} & \colhead{Filter} & \colhead{Inst.} \\
\colhead{(YYYY-mm-dd)} & \colhead{(d)} &
\colhead{(arcsec)} & \colhead{} & \colhead{}
}
\startdata
2012-03-26 & 56012.997 & \sim 0.\arcsec5 & H$\alpha$ & NOT \\
2012-03-27 & 56013.944 & 1.\arcsec5 & grism & SMARTS \\
2012-03-28 & 56014.984 & \nodata & F814M & HST \\
2012-03-30 & 56016.978 & 1.\arcsec5\pm0.25 & B\&C & Bok \\
\enddata
\tablenotetext{a}{At exposure start.}
\tablecomments{The ``C'' command column identifier in the 3 column turns on
math mode for that specific column. One could do the same for the next
column so that dollar signs would not be needed for H$\alpha$
but then all the other text would also be in math mode and thus typeset
in Latin Modern math and you will need to put it back to Roman by hand.
Note that if you do change this column to math mode the dollar signs already
present will not cause a problem. Table \ref{tab:mathmode} is published 
in its entirety in the machine readable format.  A portion is
shown here for guidance regarding its form and content.}
\end{deluxetable*}

\subsection{Tables} \label{subsec:tables}

Tables can be constructed with \latex's standard table environment or the
\aastex's deluxetable environment. The deluxetable construct handles long
tables better but has a larger overhead due to the greater amount of
defined mark up used set up and manipulate the table structure.  The choice
of which to use is up to the author.  Examples of both environments are
used in this manuscript. Table \ref{tab:table} is a simple deluxetable
example that gives the approximate changes in the subscription costs and
author publication charges from 1991 to 2013.

Tables longer than 200 data lines and complex tables should only have a
short example table with the full data set available in the machine
readable format.  The machine readable table will be available in the HTML
version of the article with just a short example in the PDF. Authors are
required to indicate to the reader where the data can be obtained in the
table comments.  Suggested text is given in the comments of Table
\ref{tab:mathmode}.  Authors are encouraged to create their own machine
readable tables using the online tool at
\url{http://authortools.aas.org/MRT/upload.html}.

\aastex\ v6 introduces five new table features that are designed to make
table construction easier and the resulting display better for AAS Journal
authors.  The items are:

\begin{enumerate}
\item Declaring math mode in specific columns,
\item Column decimal alignment, 
\item Automatic column header numbering,
\item Hiding columns, and
\item Splitting wide tables into two or three parts.
\end{enumerate}

Each of these new features are illustrated in following Table examples.
All five features work with the regular \latex\ tabular environment and in
\aastex's deluxetable environment.  The examples in this manuscript also
show where the two process differ.

\subsubsection{Column math mode}

Both the \latex\ tabular and \aastex\ deluxetable require an argument to
define the alignment and number of columns.  The most common values are
``c'', ``l'' and ``r'' for \underline{c}enter, \underline{l}eft, and
\underline{r}ight justification.  If these values are capitalized, e.g.
``C'', ``L'', or ``R'', then that specific column will automatically be in math
mode meaning that \$s are not required.  Note that having embedded dollar
signs in the table does not affect the output.  The third and forth columns
of Table \ref{tab:mathmode} shows how this math mode works.

\subsubsection{Decimal alignment}

Aligning a column by the decimal point can be difficult with only center,
left, and right justification options.  It is possible to use phantom calls
in the data, e.g. {\tt\string\phn}, to align columns by hand but this can
be tedious in long or complex tables.  To address this \aastex\ introduces
the {\tt\string\decimals} command and a new column justification option,
``D'', to align data in that column on the decimal.  In deluxetable the
{\tt\string\decimals} command is invoked before the {\tt\string\startdata}
call but can be anywhere in \latex's tabular environment.

Two other important thing to note when using decimal alignment is that each
decimal column \textit{must end with a space before the ampersand}, e.g.
``\&\&'' is not allowed.  Empty decimal columns are indicated with a decimal,
e.g. ``.''.  Do not use deluxetable's {\tt\string\nodata} command.

The ``D'' alignment token works by splitting the column into two parts on the
decimal.  While this is invisible to the user one must be aware of how it
works so that the headers are accounted for correctly.  All decimal column
headers need to span two columns to get the alignment correct. This can be
done with a multicolumn call, e.g {\tt\string\multicolumn2c\{\}} or
{\tt\string\multicolumn\{2\}\{c\}\{\}}, or use the new
{\tt\string\twocolhead\{\}} command in deluxetable.  Since \latex\ is
splitting these columns into two it is important to get the table width
right so that they appear joined on the page.  You may have to run the
\latex\ compiler twice to get it right.  Table \ref{tab:decimal}
illustrates how decimal alignment works in the tabular environment with a
$\pm$ symbol embedded between the last two columns.

%% Note that the \setcounter and \renewcommand are needed here because
%% this example is using a mix of deluxetable and tabular.  Here the
%% deluxetable counters are set with \tablenum but the situation is a bit
%% more complex for tabular.  Use the first command to set the Table number
%% to ONE LESS than it should be.  The next command will auto increment it
%% to the desired number.
\setcounter{table}{2}
\begin{table}[h!]
\renewcommand{\thetable}{\arabic{table}}
\centering
\caption{Decimal alignment made easy} \label{tab:decimal}
\begin{tabular}{cD@{$\pm$}D}
\tablewidth{0pt}
\hline
\hline
Column & \multicolumn2c{Value} & \multicolumn2c{Uncertainty}\\
\hline
\decimals
A & 1234     & 100.0     \\
B &  123.4   &  10.1     \\
C &  12.34   &   1.01    \\
D &   1.234  &   0.101   \\
E &    .1234 &   0.01001 \\
F &   1.0    &    .      \\
\hline
\multicolumn{5}{c}{NOTE. - Two decimal aligned columns}
\end{tabular}
\end{table}

\subsubsection{Automatic column header numbering} \label{subsubsec:autonumber}

The command {\tt\string\colnumbers} can be included to automatically number
each column as the last row in the header. Per the AAS Journal table format
standards, each column index numbers will be surrounded by parentheses. In
a \latex\ tabular environment the {\tt\string\colnumbers} should be invoked
at the location where the author wants the numbers to appear, e.g. after
the last line of specified table header rows. In deluxetable this command
has to come before {\tt\string\startdata}.  {\tt\string\colnumbers} will
not increment for columns hidden by the ``h'' command, see Section
\ref{subsubsec:hide}.  Table \ref{tab:table} uses this command to
automatically generate column index numbers.

Note that when using decimal alignment in a table the command 
{\tt\string\decimalcolnumbers} must be used instead of 
{\tt\string\colnumbers} and {\tt\string\decimals}. Table \ref{tab:messier}
illustrates this specific functionality.

\subsubsection{Hiding columns} \label{subsubsec:hide}

Entire columns can be \underline{h}idden from display simply by changing
the specified column identifier to ``h''.  In the \latex\ tabular environment
this column identifier conceals the entire column including the header
columns.   In \aastex's deluxetables the header row is specifically
declared with the {\tt\string\tablehead} call and each header column is
marked with {\tt\string\colhead} call.  In order to make a specific header
disappear with the ``h'' column identifier in deluxetable use 
{\tt\string\nocolhead} instead to suppress that particular column header.

Authors can use this option in many different ways.  Since column data can
be easily suppressed authors can include extra information and hid it
based on the comments of co-authors or referees.  For wide tables that will
have a machine readable version, authors could put all the information in
the \latex\ table but use this option to hid as many columns as needed until
it fits on a page. This concealed column table would serve as the
example table for the full machine readable version.  Regardless of how
columns are obscured, authors are responsible for removing any unneeded
column data or alerting the editorial office about how to treat these
columns during production for the final typeset article.

Table \ref{tab:messier} provides some basic information about the first ten
Messier Objects and illustrates how many of these new features can be used
together.  It has automatic column numbering, decimal alignment of the
distances, and one concealed column.  The Common name column
is the third in the \latex\ deluxetable but does not appear when the article
is compiled. This hidden column can be shown simply by changing the ``h'' in
the column identifier preamble to another valid value.  This table also
uses {\tt\string\tablenum} to renumber the table because a \latex\ tabular
table was inserted before it.

\begin{deluxetable*}{cchlDlc}
\tablenum{4}
\tablecaption{Fun facts about the first 10 messier objects\label{tab:messier}}
\tablewidth{0pt}
\tablehead{
\colhead{Messier} & \colhead{NGC/IC} & \nocolhead{Common} & \colhead{Object} &
\multicolumn2c{Distance} & \colhead{} & \colhead{V} \\
\colhead{Number} & \colhead{Number} & \nocolhead{Name} & \colhead{Type} &
\multicolumn2c{(kpc)} & \colhead{Constellation} & \colhead{(mag)}
}
\decimalcolnumbers
\startdata
M1 & NGC 1952 & Crab Nebula & Supernova remnant & 2 & Taurus & 8.4 \\
M2 & NGC 7089 & Messier 2 & Cluster, globular & 11.5 & Aquarius & 6.3 \\
M3 & NGC 5272 & Messier 3 & Cluster, globular & 10.4 & Canes Venatici &  6.2 \\
M4 & NGC 6121 & Messier 4 & Cluster, globular & 2.2 & Scorpius & 5.9 \\
M5 & NGC 5904 & Messier 5 & Cluster, globular & 24.5 & Serpens & 5.9 \\
M6 & NGC 6405 & Butterfly Cluster & Cluster, open & 0.31 & Scorpius & 4.2 \\
M7 & NGC 6475 & Ptolemy Cluster & Cluster, open & 0.3 & Scorpius & 3.3 \\
M8 & NGC 6523 & Lagoon Nebula & Nebula with cluster & 1.25 & Sagittarius & 6.0 \\
M9 & NGC 6333 & Messier 9 & Cluster, globular & 7.91 & Ophiuchus & 8.4 \\
M10 & NGC 6254 & Messier 10 & Cluster, globular & 4.42 & Ophiuchus & 6.4 \\
\enddata
\tablecomments{This table ``hides'' the third column in the \latex\ when compiled.
The Distance is also centered on the decimals.  Note that when using decimal
alignment you need to include the {\tt\string\decimals} command before
{\tt\string\startdata} and all of the values in that column have to have a
space before the next ampersand.}
\end{deluxetable*}

\subsubsection{Splitting a table into multiple horizontal components}

Since the AAS Journals are now all electronic with no print version there is
no reason why tables can not be as wide as authors need them to be.
However, there are some artificial limitations based on the width of a
print page.  The old way around this limitation was to rotate into 
landscape mode and use the smallest available table font
sizes, e.g. {\tt\string\tablewidth}, to get the table to fit.
Unfortunately, this was not alway enough but now along with the hide column
option outlined in Section \ref{subsubsec:hide} there is a new way to break
a table into two or three components so that it flows down a page by
invoking a new table type, splittabular or splitdeluxetable. Within these
tables a new ``B'' column separator is introduced.  Much like the vertical
bar option, ``$\vert$'', that produces a vertical table lines, e.g. Table
\ref{tab:table}, the new ``B'' separator indicates where to \underline{B}reak
a table.  Up to two ``B''s may be included.

Table 5 % \ref{tab:deluxesplit} this freaks it out when it is used!
shows how to split a wide deluxetable into three parts with
the {\tt\string\splitdeluxetable} command.  The {\tt\string\colnumbers}
option is on to show how the automatic column numbering carries through the
second table component, see Section \ref{subsubsec:autonumber}.

The last example, Table \ref{tab:tablesplit}, shows how to split the same
table but with a regular \latex\ tabular call and into two parts. Decimal
alignment is included in the third column and the ``Component'' column is
hidden to illustrate the new features working together.

\begin{splitdeluxetable*}{lccccBcccccBcccc}
\tabletypesize{\scriptsize}
\tablewidth{0pt} 
\tablenum{5}
\tablecaption{Measurements of Emission Lines: two breaks \label{tab:deluxesplit}}
\tablehead{
\colhead{Model} & \colhead{Component}& \colhead{Shift} & \colhead{FWHM} &
\multicolumn{10}{c}{Flux} \\
\colhead{} & \colhead{} & \colhead{($\rm
km~s^{-1}$)}& \colhead{($\rm km~s^{-1}$)} & \multicolumn{10}{c}{($\rm
10^{-17}~erg~s^{-1}~cm^{-2}$)} \\
\cline{5-14}
\colhead{} & \colhead{} &
\colhead{} & \colhead{} & \colhead{Ly$\alpha$} & \colhead{N\,{\footnotesize
V}} & \colhead{Si\,{\footnotesize IV}} & \colhead{C\,{\footnotesize IV}} &
\colhead{Mg\,{\footnotesize II}} & \colhead{H$\gamma$} & \colhead{H$\beta$}
& \colhead{H$\alpha$} & \colhead{He\,{\footnotesize I}} &
\colhead{Pa$\gamma$}
} 
\colnumbers
\startdata 
{       }& BELs& -97.13 &    9117$\pm      38$&    1033$\pm      33$&$< 35$&$<     166$&     637$\pm      31$&    1951$\pm      26$&     991$\pm 30$&    3502$\pm      42$&   20285$\pm      80$&    2025$\pm     116$& 1289$\pm     107$\\ 
{Model 1}& IELs& -4049.123 & 1974$\pm      22$&    2495$\pm      30$&$<     42$&$<     109$&     995$\pm 186$&      83$\pm      30$&      75$\pm      23$&     130$\pm      25$& 357$\pm      94$&     194$\pm      64$& 36$\pm      23$\\
{       }& NELs& \nodata &     641$\pm       4$&     449$\pm 23$&$<      6$&$<       9$&       --            &     275$\pm      18$& 150$\pm      11$&     313$\pm      12$&     958$\pm      43$&     318$\pm 34$& 151$\pm       17$\\
\hline
{       }& BELs& -85 &    8991$\pm      41$& 988$\pm      29$&$<     24$&$<     173$&     623$\pm      28$&    1945$\pm 29$&     989$\pm      27$&    3498$\pm      37$&   20288$\pm      73$& 2047$\pm     143$& 1376$\pm     167$\\
{Model 2}& IELs& -51000 &    2025$\pm      26$& 2494$\pm      32$&$<     37$&$<     124$&    1005$\pm     190$&      72$\pm 28$&      72$\pm      21$&     113$\pm      18$&     271$\pm      85$& 205$\pm      72$& 34$\pm      21$\\
{       }& NELs& 52 &     637$\pm      10$&     477$\pm 17$&$<      4$&$<       8$&       --            &     278$\pm      17$& 153$\pm      10$&     317$\pm      15$&     969$\pm      40$&     325$\pm 37$&
     147$\pm       22$\\
\enddata
\tablecomments{This is an example of how to split a deluxetable. You can
split any table with this command into two or three parts.  The location of
the split is given by the author based on the placement of the ``B''
indicators in the column identifier preamble.  For more information please
look at the new \aastex\ instructions.}
\end{splitdeluxetable*}

%\clearpage

\setcounter{table}{5}
\begin{table*}[h!]
\renewcommand{\thetable}{\arabic{table}}
\caption{Measurements of Emission Lines: one break\label{tab:tablesplit}}
\begin{splittabular}{lhDccccBccccccc}
%\multicolumn{5}{c}{Table 6} \\
%\multicolumn{5}{c}{Measurements of Emission Lines} \\
\hline 
\hline 
Model & Component & \multicolumn2c{Shift} & FWHM & 
\multicolumn{10}{c}{Flux} \\
 & & \multicolumn2c{($\rm km~s^{-1}$)} & {($\rm km~s^{-1}$)} & 
\multicolumn{10}{c}{($\rm 10^{-17}~erg~s^{-1}~cm^{-2}$)} \\
\cline{5-15}
 & & & & & {Ly$\alpha$} & {N\,{\footnotesize V}} & 
{Si\,{\footnotesize IV}} & {C\,{\footnotesize IV}} &
{Mg\,{\footnotesize II}} & {H$\gamma$} & {H$\beta$}
& {H$\alpha$} & {He\,{\footnotesize I}} & {Pa$\gamma$} \\
%\hline
\decimalcolnumbers
 & BELs& -97.13 &    9117$\pm      38$&    1033$\pm      33$&$< 35$&$<     166$&     637$\pm      31$&    1951$\pm      26$&     991$\pm 30$&    3502$\pm      42$&   20285$\pm      80$&    2025$\pm     116$& 1289$\pm     107$\\
Model 1 & IELs& -4049.123 & 1974$\pm      22$&    2495$\pm      30$&$<     42$&$<     109$&     995$\pm 186$&      83$\pm      30$&      75$\pm      23$&     130$\pm      25$& 357$\pm      94$&     194$\pm      64$& 36$\pm      23$\\
 & NELs& . &     641$\pm       4$&     449$\pm 23$&$<      6$&$<       9$&       --            &     275$\pm      18$& 150$\pm      11$&     313$\pm      12$&     958$\pm      43$&     318$\pm 34$& 151$\pm       17$\\
\hline
 & BELs& -85 &    8991$\pm      41$& 988$\pm      29$&$<     24$&$<     173$&     623$\pm      28$&    1945$\pm 29$&     989$\pm      27$&    3498$\pm      37$&   20288$\pm      73$& 2047$\pm     143$& 1376$\pm     167$\\
Model 2 & IELs& -51000 &    2025$\pm      26$& 2494$\pm      32$&$<     37$&$<     124$&    1005$\pm     190$&      72$\pm 28$&      72$\pm      21$&     113$\pm      18$&     271$\pm      85$& 205$\pm      72$& 34$\pm      21$\\
 & NELs& 52 &     637$\pm      10$&     477$\pm 17$&$<      4$&$<       8$&       --            &     278$\pm      17$& 153$\pm      10$&     317$\pm      15$&     969$\pm      40$&     325$\pm 37$& 147$\pm       22$\\
\hline
\end{splittabular}
\end{table*}

\subsection{Figures\label{subsec:figures}}

%% The "ht!" tells LaTeX to put the figure "here" first, at the "top" next
%% and to override the normal way of calculating a float position
\begin{figure}[ht!]
\plotone{cost-eps-converted-to.pdf}
\caption{The subscription and author publication costs from 1991 to 2013.
The data comes from Table \ref{tab:table}.\label{fig:general}}
\end{figure}

Authors can include a wide number of different graphics with their articles
in  encapsulated postscript (EPS) or portable document format (PDF).  These
range from general figures all authors are familiar with to new enhanced
graphics that can only be fully experienced in HTML.  The later include
animations, figure sets and interactive figures.  This portion of the
article provides examples for setting up all these graphics in with the
latest version of \aastex.

\subsection{General figures\label{subsec:general}}

\aastex\ has a {\tt\string\plotone} command to display a figure
consisting of one EPS/PDF file.  Figure \ref{fig:general} is an example
which uses the data from Table \ref{tab:table}. For a general figure
consisting of two EPS/PDF files the {\tt\string\plottwo} command can be
used to position the two image files side by side.  Figure \ref{fig:f2}
shows the Swift/XRT X-ray light curves of two recurrent novae.  The data
from Figures \ref{fig:f2} through \ref{fig:fig4} are taken from Table 2 of
\citet{2011ApJS..197...31S}.

\begin{figure}
\plottwo{RS_Oph-eps-converted-to.pdf}{U_Sco-eps-converted-to.pdf}
\caption{Swift/XRT X-ray light curves of RS Oph and U Sco which represent
the two canonical recurrent types, a long period system with a red giant
secondary and a short period system with a dwarf/sub-dwarf secondary,
respectively.\label{fig:f2}}
\end{figure}

Both {\tt\string\plotone} and {\tt\string\plottwo} take a
{\tt\string\caption} and an optional {\tt\string\figurenum} command to
specify the figure number\footnote{It is better to not use
{\tt\string\figurenum} and let LaTeX auto-increment all the figures. If you
do use this command you need to mark all of them accordingly.}.  Each is
based on the {\tt\string graphicx} package command,
{\tt\string\includegraphics}.  Authors are welcome to use
{\tt\string\includegraphics} along with its optional arguments that control
the height, width, scale, and position angle of a file within the figure.
More information on the full usage of {\tt\string\includegraphics} can be
found at \break
\url{https://en.wikibooks.org/wiki/LaTeX/Importing\_Graphics\#Including\_graphics}.

\subsection{Grid figures}

Including more than two EPS/PDF files in a single figure call can be tricky
easily format.  To make the process easier for authors \aastex\ v6 offers
{\tt\string\gridline} which allows any number of individual EPS/PDF file
calls within a single figure.  Each file cited in a {\tt\string\gridline}
will be displayed in a row.  By adding more {\tt\string\gridline} calls an
author can easily construct a matrix X by Y individual files as a
single general figure.

For each {\tt\string\gridline} command a EPS/PDF file is called by one of
four different commands.  These are {\tt\string\fig},
{\tt\string\rightfig}, {\tt\string\leftfig}, and {\tt\string\boxedfig}.
The first file call specifies no image position justification while the
next two will right and left justify the image, respectively.  The
{\tt\string\boxedfig} is similar to {\tt\string\fig} except that a box is
drawn around the figure file when displayed. Each of these commands takes
three arguments.  The first is the file name.  The second is the width that
file should be displayed at.  While any natural \latex\ unit is allowed, it
is recommended that author use fractional units with the
{\tt\string\textwidth}.  The last argument is text for a subcaption.

Figure \ref{fig:pyramid} shows an inverted pyramid of individual
figure constructed with six individual EPS files using the
{\tt\string\gridline} option.

\begin{figure*}
\gridline{\fig{V2491_Cyg-eps-converted-to.pdf}{0.3\textwidth}{(a)}
          \fig{CSS081007-eps-converted-to.pdf}{0.3\textwidth}{(b)}
          \fig{LMC_2009-eps-converted-to.pdf}{0.3\textwidth}{(c)}
          }
\gridline{\fig{RS_Oph-eps-converted-to.pdf}{0.3\textwidth}{(d)}
          \fig{U_Sco-eps-converted-to.pdf}{0.3\textwidth}{(e)}
          }
\gridline{\fig{KT_Eri-eps-converted-to.pdf}{0.3\textwidth}{(f)}}
\caption{Inverted pyramid figure of six individual files. The nova are
(a) V2491 Cyg, (b) HV Cet, (c) LMC 2009, (d) RS Oph, (e) U Sco, and
(f) KT Eri.\label{fig:pyramid}}
\end{figure*}

\subsection{Figure sets}

A large collection of similar style figures should be grouped together as a
figure set.  The derived PDF article will only shows an example figure
while the enhanced content is available in the figure set in the electronic
edition.  The advantage of a figure set gives the reader the ability to
easily sort through the figure collection to find individual component
figures.  All of the figure set components, along with their html framework,
are also available for download in a .tar.gz package.

Special \latex\ mark up is required to create a figure set.  Prior to
\aastex\ v6 the underlying mark up commands had to be inserted by hand
but is now included.  Note that when an article with figure set is compiled
in \latex\ none of the component figures are shown and a floating Figure
Set caption will appear in the resulting PDF.

\figsetstart
\figsetnum{4}
\figsettitle{Swift X-ray light curves}

\figsetgrpstart
\figsetgrpnum{1.1}
\figsetgrptitle{KT Eri}
\figsetplot{KT_Eri-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.2}
\figsetgrptitle{RS Oph}
\figsetplot{RS_Oph-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.3}
\figsetgrptitle{U Sco}
\figsetplot{U_Sco-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.4}
\figsetgrptitle{V2491 Cyg}
\figsetplot{V2491_Cyg-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.5}
\figsetgrptitle{Nova LMC 2009}
\figsetplot{LMC_2009-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.6}
\figsetgrptitle{HV Cet}
\figsetplot{CSS081007-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.7}
\figsetgrptitle{V2672 Oph}
\figsetplot{V2672_Oph-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.8}
\figsetgrptitle{V407 Cyg}
\figsetplot{V407_Cyg-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetend

\begin{figure}
\plotone{KT_Eri-eps-converted-to.pdf}
\caption{The Swift/XRT X-ray light curve for the first year after
outburst of the suspected recurrent nova KT Eri. At a maximum count rate of 
328 ct/s, KT Eri was the brightest nova in X-rays observed to date. All 
the component figures are available in the Figure Set. \label{fig:fig4}}
\end{figure}

Authors are encouraged to use an online tool at
\url{http://authortools.aas.org/FIGSETS/make-figset.html} to generate their
own specific figure set mark up to incorporate into their \latex\ articles.

\subsection{Animations}

Authors may include animations in their articles.  A single still frame from 
the animation should be included as a regular figure to serve as an example.
The associated figure caption should indicate to the reader exactly what the
animation shows and that the animation is available online.

\begin{figure}
\plotone{video3-eps-converted-to.pdf}
\caption{Example image from the animation which is available in the electronic
edition.}
\end{figure}

\subsection{Interactive figures}

Interactive figures give the reader the ability to manipulate the
information contained in an image which can add clarity or help further the
author's narrative.  These figures consist of two parts, the figure file in
a specific format and a javascript and html frame work that provides the
interactive control.  An example of an interactive figure is a 3D model.
The underlying figure is a X3D file while x3dom.js is the javascript driver
that displays it. An author created interface is added via a html wrapper.
The first 3D model published by the AAS Journals using this technique was
\citet{2014ApJ...793..127V}.  Authors should consult the online tutorials
for more information on how to construct their own interactive figures.

As with animations authors should include a non-interactive regular figure
to use as an example.  The example figure should also indicate to the reader
that the enhanced figure is interactive and can be accessed online.

\section{Displaying mathematics} \label{sec:displaymath}

The most common mathematical symbols and formulas are in the amsmath
package.  \aastex\ requires this package so there is no need to
specifically call for it in the document preamble.  Most modern \latex\
distributions already contain this package.  If you do not have this
package or the other required packages, revtex4-1, latexsym, graphicx,
amssymb, longtable, and epsf, they can be obtained from 
\url{http://www.ctan.org}

Mathematics can be displayed either within the text, e.g. $E = mc^2$, or
separate from in an equation.  In order to be properly rendered, all inline
math text has to be declared by surrounding the math by dollar signs (\$).

A complex equation example with inline math as part of the explanation
follows.

\begin{equation}
\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
\hat a_nu(p_1,\sigma_1) ,
\end{equation}
where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
operator $(\tau = \pm1)$.  This produces a single line formula.  \latex\ will
auto-number this and any subsequent equations.  If no number is desired then
the {\tt\string equation} call should be replaced with {\tt\string displaymath}.

\latex\ can also handle a a multi-line equation.  Use {\tt\string eqnarray}
for more than one line and end each line with a
\textbackslash\textbackslash.  Each line will be numbered unless the
\textbackslash\textbackslash\ is preceded by a {\tt\string\nonumber}
command.  Alignment points can be added with ampersands (\&).  There should be
two ampersands per line. In the examples they are centered on the equal
symbol.

\begin{eqnarray}
\gamma^\mu  & = &
 \left(
\begin{array}{cc}
0 & \sigma^\mu_+ \\
\sigma^\mu_- & 0
\end{array}     \right) ,
 \gamma^5= \left(
\begin{array}{cc}
-1 &   0\\
0 &   1
\end{array}     \right)  , \\
\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , 
\end{eqnarray}

\begin{eqnarray}
\hat a & = & \left(
\begin{array}{cc}
0 & (\hat a)_+\\
(\hat a)_- & 0
\end{array}\right), \nonumber \\
(\hat a)_\pm & = & a_\mu\sigma^\mu_\pm 
\end{eqnarray}

%% Putting eqnarrays or equations inside the mathletters environment groups
%% the enclosed equations by letter. For instance, the eqnarray below, instead
%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
%% LaTeX the paper and look at the output to see the results.

\section{Revision tracking and color highlighting} \label{sec:highlight}

Authors sometimes use color to highlight changes to their manuscript in
response to editor and referee comments.  In \aastex\ new commands
have been introduced to make this easier and formalize the process.

The first method is through a new set of editing mark up commands that
specifically identify what has been changed.  These commands are
{\tt\string\added\{<text>\}}, {\tt\string\deleted\{<text>\}}, and
{\tt\string\replaced\{<old text>\}\{<replaced text>\}}. To activate these
commands the {\tt\string trackchanges} option must be used in the
{\tt\string\documentclass} call.  When compiled this will produce the
marked text in red.  The {\tt\string\explain\{<text>\}} can be used to add
text to provide information to the reader describing the change.  Its
output is purple italic font. To see how {\tt\string\added\{<important
added info>\}}, {\tt\string\deleted\{<this can be deleted text>\}},
{\tt\string\replaced\{<old data>\}\{<replaced data>\}}, and \break
{\tt\string\explain\{<text explaining the change>\}} commands will produce
\added{important added information}\deleted{, deleted text, and }
\replaced{old data}{and replaced data,} toggle between versions compiled with
and without the {\tt\string trackchanges} option.\explain{text explaining
the change}

A summary list of all these tracking commands can be produced at the end of
the article by adding the {\tt\string\listofchanges} just before the
{\tt\string\end\{document\}} call.  The page number for each change will be
provided. If the {\tt\string linenumbers} option is also included in the
documentcall call then not only will all the lines in the article be
numbered for handy reference but the summary list will also include the
line number for each change.

The second method does not have the ability to highlight the specific
nature of the changes but does allow the author to document changes over
multiple revisions.  The commands are {\tt\string\edit1\{<text>\}},
{\tt\string\edit2\{<text>\}} and {\tt\string\edit3\{<text>\}} and they
produce {\tt\string<text>} that is highlighted in bold red, italic blue and
underlined purple, respectively.  Authors should use the first command to
\edit1{indicated which text has been changed from the first revision.}  The
second command is to highlight \edit2{new or modified text from a second
revision}.  If a third revision is needed then the last command should be used 
\edit3{to show this changed text}.  Since over 90\% of all manuscripts are
accepted after the 3rd revision these commands make it easy to identify
what text has been added and when.  Once the article is accepted all the
highlight color can be turned off simply by adding the
{\tt\string\turnoffediting} command in the preamble. Likewise, the new commands
{\tt\string\turnoffeditone}, {\tt\string\turnoffedittwo}, and
{\tt\string\turnoffeditthree} can be used to only turn off the 
{\tt\string\edit1\{<text>\}}, {\tt\string\edit2\{<text>\}} and 
{\tt\string\edit3\{<text>\}}, respectively.

Similar to marking editing changes with the {\tt\string\edit} options there
are also the {\tt\string\authorcomments1\{<text>\}}, 
{\tt\string\authorcomments2\{<text>\}} and
{\tt\string\authorcomments3\{<text>\}} commands.  These produce the same
bold red, italic blue and underlined purple text but when the
{\tt\string\turnoffediting} command is present the {\tt\string<text>}
material does not appear in the manuscript.  Authors can use these commands
to mark up text that they are not sure should appear in the final
manuscript or as a way to communicate comments between co-authors when
writing the article.

\section{Software and third party data repository citations} \label{sec:cite}

The AAS Journals would like to encourage authors to change software and
third party data repository references from the current standard of a
footnote to a first class citation in the bibliography.  As a bibliographic
citation these important references will be more easily captured and credit
will be given to the appropriate people.

The first step to making this happen is to have the data or software in
a long term repository that has made these items available via a persistent
identifier like a Digital Object Identifier (DOI).  A list of repositories
that satisfy this criteria plus each one's pros and cons are given at \break
\url{https://github.com/AASJournals/Tutorials/tree/master/Repositories}.

In the bibliography the format for data or code follows this format: \\

\noindent author year, title, version, publisher, prefix:identifier\\

\citet{2015ApJ...805...23C} provides a example of how the citation in the
article references the external code at
\doi{10.5281/zenodo.15991}.  Unfortunately, bibtex does
not have specific bibtex entries for these types of references so the
``@misc'' type should be used.  The Repository tutorial explains how to
code the ``@misc'' type correctly.  The most recent aasjournal.bst file,
available with \aastex\ v6, will output bibtex ``@misc'' type properly.

%% If you wish to include an acknowledgments section in your paper,
%% separate it off from the body of the text using the \acknowledgments
%% command.
\acknowledgments

We thank all the people that have made this AASTeX what it is today.  This
includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
for the new "modern" style design. Considerable help was provided via bug
reports and hacks from numerous people including Patricio Cubillos, Alex
Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
Gagne.

%% To help institutions obtain information on the effectiveness of their 
%% telescopes the AAS Journals has created a group of keywords for telescope 
%% facilities.
%
%% Following the acknowledgments section, use the following syntax and the
%% \facility{} or \facilities{} macros to list the keywords of facilities used 
%% in the research for the paper.  Each keyword is check against the master 
%% list during copy editing.  Individual instruments can be provided in 
%% parentheses, after the keyword, but they are not verified.

\vspace{5mm}
\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
CTIO:1.5m,CXO}

%% Similar to \facility{}, there is the optional \software command to allow 
%% authors a place to specify which programs were used during the creation of 
%% the manusscript. Authors should list each code and include either a
%% citation or url to the code inside ()s when available.

\software{astropy \citep{2013A&A...558A..33A},  
          Cloudy \citep{2013RMxAA..49..137F}, 
          SExtractor \citep{1996A&AS..117..393B}
          }

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc. The
%% Figure and Table counter will not reset.

\appendix

\section{Appendix information}

Appendices can be broken into separate sections just like in the main text.
The only difference is that each appendix section is indexed by a letter
(A, B, C, etc.) instead of a number.  Likewise numbered equations have
the section letter appended.  Here is an equation as an example.

\begin{equation}
I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
\end{equation}

Appendix tables and figures should not be numbered like equations. Instead
they should continue the sequence from the main article body.

\section{Author publication charges} \label{sec:pubcharge}

Finally some information about the AAS Journal's publication charges.
In April 2011 the traditional way of calculating author charges based on 
the number of printed pages was changed.  The reason for the change
was due to a recognition of the growing number of article items that could not 
be represented in print. Now author charges are determined by a number of
digital ``quanta''.  A single quantum is 350 words, one figure, one table,
and one enhanced digital item.  For the latter this includes machine readable
tables, figure sets, animations, and interactive figures.  The current cost
is \$27 per word quantum and \$30 for all other quantum type.

\section{Rotating tables} \label{sec:rotate}

The process of rotating tables into landscape mode is slightly different in
\aastex v6.2. Instead of the {\tt\string\rotate} command, a new environment
has been created to handle this task. To place a single page table in a
landscape mode start the table portion with
{\tt\string\begin\{rotatetable\}} and end with
{\tt\string\end\{rotatetable\}}.

Tables that exceed a print page take a slightly different environment since
both rotation and long table printing are required. In these cases start
with {\tt\string\begin\{longrotatetable\}} and end with
{\tt\string\end\{longrotatetable\}}. Table \ref{chartable} is an
example of a multi-page, rotated table.

\begin{longrotatetable}
\begin{deluxetable*}{lllrrrrrrll}
\tablecaption{Observable Characteristics of 
Galactic/Magellanic Cloud novae with X-ray observations\label{chartable}}
\tablewidth{700pt}
\tabletypesize{\scriptsize}
\tablehead{
\colhead{Name} & \colhead{V$_{max}$} & 
\colhead{Date} & \colhead{t$_2$} & 
\colhead{FWHM} & \colhead{E(B-V)} & 
\colhead{N$_H$} & \colhead{Period} & 
\colhead{D} & \colhead{Dust?} & \colhead{RN?} \\ 
\colhead{} & \colhead{(mag)} & \colhead{(JD)} & \colhead{(d)} & 
\colhead{(km s$^{-1}$)} & \colhead{(mag)} & \colhead{(cm$^{-2}$)} &
\colhead{(d)} & \colhead{(kpc)} & \colhead{} & \colhead{}
} 
\startdata
CI Aql & 8.83 (1) & 2451665.5 (1) & 32 (2) & 2300 (3) & 0.8$\pm0.2$ (4) & 1.2e+22 & 0.62 (4) & 6.25$\pm5$ (4) & N & Y \\
{\bf CSS081007} & \nodata & 2454596.5 & \nodata & \nodata & 0.146 & 1.1e+21 & 1.77 (5) & 4.45$\pm1.95$ (6) & \nodata & \nodata \\
GQ Mus & 7.2 (7) & 2445352.5 (7) & 18 (7) & 1000 (8) & 0.45 (9) & 3.8e+21  & 0.059375 (10) & 4.8$\pm1$ (9) & N (7) & \nodata \\
IM Nor & 7.84 (11) & 2452289 (2) & 50 (2) & 1150 (12) & 0.8$\pm0.2$ (4) & 8e+21 & 0.102 (13) & 4.25$\pm3.4$ (4) & N & Y \\
{\bf KT Eri} & 5.42 (14) & 2455150.17 (14) & 6.6 (14) & 3000 (15) & 0.08 (15) & 5.5e+20 & \nodata & 6.5 (15) & N & M \\
{\bf LMC 1995} & 10.7 (16) & 2449778.5 (16) & 15$\pm2$ (17) & \nodata & 0.15 (203) & 7.8e+20  & \nodata & 50 & \nodata & \nodata \\
LMC 2000 & 11.45 (18) & 2451737.5 (18) & 9$\pm2$ (19) & 1700 (20) & 0.15 (203) & 7.8e+20  & \nodata & 50 & \nodata & \nodata \\
{\bf LMC 2005} & 11.5 (21) & 2453700.5 (21) & 63 (22) & 900 (23) & 0.15 (203) & 1e+21 & \nodata & 50  & M (24) & \nodata \\
{\bf LMC 2009a} & 10.6 (25) & 2454867.5 (25) & 4$\pm1$  & 3900 (25) & 0.15 (203)  & 5.7e+20 & 1.19 (26) & 50 & N & Y \\
{\bf SMC 2005} & 10.4 (27) & 2453588.5 (27) & \nodata & 3200 (28) & \nodata & 5e+20  & \nodata & 61 & \nodata & \nodata \\
{\bf QY Mus} & 8.1 (29) & 2454739.90 (29) & 60:  & \nodata & 0.71 (30) & 4.2e+21  & \nodata & \nodata & M & \nodata \\
{\bf RS Oph} & 4.5 (31) & 2453779.44 (14) & 7.9 (14) & 3930 (31) & 0.73 (32) & 2.25e+21 & 456 (33) & 1.6$\pm0.3$ (33) & N (34) & Y \\
{\bf U Sco} & 8.05 (35) & 2455224.94 (35) & 1.2 (36) & 7600 (37) & 0.2$\pm0.1$ (4) & 1.2e+21 & 1.23056 (36) & 12$\pm2$ (4) & N & Y \\
{\bf V1047 Cen} & 8.5 (38) & 2453614.5 (39) & 6 (40) & 840 (38) & \nodata & 1.4e+22  & \nodata & \nodata & \nodata & \nodata \\
{\bf V1065 Cen} & 8.2 (41) & 2454123.5 (41) & 11 (42) & 2700 (43) & 0.5$\pm0.1$ (42) & 3.75e+21 & \nodata & 9.05$\pm2.8$ (42) & Y (42) & \nodata \\
V1187 Sco & 7.4 (44) & 2453220.5 (44) & 7: (45) & 3000 (44) & 1.56 (44) & 8.0e+21 & \nodata & 4.9$\pm0.5$ (44) & N & \nodata \\
{\bf V1188 Sco} & 8.7 (46) & 2453577.5 (46) & 7 (40) & 1730 (47) & \nodata & 5.0e+21  & \nodata & 7.5 (39) & \nodata & \nodata \\
{\bf V1213 Cen} & 8.53 (48) & 2454959.5 (48) & 11$\pm2$ (49) & 2300 (50) & 2.07 (30) & 1.0e+22 & \nodata & \nodata & \nodata & \nodata \\
{\bf V1280 Sco} & 3.79 (51) & 2454147.65 (14) & 21 (52) & 640 (53) & 0.36 (54) & 1.6e+21  & \nodata & 1.6$\pm0.4$ (54) & Y (54) & \nodata \\
{\bf V1281 Sco} & 8.8 (55) & 2454152.21 (55) & 15:& 1800 (56) & 0.7 (57) & 3.2e+21 & \nodata & \nodata & N & \nodata \\
{\bf V1309 Sco} & 7.1 (58) & 2454714.5 (58) & 23$\pm2$ (59) & 670 (60) & 1.2 (30) & 4.0e+21 & \nodata & \nodata & \nodata & \nodata \\
{\bf V1494 Aql} & 3.8 (61) & 2451515.5 (61) & 6.6$\pm0.5$ (61) & 1200 (62) & 0.6 (63) & 3.6e+21  & 0.13467 (64) & 1.6$\pm0.1$ (63) & N & \nodata \\
{\bf V1663 Aql} & 10.5 (65) & 2453531.5 (65) & 17 (66) & 1900 (67) & 2: (68) & 1.6e+22  & \nodata & 8.9$\pm3.6$ (69) & N & \nodata \\
V1974 Cyg & 4.3 (70) & 2448654.5 (70) & 17 (71) & 2000 (19) & 0.36$\pm0.04$ (71) & 2.7e+21  & 0.081263 (70) & 1.8$\pm0.1$ (72) & N & \nodata \\
{\bf V2361 Cyg} & 9.3 (73) & 2453412.5 (73) & 6 (40) & 3200 (74) & 1.2: (75) & 7.0e+21 & \nodata & \nodata & Y (40) & \nodata \\
{\bf V2362 Cyg} & 7.8 (76) & 2453831.5 (76) & 9 (77) & 1850 (78) & 0.575$\pm0.015$ (79) & 4.4e+21  & 0.06577 (80) & 7.75$\pm3$ (77) & Y (81) & \nodata \\
{\bf V2467 Cyg} & 6.7 (82) & 2454176.27 (82) & 7 (83) & 950 (82) & 1.5 (84) & 1.4e+22  & 0.159 (85) & 3.1$\pm0.5$ (86) & M (87) & \nodata \\
{\bf V2468 Cyg} & 7.4 (88) & 2454534.2 (88) & 10: & 1000 (88) & 0.77 (89) & 1.0e+22  & 0.242 (90) & \nodata & N & \nodata \\
{\bf V2491 Cyg} & 7.54 (91) & 2454567.86 (91) & 4.6 (92) & 4860 (93) & 0.43 (94) & 4.7e+21  & 0.09580: (95) & 10.5 (96) & N & M \\
V2487 Oph & 9.5 (97) & 2450979.5 (97) & 6.3 (98) & 10000 (98) & 0.38$\pm0.08$ (98) & 2.0e+21 & \nodata & 27.5$\pm3$ (99) & N (100) & Y (101) \\
{\bf V2540 Oph} & 8.5 (102) & 2452295.5 (102) & \nodata & \nodata & \nodata & 2.3e+21 & 0.284781 (103) & 5.2$\pm0.8$ (103) & N & \nodata \\
V2575 Oph & 11.1 (104) & 2453778.8 (104) & 20: & 560 (104) & 1.4 (105) & 3.3e+21 & \nodata & \nodata & N (105) & \nodata \\
{\bf V2576 Oph} & 9.2 (106) & 2453832.5 (106) & 8: & 1470 (106) & 0.25 (107) & 2.6e+21  & \nodata & \nodata & N & \nodata \\
{\bf V2615 Oph} & 8.52 (108) & 2454187.5 (108) & 26.5 (108) & 800 (109) & 0.9 (108) & 3.1e+21  & \nodata & 3.7$\pm0.2$ (108) & Y (110) & \nodata \\
{\bf V2670 Oph} & 9.9 (111) & 2454613.11 (111) & 15: & 600 (112) & 1.3: (113) & 2.9e+21  & \nodata & \nodata & N (114) & \nodata \\
{\bf V2671 Oph} & 11.1 (115) & 2454617.5 (115) & 8: & 1210 (116) & 2.0 (117) & 3.3e+21  & \nodata & \nodata & M (117) & \nodata \\
{\bf V2672 Oph} & 10.0 (118) & 2455060.02 (118) & 2.3 (119) & 8000 (118) & 1.6$\pm0.1$ (119) & 4.0e+21  & \nodata & 19$\pm2$ (119) & \nodata & M \\
V351 Pup & 6.5 (120) & 2448617.5 (120) & 16 (121) & \nodata & 0.72$\pm0.1$ (122) & 6.2e+21 & 0.1182 (123) & 2.7$\pm0.7$ (122) & N & \nodata \\
{\bf V382 Nor} & 8.9 (124) & 2453447.5 (124) & 12 (40) & 1850 (23) & \nodata & 1.7e+22 & \nodata & \nodata & \nodata & \nodata \\
V382 Vel & 2.85 (125) & 2451320.5 (125) & 4.5 (126) & 2400 (126) & 0.05: (126) & 3.4e+21  & 0.146126 (127) & 1.68$\pm0.3$ (126) & N & \nodata \\
{\bf V407 Cyg} & 6.8 (128) & 2455266.314 (128) & 5.9 (129) & 2760 (129) & 0.5$\pm0.05$ (130) & 8.8e+21 & 15595 (131) & 2.7 (131) & \nodata & Y \\
{\bf V458 Vul} & 8.24 (132) & 2454322.39 (132) & 7 (133) & 1750 (134) & 0.6 (135) & 3.6e+21 & 0.06812255 (136) & 8.5$\pm1.8$ (133) & N (135) & \nodata \\
{\bf V459 Vul} & 7.57 (137) & 2454461.5 (137) & 18 (138) & 910 (139) & 1.0 (140) & 5.5e+21  & \nodata & 3.65$\pm1.35$ (138) & Y (140) & \nodata \\
V4633 Sgr & 7.8 (141) & 2450895.5 (141) & 19$\pm3$ (142) & 1700 (143) & 0.21 (142) & 1.4e+21  & 0.125576 (144) & 8.9$\pm2.5$ (142) & N & \nodata \\
{\bf V4643 Sgr} & 8.07 (145) & 2451965.867 (145) & 4.8 (146) & 4700 (147) & 1.67 (148) & 1.4e+22 & \nodata & 3 (148) & N & \nodata \\
{\bf V4743 Sgr} & 5.0 (149) & 2452537.5 (149) & 9 (150) & 2400 (149) & 0.25 (151) & 1.2e+21 & 0.281 (152) & 3.9$\pm0.3$ (151) & N & \nodata \\
{\bf V4745 Sgr} & 7.41 (153) & 2452747.5 (153) & 8.6 (154) & 1600 (155) & 0.1 (154) & 9.0e+20  & 0.20782 (156) & 14$\pm5$ (154) & \nodata & \nodata \\
{\bf V476 Sct} & 10.3 (157) & 2453643.5 (157) & 15 (158) & \nodata & 1.9 (158) & 1.2e+22  & \nodata & 4$\pm1$ (158) & M (159) & \nodata \\
{\bf V477 Sct} & 9.8 (160) & 2453655.5 (160) & 3 (160) & 2900 (161) & 1.2: (162) & 4e+21  & \nodata & \nodata & M (163) & \nodata \\
{\bf V5114 Sgr} & 8.38 (164) & 2453081.5 (164) & 11 (165) & 2000 (23) & \nodata & 1.5e+21  & \nodata & 7.7$\pm0.7$ (165) & N (166) & \nodata \\
{\bf V5115 Sgr} & 7.7 (167) & 2453459.5 (167) & 7 (40) & 1300 (168) & 0.53 (169) & 2.3e+21  & \nodata & \nodata & N (169) & \nodata \\
{\bf V5116 Sgr} & 8.15 (170) & 2453556.91 (170) & 6.5 (171) & 970 (172) & 0.25 (173) & 1.5e+21 & 0.1238 (171) & 11$\pm3$ (173) & N (174) & \nodata \\
{\bf V5558 Sgr} & 6.53 (175) & 2454291.5 (175) & 125 (176) & 1000 (177) & 0.80 (178) & 1.6e+22  & \nodata & 1.3$\pm0.3$ (176) & N (179) & \nodata \\
{\bf V5579 Sgr} & 5.56 (180) & 2454579.62 (180) & 7: & 1500 (23) & 1.2 (181) & 3.3e+21 & \nodata & \nodata & Y (181) & \nodata \\
{\bf V5583 Sgr} & 7.43 (182) & 2455051.07 (182) & 5: & 2300 (182) & 0.39 (30) & 2.0e+21 & \nodata & 10.5 & \nodata & \nodata \\
{\bf V574 Pup} & 6.93 (183) & 2453332.22 (183) & 13 (184) & 2800 (184) & 0.5$\pm0.1$  & 6.2e+21 & \nodata & 6.5$\pm1$  & M (185) & \nodata \\
{\bf V597 Pup} & 7.0 (186) & 2454418.75 (186) & 3: & 1800 (187) & 0.3 (188) & 5.0e+21  & 0.11119 (189) & \nodata & N (188) & \nodata \\
{\bf V598 Pup} & 3.46 (14) & 2454257.79 (14) & 9$\pm1$ (190) & \nodata & 0.16 (190) & 1.4e+21 & \nodata & 2.95$\pm0.8$ (190) & \nodata & \nodata \\
{\bf V679 Car} & 7.55 (191) & 2454797.77 (191) & 20: & \nodata & \nodata & 1.3e+22  & \nodata & \nodata & \nodata & \nodata \\
{\bf V723 Cas} & 7.1 (192) & 2450069.0 (192) & 263 (2) & 600 (193) & 0.5 (194) & 2.35e+21  & 0.69 (195) & 3.86$\pm0.23$ (196) & N & \nodata \\
V838 Her & 5 (197) & 2448340.5 (197) & 2 (198) & \nodata & 0.5$\pm0.1$ (198) & 2.6e+21  & 0.2975 (199) & 3$\pm1$ (198) & Y (200) & \nodata \\
{\bf XMMSL1 J06} & 12 (201) & 2453643.5 (202) & 8$\pm2$ (202) & \nodata & 0.15 (203) & 8.7e+20 & \nodata & 50 & \nodata & \nodata \\
\enddata
\end{deluxetable*}
\end{longrotatetable}

A handy "cheat sheat" that provides the necessary LaTeX to produce 17 
different types of tables is available at \url{http://journals.aas.org/authors/aastex/aasguide.html#table_cheat_sheet}.

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% \aastex provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

\begin{thebibliography}{}

\bibitem[Astropy Collaboration et al.(2013)]{2013A&A...558A..33A} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, A33 
\bibitem[Bertin \& Arnouts(1996)]{1996A&AS..117..393B} Bertin, E., \& Arnouts, S.\ 1996, \aaps, 117, 393 
\bibitem[Corrales(2015)]{2015ApJ...805...23C} Corrales, L.\ 2015, \apj, 805, 23
\bibitem[Ferland et al.(2013)]{2013RMxAA..49..137F} Ferland, G.~J., Porter, R.~L., van Hoof, P.~A.~M., et al.\ 2013, \rmxaa, 49, 137
\bibitem[Hanisch \& Biemesderfer(1989)]{1989BAAS...21..780H} Hanisch, R.~J., \& Biemesderfer, C.~D.\ 1989, \baas, 21, 780 
\bibitem[Lamport(1994)]{lamport94} Lamport, L. 1994, LaTeX: A Document Preparation System, 2nd Edition (Boston, Addison-Wesley Professional)
\bibitem[Schwarz et al.(2011)]{2011ApJS..197...31S} Schwarz, G.~J., Ness, J.-U., Osborne, J.~P., et al.\ 2011, \apjs, 197, 31  
\bibitem[Vogt et al.(2014)]{2014ApJ...793..127V} Vogt, F.~P.~A., Dopita, M.~A., Kewley, L.~J., et al.\ 2014, \apj, 793, 127

\end{thebibliography}

%% This command is needed to show the entire author+affilation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{document}

% End of file `sample62.tex'.

### 2018-11-08 rnaas.tex
Initial ShareLaTeX Import

%% rnaastex.cls is the classfile used for Research Notes. It is derived
%% from aastex61.cls with a few tweaks to allow for the unique format required.
%% (10/15/17)
%%\documentclass{rnaastex}

%% Better is to use the "RNAAS" style option in AASTeX v6.2
%% (01/08/18)
\documentclass[RNAAS]{aastex62}

%% Define new commands here
\newcommand\latex{La\TeX}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figures/}}

\begin{document}

\title{Transient brightenings observed in many instruments}

%% Note that the corresponding author command and emails has to come
%% before everything else. Also place all the emails in the \email
%% command instead of using multiple \email calls.
\correspondingauthor{Adam R. Kobelski}
\email{adam.kobelski@mail.wvu.edu, ltarr2@gmu.edu, sjaeggli@nso.edu, sabrina.savage@nasa.gov}

\author{Adam R. Kobelski}
\affiliation{West Virginia University}

\author{Lucas A. Tarr}
\affiliation{George Mason University}

\author{Sarah Jaeggli}
\affiliation{National Solar Observatory}

%% The \author command can take an optional ORCID.
\author{Sabrina Savage}
\affiliation{NASA Marshall Space Flight Center}

%% Note that RNAAS manuscripts DO NOT have abstracts.
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{editorials, notices --- 
miscellaneous --- catalogs --- surveys}

%% Start the main body of the article. If no sections in the 
%% research note leave the \section call blank to make the title.
\section{}

\textit{Research Notes of the \href{https://aas.org}{American Astronomical Society}}
(\href{http://rnaas.aas.org}{RNAAS}) is a publication in the AAS portfolio
(alongside ApJ, AJ, ApJ Supplements, and ApJ Letters) through which authors can 
promptly and briefly share materials of interest with the astronomical community
in a form that will be searchable via ADS and permanently archived.

The astronomical community has long faced a challenge in disseminating
information that may not meet the criteria for a traditional journal article.
There have generally been few options available for sharing works in progress,
comments and clarifications, null results, and timely reports of observations
(such as the spectrum of a supernova), as well as results that wouldn’t
traditionally merit a full paper (such as the discovery of a single exoplanet
or contributions to the monitoring of variable sources).

Launched in 2017, RNAAS was developed as a supported and long-term
communication channel for results such as these that would otherwise be
difficult to broadly disseminate to the professional community and persistently
archive for future reference.

Submissions to RNAAS should be brief communications - 1,000 words or fewer
\footnote{An easy way to count the number of words in a Research Note is to use
the \texttt{texcount} utility installed with most \latex\ installations. The
call  \texttt{texcount -incbib -v3 rnaas.tex}) gives 57 words in the front
matter and 493 words in the text/references/captions of this template. Another
option is by copying the words into MS/Word, and using ``Word Count'' under the
Tool tab.}, and no more than a single figure (e.g. Figure \ref{fig:1}) or table
(but not both) - and should be written in a style similar to that of a
traditional journal article, including references, where appropriate, but not
including an abstract.

Unlike the other journals in the AAS portfolio, RNAAS publications are not
peer reviewed; they are, however, reviewed by an editor for appropriateness
and format before publication. If accepted, RNAAS submissions are typically
published within 72 hours of manuscript receipt. Each RNAAS article is
issued a DOI and indexed by ADS \citep{2000A&AS..143...41K} to create a
long-term, citable record of work.

Articles can be submitted in \latex\ (preferably with the new "RNAAS"
style option in AASTeX v6.2), MS/Word, or via the direct submission in the
\href{http://www.authorea.com}{Authorea} or
\href{http://www.overleaf.com}{Overleaf} online collaborative editors.

Authors are expected to follow the AAS's ethics \citep{2006ApJ...652..847K},
including guidance on plagiarism \citep{2012AAS...21920404V}.

%% An example figure call using \includegraphics
\begin{figure}[h!]
\begin{center}
\includegraphics[scale=0.85,angle=0]{aas.pdf}
\caption{Top page of the AAS Journals' website, \url{http://journals.aas.org},
on October 15, 2017.  Each RNAAS manuscript is only allowed one figure or
table (but not both). Including the
\href{http://journals.aas.org//authors/data.html\#DbF}{data behind the figure}
in a Note is encouraged, and the data will be provided as a link in the
published Note.\label{fig:1}}
\end{center}
\end{figure}

%% An example table using AASTeX's deluxetable. Note that since
%% only one figure OR one table is allowed this is commented out.
%\begin{deluxetable}{ccl}
%\tablecaption{Example table some English and Greek letters\label{tab:1}}
%\tablehead{
%\colhead{Index number} & \colhead{English} & \colhead{Greek}
%}
%\startdata
%1 & a & alpha ($\alpha$) \\
%2 & b & beta ($\beta$) \\
%3 & c & gamma ($\gamma$) \\
%4 & d & delta ($\delta$) \\
%5 & e & epsilon ($\epsilon$) \\
%\enddata
%\tablecomments{Long tables should only show a short example with the full
%version as a machine readable table with the article.}
%\end{deluxetable}

\acknowledgments

Acknowledge people, facilities, and software here but remember that this counts
against your 1000 word limit.

\begin{thebibliography}{}

\bibitem[Kennicutt et al.(2006)]{2006ApJ...652..847K} Kennicutt, R.~C., Jr., Vishniac, E., \& Sneden, C.\ 2006, \apj, 652, 847

\bibitem[Kurtz et al.(2000)]{2000A&AS..143...41K} Kurtz, M.~J., Eichhorn, G., Accomazzi, A., et al.\ 2000, \aaps, 143, 41

\bibitem[Vishniac(2012)]{2012AAS...21920404V} Vishniac, E.~T.\ 2012, American Astronomical Society Meeting Abstracts \#219, 219, 204.04

\end{thebibliography}

\end{document}

### 2019-04-24 Paper1.tex
I changed the title
Updates from ShareLaTeX
started making a useful document

@@
-%%
-%% Beginning of file 'sample62.tex'
-%%
-%% Modified 2018 January
-%%
-%% This is a sample manuscript marked up using the
-%% AASTeX v6.2 LaTeX 2e macros.
-%%
-%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
-%% (Copyright 2000-2015).  See the classfile for details.
-
-%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
-%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
-%% All of these external packages should already be present in the modern TeX 
-%% distributions.  If not they can also be obtained at www.ctan.org.
-
-%% The first piece of markup in an AASTeX v6.x document is the \documentclass
-%% command. LaTeX will ignore any data that comes before this command. The 
-%% documentclass can take an optional argument to modify the output style.
-%% The command below calls the preprint style  which will produce a tightly 
-%% typeset, one-column, single-spaced document.  It is the default and thus
-%% does not need to be explicitly stated.
-%%
-%%
-%% using aastex version 6.2
 \documentclass{aastex62}
@@
 %% this information may be modified by the editorial offices.
-\shorttitle{Sample article}
-\shortauthors{Schwarz et al.}
+\shorttitle{The Kolsch of Data Sets}
+\shortauthors{Kobelski et al.}
 %%
@@
 
-\title{An Example Article using \aastex v6.2\footnote{Released on January, 8th, 2018}}
+\title{Transient brightenings observed with multiple instruments}
+\correspondingauthor{Adam R. Kobelski}
+\email{adam.kobelski@mail.wvu.edu, ltarr2@gmu.edu, sjaeggli@nso.edu, sabrina.savage@nasa.gov}
 
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire. In v6.2 you can include a footnote in the title.
+\author{Adam R. Kobelski}
+\affiliation{West Virginia University}
 
-%% A significant change from earlier AASTEX versions is in the structure for 
-%% calling author and affilations. The change was necessary to implement 
-%% autoindexing of affilations which prior was a manual process that could 
-%% easily be tedious in large author manuscripts.
-%%
-%% The \author command is the same as before except it now takes an optional
-%% arguement which is the 16 digit ORCID. The syntax is:
-%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
-%%
-%% This will hyperlink the author name to the author's ORCID page. Note that
-%% during compilation, LaTeX will do some limited checking of the format of
-%% the ID to make sure it is valid.
-%%
-%% Use \affiliation for affiliation information. The old \affil is now aliased
-%% to \affiliation. AASTeX v6.2 will automatically index these in the header.
-%% When a duplicate is found its index will be the same as its previous entry.
-%%
-%% Note that \altaffilmark and \altaffiltext have been removed and thus 
-%% can not be used to document secondary affiliations. If they are used latex
-%% will issue a specific error message and quit. Please use multiple 
-%% \affiliation calls for to document more than one affiliation.
-%%
-%% The new \altaffiliation can be used to indicate some secondary information
-%% such as fellowships. This command produces a non-numeric footnote that is
-%% set away from the numeric \affiliation footnotes.  NOTE that if an
-%% \altaffiliation command is used it must come BEFORE the \affiliation call,
-%% right after the \author command, in order to place the footnotes in
-%% the proper location.
-%%
-%% Use \email to set provide email addresses. Each \email will appear on its
-%% own line so you can put multiple email address in one \email call. A new
-%% \correspondingauthor command is available in V6.2 to identify the
-%% corresponding author of the manuscript. It is the author's responsibility
-%% to make sure this name is also in the author list.
-%%
-%% While authors can be grouped inside the same \author and \affiliation
-%% commands it is better to have a single author for each. This allows for
-%% one to exploit all the new benefits and should make book-keeping easier.
-%%
-%% If done correctly the peer review system will be able to
-%% automatically put the author and affiliation information from the manuscript
-%% and save the corresponding author the trouble of entering it by hand.
+\author[0000-0002-8259-8303]{Lucas A. Tarr}
+\affiliation{George Mason University}
 
-\correspondingauthor{August Muench}
-\email{greg.schwarz@aas.org, gus.muench@aas.org}
+\author{Sarah Jaeggli}
+\affiliation{National Solar Observatory}
 
-\author[0000-0002-0786-7307]{Greg J. Schwarz}
-\affil{American Astronomical Society \\
-2000 Florida Ave., NW, Suite 300 \\
-Washington, DC 20009-1231, USA}
-
-\author{August Muench}
-\affiliation{American Astronomical Society \\
-2000 Florida Ave., NW, Suite 300 \\
-Washington, DC 20009-1231, USA}
-\collaboration{(AAS Journals Data Scientists collaboration)}
-
-\author{Butler Burton}
-\affiliation{National Radio Astronomy Observatory}
-\affiliation{AAS Journals Associate Editor-in-Chief}
-\nocollaboration
-
-\author{Amy Hendrickson}
-\altaffiliation{Creator of AASTeX v6.2}
-\affiliation{TeXnology Inc.}
-\collaboration{(LaTeX collaboration)}
-
-\author{Julie Steffen}
-\affiliation{AAS Director of Publishing}
-\affiliation{American Astronomical Society \\
-2000 Florida Ave., NW, Suite 300 \\
-Washington, DC 20009-1231, USA}
-
-\author{Jeff Lewandowski}
-\affiliation{IOP Senior Publisher for the AAS Journals}
-\affiliation{IOP Publishing, Washington, DC 20005}
-
-%% Note that the \and command from previous versions of AASTeX is now
-%% depreciated in this version as it is no longer necessary. AASTeX 
-%% automatically takes care of all commas and "and"s between authors names.
-
-%% AASTeX 6.2 has the new \collaboration and \nocollaboration commands to
-%% provide the collaboration status of a group of authors. These commands 
-%% can be used either before or after the list of corresponding authors. The
-%% argument for \collaboration is the collaboration identifier. Authors are
-%% encouraged to surround collaboration identifiers with ()s. The 
-%% \nocollaboration command takes no argument and exists to indicate that
-%% the nearby authors are not part of surrounding collaborations.
-
-%% Mark off the abstract in the ``abstract'' environment. 
+%% The \author command can take an optional ORCID.
+\author{Sabrina Savage}
+\affiliation{NASA Marshall Space Flight Center}
 \begin{abstract}
-
-This example manuscript is intended to serve as a tutorial and template for
-authors to use when writing their own AAS Journal articles. The manuscript
-includes a history of \aastex\ and documents the new features in the
-previous versions as well as the new features in version 6.2. This
-manuscript includes many figure and table examples to illustrate these new
-features.  Information on features not explicitly mentioned in the article
-can be viewed in the manuscript comments or more extensive online
-documentation. Authors are welcome replace the text, tables, figures, and
-bibliography with their own and submit the resulting manuscript to the AAS
-Journals peer review system.  The first lesson in the tutorial is to remind
-authors that the AAS Journals, the Astrophysical Journal (ApJ), the
-Astrophysical Journal Letters (ApJL), and Astronomical Journal (AJ), all
-have a 250 word limit for the abstract\footnote{Note that manuscripts 
-submitted to the new Research Notes of the American Astronomical Society 
-(RNAAS) do \textbf{not} have abstracts.}.  If you exceed this length the
-Editorial office will ask you to shorten it.
+Here is our abstract.  We did work
 
 \end{abstract}
-
-%% Keywords should appear after the \end{abstract} command. 
-%% See the online documentation for the full list of available subject
-%% keywords and the rules for their use.
-\keywords{editorials, notices --- 
-miscellaneous --- catalogs --- surveys}
-
-%% From the front matter, we move on to the body of the paper.
-%% Sections are demarcated by \section and \subsection, respectively.
-%% Observe the use of the LaTeX \label
-%% command after the \subsection to give a symbolic KEY to the
-%% subsection for cross-referencing in a \ref command.
-%% You can use LaTeX's \ref and \label commands to keep track of
-%% cross-references to sections, equations, tables, and figures.
-%% That way, if you change the order of any elements, LaTeX will
-%% automatically renumber them.
-%%
-%% We recommend that authors also use the natbib \citep
-%% and \citet commands to identify citations.  The citations are
-%% tied to the reference list via symbolic KEYs. The KEY corresponds
-%% to the KEY in the \bibitem in the reference list below.
+\keywords{The Sun, Radio, XRay, EUV}
 
 \section{Introduction} \label{sec:intro}
+Our work is awesome, here's why
+\section{Observations} \label{sec:Obs}
+\subsection{IBIS}
+The IBIS data was reduced primarily using the pipeline code provided by NSO\footnote{Version 1.4, available here: https://www.nso.edu/telescopes/dunn-solar-telescope/dst-pipelines/}
 
-\latex\ \footnote{\url{http://www.latex-project.org/}} is a document markup
-language that is particularly well suited for the publication of
-mathematical and scientific articles \citep{lamport94}. \latex\ was written
-in 1985 by Leslie Lamport who based it on the \TeX\ typesetting language
-which itself was created by Donald E. Knuth in 1978.  In 1988 a suite of
-\latex\ macros were developed to investigate electronic submission and
-publication of AAS Journal articles \citep{1989BAAS...21..780H}.  Shortly
-afterwards, Chris Biemesdefer merged these macros and more into a \latex\
-2.08 style file called \aastex.  These early \aastex\ versions introduced
-many common commands and practices that authors take for granted today.
-Substantial revisions
-were made by Lee Brotzman and Pierre Landau when the package was updated to
-v4.0.  AASTeX v5.0, written in 1995 by Arthur Ogawa, upgraded to \latex\ 2e
-which uses the document class in lieu of a style file.  Other improvements
-to version 5 included hypertext support, landscape deluxetables and
-improved figure support to facilitate electronic submission.  
-\aastex\ v5.2 was released in 2005 and introduced additional graphics
-support plus new mark up to identifier astronomical objects, datasets and
-facilities.
+\subsection{ALMA}
 
-In 1996 Maxim Markevitch modified the AAS preprint style file, aaspp4.sty,
-to closely emulate the very tight, two column style of a typeset
-Astrophysical Journal article.  The result was emulateapj.sty.  A year
-later Alexey Vikhlinin took over development and maintenance.  In 2001 he
-converted emulateapj into a class file in \latex\ 2e and in 2003 Vikhlinin
-completely rewrote emulateapj based on the APS Journal's RevTEX class.
+\subsection{Hinode}
 
-During this time emulateapj gained growing acceptance in the astronomical
-community as it filled an author need to obtain an approximate number of
-manuscript pages prior to submission for cost and length estimates. The
-tighter typeset also had the added advantage of saving paper when printing
-out hard copies.
-
-Even though author publication charges are no longer based on print pages
-\footnote{see Section \ref{sec:pubcharge} in the Appendix for more details
-about how current article costs are calculated.} the emulateapj class file
-has proven to be extremely popular with AAS Journal authors.  An informal
-analysis of submitted \latex\ manuscripts in 2015 revealed that $\sim$65\%
-either called emulateapj or have a commented emulateapj classfile call
-indicating it was used at some stage of the manuscript construction.
-Clearly authors want to have access to a tightly typeset version of the
-article when corresponding with co-authors and for preprint submissions.
-
-When planning the next \aastex\ release the popularity of emulateapj played
-an important roll in the decision to drop the old base code and adopt and
-modify emulateapj for \aastex\ v6.+ instead.  The change brings \aastex\
-inline with what the majority of authors are already using while still
-delivering new and improved features.  \aastex\ v6.0 through v6.2 were written
-by Amy Hendrickson and released in January 2016 (v6.0), October 2016 (v6.1),
-and January 2018 (v6.2), respectively.  Some of the new features in v6.0 
-included:
-
-\begin{enumerate}
-\item improved citations for third party data repositories and software,
-\item easier construction of matrix figures consisting of multiple 
-encapsulated postscript (EPS) or portable document format (PDF) files,
-\item figure set mark up for large collections of similar figures,
-\item color mark up to easily enable/disable revised text highlighting,
-\item improved url support, and
-\item numerous table options such as the ability to hide columns, column 
-decimal alignment, automatic column math mode and numbering, plus splitting of
-wide tables.
-\end{enumerate}
-
-The features in v6.1 were:
-
-\begin{enumerate}
-\item ORCID support for preprints,
-\item improved author, affiliation and collaboration mark up,
-\item reintroduced the old AASTeX v5.2 {\tt\string\received}, 
-      {\tt\string\revised}, {\tt\string\accepted}, and
-      {\tt\string\published} commands plus
-      added the new {\tt\string\submitjournal} command to document
-      which AAS Journal the manuscript was submitted to, plus
-\item new typeset style options.
-\end{enumerate}
-
-The new features in v6.2 are:
-
-\begin{enumerate}
-\item A new RNAAS style option for Research Note manuscripts,
-\item Titles no longer put in all caps,
-\item No page skip between the title page and article body,
-\item re-introduce RevTeX's widetext environment for long lines in
-      two column style formats, and
-\item upgrade to the {\tt\string\doi} command.
-\end{enumerate}
-
-The rest of this article provides information and examples on how to create
-your own AAS Journal manuscript with v6.2.  Special emphasis is placed on
-how to use the full potential of \aastex\ v6+.  The next section describes
-the different manuscript styles available and how they differ from past
-releases.  Section \ref{sec:floats} describes how tables and figures are
-placed in a \latex\ document. Specific examples of tables, Section
-\ref{subsec:tables}, and figures, Section \ref{subsec:figures}, are also
-provided.  Section \ref{sec:displaymath} discusses how to display math and
-incorporate equations in a manuscript while Section \ref{sec:highlight}
-discuss how to use the new revision mark up.  The last section,
-\ref{sec:cite}, shows how recognize software and external data as first
-class references in the manuscript bibliography.  An appendix is included
-to show how to construct one and provide some information on how article
-charges are calculated.  Additional information is available both embedded
-in the comments of this \latex\ file and in the online documentation at
-\url{http://journals.aas.org/authors/aastex.html}.
-
-\section{Manuscript styles} \label{sec:style}
-
-The default style in \aastex\ v6.2 is a tight single column style, e.g.  10
-point font, single spaced.  The single column style is very useful for
-article with wide equations. It is also the easiest to style to work with
-since figures and tables, see Section \ref{sec:floats}, will span the
-entire page, reducing the need for address float sizing.
-
-To invoke a two column style similar to the what is produced in
-the published PDF copy use \\
-
-\noindent {\tt\string\documentclass[twocolumn]\{aastex62\}}. \\
-
-\noindent Note that in the two column style figures and tables will only
-span one column unless specifically ordered across both with the ``*'' flag,
-e.g. \\
-
-\noindent{\tt\string\begin\{figure*\}} ... {\tt\string\end\{figure*\}}, \\
-\noindent{\tt\string\begin\{table*\}} ... {\tt\string\end\{table*\}}, and \\
-\noindent{\tt\string\begin\{deluxetable*\}} ... {\tt\string\end\{deluxetable*\}}. \\
-
-\noindent This option is ignored in the onecolumn style.
-
-Some other style options are outlined in the commented sections of this 
-article.  Any combination of style options can be used.
-
-Two style options that are needed to fully use the new revision tracking
-feature, see Section \ref{sec:highlight}, are {\tt\string linenumbers} which 
-uses the lineno style file to number each article line in the left margin and 
-{\tt\string trackchanges} which controls the revision and commenting highlight
-output.
-
-There is also a new {\tt\string modern} option that uses a Daniel
-Foreman-Mackey and David Hogg design to produce stylish, single column
-output that has wider left and right margins. It is designed to have fewer
-words per line to improve reader retention. It also looks better on devices
-with smaller displays such as smart phones.
-
-For a Research Note use the {\tt\string RNAAS} option which will produce a
-manuscript with no abstract and in the {\tt\string modern} style.
-
-\section{Floats} \label{sec:floats}
-
-Floats are non-text items that generally can not be split over a page.
-They also have captions and can be numbered for reference.  Primarily these
-are figures and tables but authors can define their own. \latex\ tries to
-place a float where indicated in the manuscript but will move it later if
-there is not enough room at that location, hence the term ``float''.
-
-Authors are encouraged to embed their tables and figures within the text as
-they are mentioned.  Please do not place the figures and text at the end of
-the article as was the old practice.  Editors and the vast majority of
-referees find it much easier to read a manuscript with embedded figures and
-tables.
-
-Depending on the number of floats and the particular amount of text and
-equations present in a manuscript the ultimate location of any specific
-float can be hard to predict prior to compilation. It is recommended that
-authors textbf{not} spend significant time trying to get float placement
-perfect for peer review.  The AAS Journal's publisher has sophisticated
-typesetting software that will produce the optimal layout during
-production.
-
-Note that authors of Research Notes are only allowed one float, either one
-table or one figure.
+\section{Coalignment} \label{sec:coalign}
+Coaligning the various instruments was a challenge.  We did it like this:
 
@@
 
-For authors that do want to take the time to optimize the locations of
-their floats there are some techniques that can be used.  The simplest
-solution is to placing a float earlier in the text to get the position
-right but this option will break down if the manuscript is altered, see
-Table \ref{tab:table}.  A better method is to force \latex\ to place a
-float in a general area with the use of the optional {\tt\string [placement
-specifier]} parameter for figures and tables. This parameter goes after
-{\tt\string \begin\{figure\}}, {\tt\string \begin\{table\}}, and
-{\tt\string \begin\{deluxetable\}}.  The main arguments the specifier takes
-are ``h'', ``t'', ``b'', and ``!''.  These tell \latex\ to place the float
-\underline{h}ere (or as close as possible to this location as possible), at
-the \underline{t}op of the page, and at the \underline{b}ottom of the page.
-The last argument, ``!'', tells \latex\ to override its internal method of
-calculating the float position.  A sequence of rules can be created by
-using multiple arguments.  For example, {\tt\string \begin\{figure\}[htb!]}
-tells \latex\ to try the current location first, then the top of the page
-and finally the bottom of the page without regard to what it thinks the
-proper position should be.  Many of the tables and figures in this article
-use a placement specifier to set their positions.
-
-Note that the \latex\ {\tt\string tabular} environment is not a float.  Only
-when a {\tt\string tabular} is surrounded by {\tt\string\begin\{table\}} ...
-{\tt\string\end\{table\}} is it a true float and the rules and suggestions
-above apply.
-
-In AASTeX v6.2 all deluxetables are float tables and thus if they are
-longer than a page will spill off the bottom. Long deluxetables should
-begin with the {\tt\string\startlongtable} command. This initiates a
-longtable environment.  Authors might have to use {\tt\string\clearpage} to
-isolate a long table or optimally place it within the surrounding text.
-
-\begin{deluxetable*}{ccCrlc}[b!]
-\tablecaption{Column math mode in an observation log \label{tab:mathmode}}
-\tablecolumns{6}
-\tablenum{2}
-\tablewidth{0pt}
-\tablehead{
-\colhead{UT start time\tablenotemark{a}} &
-\colhead{MJD start time\tablenotemark{a}} &
-\colhead{Seeing} & \colhead{Filter} & \colhead{Inst.} \\
-\colhead{(YYYY-mm-dd)} & \colhead{(d)} &
-\colhead{(arcsec)} & \colhead{} & \colhead{}
-}
-\startdata
-2012-03-26 & 56012.997 & \sim 0.\arcsec5 & H$\alpha$ & NOT \\
-2012-03-27 & 56013.944 & 1.\arcsec5 & grism & SMARTS \\
-2012-03-28 & 56014.984 & \nodata & F814M & HST \\
-2012-03-30 & 56016.978 & 1.\arcsec5\pm0.25 & B\&C & Bok \\
-\enddata
-\tablenotetext{a}{At exposure start.}
-\tablecomments{The ``C'' command column identifier in the 3 column turns on
-math mode for that specific column. One could do the same for the next
-column so that dollar signs would not be needed for H$\alpha$
-but then all the other text would also be in math mode and thus typeset
-in Latin Modern math and you will need to put it back to Roman by hand.
-Note that if you do change this column to math mode the dollar signs already
-present will not cause a problem. Table \ref{tab:mathmode} is published 
-in its entirety in the machine readable format.  A portion is
-shown here for guidance regarding its form and content.}
-\end{deluxetable*}
-
-\subsection{Tables} \label{subsec:tables}
-
-Tables can be constructed with \latex's standard table environment or the
-\aastex's deluxetable environment. The deluxetable construct handles long
-tables better but has a larger overhead due to the greater amount of
-defined mark up used set up and manipulate the table structure.  The choice
-of which to use is up to the author.  Examples of both environments are
-used in this manuscript. Table \ref{tab:table} is a simple deluxetable
-example that gives the approximate changes in the subscription costs and
-author publication charges from 1991 to 2013.
-
-Tables longer than 200 data lines and complex tables should only have a
-short example table with the full data set available in the machine
-readable format.  The machine readable table will be available in the HTML
-version of the article with just a short example in the PDF. Authors are
-required to indicate to the reader where the data can be obtained in the
-table comments.  Suggested text is given in the comments of Table
-\ref{tab:mathmode}.  Authors are encouraged to create their own machine
-readable tables using the online tool at
-\url{http://authortools.aas.org/MRT/upload.html}.
-
-\aastex\ v6 introduces five new table features that are designed to make
-table construction easier and the resulting display better for AAS Journal
-authors.  The items are:
-
-\begin{enumerate}
-\item Declaring math mode in specific columns,
-\item Column decimal alignment, 
-\item Automatic column header numbering,
-\item Hiding columns, and
-\item Splitting wide tables into two or three parts.
-\end{enumerate}
-
-Each of these new features are illustrated in following Table examples.
-All five features work with the regular \latex\ tabular environment and in
-\aastex's deluxetable environment.  The examples in this manuscript also
-show where the two process differ.
-
-\subsubsection{Column math mode}
-
-Both the \latex\ tabular and \aastex\ deluxetable require an argument to
-define the alignment and number of columns.  The most common values are
-``c'', ``l'' and ``r'' for \underline{c}enter, \underline{l}eft, and
-\underline{r}ight justification.  If these values are capitalized, e.g.
-``C'', ``L'', or ``R'', then that specific column will automatically be in math
-mode meaning that \$s are not required.  Note that having embedded dollar
-signs in the table does not affect the output.  The third and forth columns
-of Table \ref{tab:mathmode} shows how this math mode works.
-
-\subsubsection{Decimal alignment}
-
-Aligning a column by the decimal point can be difficult with only center,
-left, and right justification options.  It is possible to use phantom calls
-in the data, e.g. {\tt\string\phn}, to align columns by hand but this can
-be tedious in long or complex tables.  To address this \aastex\ introduces
-the {\tt\string\decimals} command and a new column justification option,
-``D'', to align data in that column on the decimal.  In deluxetable the
-{\tt\string\decimals} command is invoked before the {\tt\string\startdata}
-call but can be anywhere in \latex's tabular environment.
-
-Two other important thing to note when using decimal alignment is that each
-decimal column \textit{must end with a space before the ampersand}, e.g.
-``\&\&'' is not allowed.  Empty decimal columns are indicated with a decimal,
-e.g. ``.''.  Do not use deluxetable's {\tt\string\nodata} command.
-
-The ``D'' alignment token works by splitting the column into two parts on the
-decimal.  While this is invisible to the user one must be aware of how it
-works so that the headers are accounted for correctly.  All decimal column
-headers need to span two columns to get the alignment correct. This can be
-done with a multicolumn call, e.g {\tt\string\multicolumn2c\{\}} or
-{\tt\string\multicolumn\{2\}\{c\}\{\}}, or use the new
-{\tt\string\twocolhead\{\}} command in deluxetable.  Since \latex\ is
-splitting these columns into two it is important to get the table width
-right so that they appear joined on the page.  You may have to run the
-\latex\ compiler twice to get it right.  Table \ref{tab:decimal}
-illustrates how decimal alignment works in the tabular environment with a
-$\pm$ symbol embedded between the last two columns.
-
-%% Note that the \setcounter and \renewcommand are needed here because
-%% this example is using a mix of deluxetable and tabular.  Here the
-%% deluxetable counters are set with \tablenum but the situation is a bit
-%% more complex for tabular.  Use the first command to set the Table number
-%% to ONE LESS than it should be.  The next command will auto increment it
-%% to the desired number.
-\setcounter{table}{2}
-\begin{table}[h!]
-\renewcommand{\thetable}{\arabic{table}}
-\centering
-\caption{Decimal alignment made easy} \label{tab:decimal}
-\begin{tabular}{cD@{$\pm$}D}
-\tablewidth{0pt}
-\hline
-\hline
-Column & \multicolumn2c{Value} & \multicolumn2c{Uncertainty}\\
-\hline
-\decimals
-A & 1234     & 100.0     \\
-B &  123.4   &  10.1     \\
-C &  12.34   &   1.01    \\
-D &   1.234  &   0.101   \\
-E &    .1234 &   0.01001 \\
-F &   1.0    &    .      \\
-\hline
-\multicolumn{5}{c}{NOTE. - Two decimal aligned columns}
-\end{tabular}
-\end{table}
-
-\subsubsection{Automatic column header numbering} \label{subsubsec:autonumber}
-
-The command {\tt\string\colnumbers} can be included to automatically number
-each column as the last row in the header. Per the AAS Journal table format
-standards, each column index numbers will be surrounded by parentheses. In
-a \latex\ tabular environment the {\tt\string\colnumbers} should be invoked
-at the location where the author wants the numbers to appear, e.g. after
-the last line of specified table header rows. In deluxetable this command
-has to come before {\tt\string\startdata}.  {\tt\string\colnumbers} will
-not increment for columns hidden by the ``h'' command, see Section
-\ref{subsubsec:hide}.  Table \ref{tab:table} uses this command to
-automatically generate column index numbers.
-
-Note that when using decimal alignment in a table the command 
-{\tt\string\decimalcolnumbers} must be used instead of 
-{\tt\string\colnumbers} and {\tt\string\decimals}. Table \ref{tab:messier}
-illustrates this specific functionality.
-
-\subsubsection{Hiding columns} \label{subsubsec:hide}
-
-Entire columns can be \underline{h}idden from display simply by changing
-the specified column identifier to ``h''.  In the \latex\ tabular environment
-this column identifier conceals the entire column including the header
-columns.   In \aastex's deluxetables the header row is specifically
-declared with the {\tt\string\tablehead} call and each header column is
-marked with {\tt\string\colhead} call.  In order to make a specific header
-disappear with the ``h'' column identifier in deluxetable use 
-{\tt\string\nocolhead} instead to suppress that particular column header.
-
-Authors can use this option in many different ways.  Since column data can
-be easily suppressed authors can include extra information and hid it
-based on the comments of co-authors or referees.  For wide tables that will
-have a machine readable version, authors could put all the information in
-the \latex\ table but use this option to hid as many columns as needed until
-it fits on a page. This concealed column table would serve as the
-example table for the full machine readable version.  Regardless of how
-columns are obscured, authors are responsible for removing any unneeded
-column data or alerting the editorial office about how to treat these
-columns during production for the final typeset article.
-
-Table \ref{tab:messier} provides some basic information about the first ten
-Messier Objects and illustrates how many of these new features can be used
-together.  It has automatic column numbering, decimal alignment of the
-distances, and one concealed column.  The Common name column
-is the third in the \latex\ deluxetable but does not appear when the article
-is compiled. This hidden column can be shown simply by changing the ``h'' in
-the column identifier preamble to another valid value.  This table also
-uses {\tt\string\tablenum} to renumber the table because a \latex\ tabular
-table was inserted before it.
-
-\begin{deluxetable*}{cchlDlc}
-\tablenum{4}
-\tablecaption{Fun facts about the first 10 messier objects\label{tab:messier}}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Messier} & \colhead{NGC/IC} & \nocolhead{Common} & \colhead{Object} &
-\multicolumn2c{Distance} & \colhead{} & \colhead{V} \\
-\colhead{Number} & \colhead{Number} & \nocolhead{Name} & \colhead{Type} &
-\multicolumn2c{(kpc)} & \colhead{Constellation} & \colhead{(mag)}
-}
-\decimalcolnumbers
-\startdata
-M1 & NGC 1952 & Crab Nebula & Supernova remnant & 2 & Taurus & 8.4 \\
-M2 & NGC 7089 & Messier 2 & Cluster, globular & 11.5 & Aquarius & 6.3 \\
-M3 & NGC 5272 & Messier 3 & Cluster, globular & 10.4 & Canes Venatici &  6.2 \\
-M4 & NGC 6121 & Messier 4 & Cluster, globular & 2.2 & Scorpius & 5.9 \\
-M5 & NGC 5904 & Messier 5 & Cluster, globular & 24.5 & Serpens & 5.9 \\
-M6 & NGC 6405 & Butterfly Cluster & Cluster, open & 0.31 & Scorpius & 4.2 \\
-M7 & NGC 6475 & Ptolemy Cluster & Cluster, open & 0.3 & Scorpius & 3.3 \\
-M8 & NGC 6523 & Lagoon Nebula & Nebula with cluster & 1.25 & Sagittarius & 6.0 \\
-M9 & NGC 6333 & Messier 9 & Cluster, globular & 7.91 & Ophiuchus & 8.4 \\
-M10 & NGC 6254 & Messier 10 & Cluster, globular & 4.42 & Ophiuchus & 6.4 \\
-\enddata
-\tablecomments{This table ``hides'' the third column in the \latex\ when compiled.
-The Distance is also centered on the decimals.  Note that when using decimal
-alignment you need to include the {\tt\string\decimals} command before
-{\tt\string\startdata} and all of the values in that column have to have a
-space before the next ampersand.}
-\end{deluxetable*}
-
-\subsubsection{Splitting a table into multiple horizontal components}
-
-Since the AAS Journals are now all electronic with no print version there is
-no reason why tables can not be as wide as authors need them to be.
-However, there are some artificial limitations based on the width of a
-print page.  The old way around this limitation was to rotate into 
-landscape mode and use the smallest available table font
-sizes, e.g. {\tt\string\tablewidth}, to get the table to fit.
-Unfortunately, this was not alway enough but now along with the hide column
-option outlined in Section \ref{subsubsec:hide} there is a new way to break
-a table into two or three components so that it flows down a page by
-invoking a new table type, splittabular or splitdeluxetable. Within these
-tables a new ``B'' column separator is introduced.  Much like the vertical
-bar option, ``$\vert$'', that produces a vertical table lines, e.g. Table
-\ref{tab:table}, the new ``B'' separator indicates where to \underline{B}reak
-a table.  Up to two ``B''s may be included.
-
-Table 5 % \ref{tab:deluxesplit} this freaks it out when it is used!
-shows how to split a wide deluxetable into three parts with
-the {\tt\string\splitdeluxetable} command.  The {\tt\string\colnumbers}
-option is on to show how the automatic column numbering carries through the
-second table component, see Section \ref{subsubsec:autonumber}.
-
-The last example, Table \ref{tab:tablesplit}, shows how to split the same
-table but with a regular \latex\ tabular call and into two parts. Decimal
-alignment is included in the third column and the ``Component'' column is
-hidden to illustrate the new features working together.
-
-\begin{splitdeluxetable*}{lccccBcccccBcccc}
-\tabletypesize{\scriptsize}
-\tablewidth{0pt} 
-\tablenum{5}
-\tablecaption{Measurements of Emission Lines: two breaks \label{tab:deluxesplit}}
-\tablehead{
-\colhead{Model} & \colhead{Component}& \colhead{Shift} & \colhead{FWHM} &
-\multicolumn{10}{c}{Flux} \\
-\colhead{} & \colhead{} & \colhead{($\rm
-km~s^{-1}$)}& \colhead{($\rm km~s^{-1}$)} & \multicolumn{10}{c}{($\rm
-10^{-17}~erg~s^{-1}~cm^{-2}$)} \\
-\cline{5-14}
-\colhead{} & \colhead{} &
-\colhead{} & \colhead{} & \colhead{Ly$\alpha$} & \colhead{N\,{\footnotesize
-V}} & \colhead{Si\,{\footnotesize IV}} & \colhead{C\,{\footnotesize IV}} &
-\colhead{Mg\,{\footnotesize II}} & \colhead{H$\gamma$} & \colhead{H$\beta$}
-& \colhead{H$\alpha$} & \colhead{He\,{\footnotesize I}} &
-\colhead{Pa$\gamma$}
-} 
-\colnumbers
-\startdata 
-{       }& BELs& -97.13 &    9117$\pm      38$&    1033$\pm      33$&$< 35$&$<     166$&     637$\pm      31$&    1951$\pm      26$&     991$\pm 30$&    3502$\pm      42$&   20285$\pm      80$&    2025$\pm     116$& 1289$\pm     107$\\
-{Model 1}& IELs& -4049.123 & 1974$\pm      22$&    2495$\pm      30$&$<     42$&$<     109$&     995$\pm 186$&      83$\pm      30$&      75$\pm      23$&     130$\pm      25$& 357$\pm      94$&     194$\pm      64$& 36$\pm      23$\\
-{       }& NELs& \nodata &     641$\pm       4$&     449$\pm 23$&$<      6$&$<       9$&       --            &     275$\pm      18$& 150$\pm      11$&     313$\pm      12$&     958$\pm      43$&     318$\pm 34$& 151$\pm       17$\\
-\hline
-{       }& BELs& -85 &    8991$\pm      41$& 988$\pm      29$&$<     24$&$<     173$&     623$\pm      28$&    1945$\pm 29$&     989$\pm      27$&    3498$\pm      37$&   20288$\pm      73$& 2047$\pm     143$& 1376$\pm     167$\\
-{Model 2}& IELs& -51000 &    2025$\pm      26$& 2494$\pm      32$&$<     37$&$<     124$&    1005$\pm     190$&      72$\pm 28$&      72$\pm      21$&     113$\pm      18$&     271$\pm      85$& 205$\pm      72$& 34$\pm      21$\\
-{       }& NELs& 52 &     637$\pm      10$&     477$\pm 17$&$<      4$&$<       8$&       --            &     278$\pm      17$& 153$\pm      10$&     317$\pm      15$&     969$\pm      40$&     325$\pm 37$&
-     147$\pm       22$\\
-\enddata
-\tablecomments{This is an example of how to split a deluxetable. You can
-split any table with this command into two or three parts.  The location of
-the split is given by the author based on the placement of the ``B''
-indicators in the column identifier preamble.  For more information please
-look at the new \aastex\ instructions.}
-\end{splitdeluxetable*}
-
-%\clearpage
-
-\setcounter{table}{5}
-\begin{table*}[h!]
-\renewcommand{\thetable}{\arabic{table}}
-\caption{Measurements of Emission Lines: one break\label{tab:tablesplit}}
-\begin{splittabular}{lhDccccBccccccc}
-%\multicolumn{5}{c}{Table 6} \\
-%\multicolumn{5}{c}{Measurements of Emission Lines} \\
-\hline 
-\hline 
-Model & Component & \multicolumn2c{Shift} & FWHM & 
-\multicolumn{10}{c}{Flux} \\
- & & \multicolumn2c{($\rm km~s^{-1}$)} & {($\rm km~s^{-1}$)} & 
-\multicolumn{10}{c}{($\rm 10^{-17}~erg~s^{-1}~cm^{-2}$)} \\
-\cline{5-15}
- & & & & & {Ly$\alpha$} & {N\,{\footnotesize V}} & 
-{Si\,{\footnotesize IV}} & {C\,{\footnotesize IV}} &
-{Mg\,{\footnotesize II}} & {H$\gamma$} & {H$\beta$}
-& {H$\alpha$} & {He\,{\footnotesize I}} & {Pa$\gamma$} \\
-%\hline
-\decimalcolnumbers
- & BELs& -97.13 &    9117$\pm      38$&    1033$\pm      33$&$< 35$&$<     166$&     637$\pm      31$&    1951$\pm      26$&     991$\pm 30$&    3502$\pm      42$&   20285$\pm      80$&    2025$\pm     116$& 1289$\pm     107$\\
-Model 1 & IELs& -4049.123 & 1974$\pm      22$&    2495$\pm      30$&$<     42$&$<     109$&     995$\pm 186$&      83$\pm      30$&      75$\pm      23$&     130$\pm      25$& 357$\pm      94$&     194$\pm      64$& 36$\pm      23$\\
- & NELs& .
-&     641$\pm       4$&     449$\pm 23$&$<      6$&$<       9$&       --            &     275$\pm      18$& 150$\pm      11$&     313$\pm      12$&     958$\pm      43$&     318$\pm 34$& 151$\pm       17$\\
-\hline
- & BELs& -85 &    8991$\pm      41$& 988$\pm      29$&$<     24$&$<     173$&     623$\pm      28$&    1945$\pm 29$&     989$\pm      27$&    3498$\pm      37$&   20288$\pm      73$& 2047$\pm     143$& 1376$\pm     167$\\
-Model 2 & IELs& -51000 &    2025$\pm      26$& 2494$\pm      32$&$<     37$&$<     124$&    1005$\pm     190$&      72$\pm 28$&      72$\pm      21$&     113$\pm      18$&     271$\pm      85$& 205$\pm      72$& 34$\pm      21$\\
- & NELs& 52 &     637$\pm      10$&     477$\pm 17$&$<      4$&$<       8$&       --            &     278$\pm      17$& 153$\pm      10$&     317$\pm      15$&     969$\pm      40$&     325$\pm 37$& 147$\pm       22$\\
-\hline
-\end{splittabular}
-\end{table*}
-
-\subsection{Figures\label{subsec:figures}}
-
-%% The "ht!" tells LaTeX to put the figure "here" first, at the "top" next
-%% and to override the normal way of calculating a float position
-\begin{figure}[ht!]
-\plotone{cost-eps-converted-to.pdf}
-\caption{The subscription and author publication costs from 1991 to 2013.
-The data comes from Table \ref{tab:table}.\label{fig:general}}
-\end{figure}
-
-Authors can include a wide number of different graphics with their articles
-in  encapsulated postscript (EPS) or portable document format (PDF).  These
-range from general figures all authors are familiar with to new enhanced
-graphics that can only be fully experienced in HTML.  The later include
-animations, figure sets and interactive figures.  This portion of the
-article provides examples for setting up all these graphics in with the
-latest version of \aastex.
-
-\subsection{General figures\label{subsec:general}}
-
-\aastex\ has a {\tt\string\plotone} command to display a figure
-consisting of one EPS/PDF file.  Figure \ref{fig:general} is an example
-which uses the data from Table \ref{tab:table}. For a general figure
-consisting of two EPS/PDF files the {\tt\string\plottwo} command can be
-used to position the two image files side by side.  Figure \ref{fig:f2}
-shows the Swift/XRT X-ray light curves of two recurrent novae.  The data
-from Figures \ref{fig:f2} through \ref{fig:fig4} are taken from Table 2 of
-\citet{2011ApJS..197...31S}.
-
-\begin{figure}
-\plottwo{RS_Oph-eps-converted-to.pdf}{U_Sco-eps-converted-to.pdf}
-\caption{Swift/XRT X-ray light curves of RS Oph and U Sco which represent
-the two canonical recurrent types, a long period system with a red giant
-secondary and a short period system with a dwarf/sub-dwarf secondary,
-respectively.\label{fig:f2}}
-\end{figure}
-
-Both {\tt\string\plotone} and {\tt\string\plottwo} take a
-{\tt\string\caption} and an optional {\tt\string\figurenum} command to
-specify the figure number\footnote{It is better to not use
-{\tt\string\figurenum} and let LaTeX auto-increment all the figures. If you
-do use this command you need to mark all of them accordingly.}.  Each is
-based on the {\tt\string graphicx} package command,
-{\tt\string\includegraphics}.  Authors are welcome to use
-{\tt\string\includegraphics} along with its optional arguments that control
-the height, width, scale, and position angle of a file within the figure.
-More information on the full usage of {\tt\string\includegraphics} can be
-found at \break
-\url{https://en.wikibooks.org/wiki/LaTeX/Importing\_Graphics\#Including\_graphics}.
-
-\subsection{Grid figures}
-
-Including more than two EPS/PDF files in a single figure call can be tricky
-easily format.  To make the process easier for authors \aastex\ v6 offers
-{\tt\string\gridline} which allows any number of individual EPS/PDF file
-calls within a single figure.  Each file cited in a {\tt\string\gridline}
-will be displayed in a row.  By adding more {\tt\string\gridline} calls an
-author can easily construct a matrix X by Y individual files as a
-single general figure.
-
-For each {\tt\string\gridline} command a EPS/PDF file is called by one of
-four different commands.  These are {\tt\string\fig},
-{\tt\string\rightfig}, {\tt\string\leftfig}, and {\tt\string\boxedfig}.
-The first file call specifies no image position justification while the
-next two will right and left justify the image, respectively.  The
-{\tt\string\boxedfig} is similar to {\tt\string\fig} except that a box is
-drawn around the figure file when displayed. Each of these commands takes
-three arguments.  The first is the file name.  The second is the width that
-file should be displayed at.  While any natural \latex\ unit is allowed, it
-is recommended that author use fractional units with the
-{\tt\string\textwidth}.  The last argument is text for a subcaption.
-
-Figure \ref{fig:pyramid} shows an inverted pyramid of individual
-figure constructed with six individual EPS files using the
-{\tt\string\gridline} option.
-
-\begin{figure*}
-\gridline{\fig{V2491_Cyg-eps-converted-to.pdf}{0.3\textwidth}{(a)}
-          \fig{CSS081007-eps-converted-to.pdf}{0.3\textwidth}{(b)}
-          \fig{LMC_2009-eps-converted-to.pdf}{0.3\textwidth}{(c)}
-          }
-\gridline{\fig{RS_Oph-eps-converted-to.pdf}{0.3\textwidth}{(d)}
-          \fig{U_Sco-eps-converted-to.pdf}{0.3\textwidth}{(e)}
-          }
-\gridline{\fig{KT_Eri-eps-converted-to.pdf}{0.3\textwidth}{(f)}}
-\caption{Inverted pyramid figure of six individual files. The nova are
-(a) V2491 Cyg, (b) HV Cet, (c) LMC 2009, (d) RS Oph, (e) U Sco, and
-(f) KT Eri.\label{fig:pyramid}}
-\end{figure*}
-
-\subsection{Figure sets}
-
-A large collection of similar style figures should be grouped together as a
-figure set.  The derived PDF article will only shows an example figure
-while the enhanced content is available in the figure set in the electronic
-edition.  The advantage of a figure set gives the reader the ability to
-easily sort through the figure collection to find individual component
-figures.  All of the figure set components, along with their html framework,
-are also available for download in a .tar.gz package.
-
-Special \latex\ mark up is required to create a figure set.  Prior to
-\aastex\ v6 the underlying mark up commands had to be inserted by hand
-but is now included.  Note that when an article with figure set is compiled
-in \latex\ none of the component figures are shown and a floating Figure
-Set caption will appear in the resulting PDF.
-
-\figsetstart
-\figsetnum{4}
-\figsettitle{Swift X-ray light curves}
-
-\figsetgrpstart
-\figsetgrpnum{1.1}
-\figsetgrptitle{KT Eri}
-\figsetplot{KT_Eri-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.2}
-\figsetgrptitle{RS Oph}
-\figsetplot{RS_Oph-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.3}
-\figsetgrptitle{U Sco}
-\figsetplot{U_Sco-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.4}
-\figsetgrptitle{V2491 Cyg}
-\figsetplot{V2491_Cyg-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.5}
-\figsetgrptitle{Nova LMC 2009}
-\figsetplot{LMC_2009-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.6}
-\figsetgrptitle{HV Cet}
-\figsetplot{CSS081007-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.7}
-\figsetgrptitle{V2672 Oph}
-\figsetplot{V2672_Oph-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.8}
-\figsetgrptitle{V407 Cyg}
-\figsetplot{V407_Cyg-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetend
-
-\begin{figure}
-\plotone{KT_Eri-eps-converted-to.pdf}
-\caption{The Swift/XRT X-ray light curve for the first year after
-outburst of the suspected recurrent nova KT Eri. At a maximum count rate of 
-328 ct/s, KT Eri was the brightest nova in X-rays observed to date. All 
-the component figures are available in the Figure Set. \label{fig:fig4}}
-\end{figure}
-
-Authors are encouraged to use an online tool at
-\url{http://authortools.aas.org/FIGSETS/make-figset.html} to generate their
-own specific figure set mark up to incorporate into their \latex\ articles.
-
-\subsection{Animations}
-
-Authors may include animations in their articles.  A single still frame from 
-the animation should be included as a regular figure to serve as an example.
-The associated figure caption should indicate to the reader exactly what the
-animation shows and that the animation is available online.
-
-\begin{figure}
-\plotone{video3-eps-converted-to.pdf}
-\caption{Example image from the animation which is available in the electronic
-edition.}
-\end{figure}
-
-\subsection{Interactive figures}
-
-Interactive figures give the reader the ability to manipulate the
-information contained in an image which can add clarity or help further the
-author's narrative.  These figures consist of two parts, the figure file in
-a specific format and a javascript and html frame work that provides the
-interactive control.  An example of an interactive figure is a 3D model.
-The underlying figure is a X3D file while x3dom.js is the javascript driver
-that displays it. An author created interface is added via a html wrapper.
-The first 3D model published by the AAS Journals using this technique was
-\citet{2014ApJ...793..127V}.  Authors should consult the online tutorials
-for more information on how to construct their own interactive figures.
-
-As with animations authors should include a non-interactive regular figure
-to use as an example.  The example figure should also indicate to the reader
-that the enhanced figure is interactive and can be accessed online.
-
 \section{Displaying mathematics} \label{sec:displaymath}
-
-The most common mathematical symbols and formulas are in the amsmath
-package.  \aastex\ requires this package so there is no need to
-specifically call for it in the document preamble.  Most modern \latex\
-distributions already contain this package.  If you do not have this
-package or the other required packages, revtex4-1, latexsym, graphicx,
-amssymb, longtable, and epsf, they can be obtained from 
-\url{http://www.ctan.org}
-
-Mathematics can be displayed either within the text, e.g. $E = mc^2$, or
-separate from in an equation.  In order to be properly rendered, all inline
-math text has to be declared by surrounding the math by dollar signs (\$).
-
-A complex equation example with inline math as part of the explanation
-follows.
-
-\begin{equation}
-\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
-\hat a_nu(p_1,\sigma_1) ,
-\end{equation}
-where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
-and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
-and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
-operator $(\tau = \pm1)$.  This produces a single line formula.  \latex\ will
-auto-number this and any subsequent equations.  If no number is desired then
-the {\tt\string equation} call should be replaced with {\tt\string displaymath}.
-
-\latex\ can also handle a a multi-line equation.  Use {\tt\string eqnarray}
-for more than one line and end each line with a
-\textbackslash\textbackslash.  Each line will be numbered unless the
-\textbackslash\textbackslash\ is preceded by a {\tt\string\nonumber}
-command.  Alignment points can be added with ampersands (\&).  There should be
-two ampersands per line. In the examples they are centered on the equal
-symbol.
-
-\begin{eqnarray}
-\gamma^\mu  & = &
- \left(
-\begin{array}{cc}
-0 & \sigma^\mu_+ \\
-\sigma^\mu_- & 0
-\end{array}     \right) ,
- \gamma^5= \left(
-\begin{array}{cc}
--1 &   0\\
-0 &   1
-\end{array}     \right)  , \\
-\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , 
-\end{eqnarray}
-
-\begin{eqnarray}
-\hat a & = & \left(
-\begin{array}{cc}
-0 & (\hat a)_+\\
-(\hat a)_- & 0
-\end{array}\right), \nonumber \\
-(\hat a)_\pm & = & a_\mu\sigma^\mu_\pm 
-\end{eqnarray}
-
-%% Putting eqnarrays or equations inside the mathletters environment groups
-%% the enclosed equations by letter. For instance, the eqnarray below, instead
-%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
-%% LaTeX the paper and look at the output to see the results.
 
@@
 
-\citet{2015ApJ...805...23C} provides a example of how the citation in the
-article references the external code at
-\doi{10.5281/zenodo.15991}.  Unfortunately, bibtex does
-not have specific bibtex entries for these types of references so the
-``@misc'' type should be used.  The Repository tutorial explains how to
-code the ``@misc'' type correctly.  The most recent aasjournal.bst file,
-available with \aastex\ v6, will output bibtex ``@misc'' type properly.
-
 %% If you wish to include an acknowledgments section in your paper,
@@
 
-\software{astropy \citep{2013A&A...558A..33A},  
-          Cloudy \citep{2013RMxAA..49..137F}, 
-          SExtractor \citep{1996A&AS..117..393B}
+\software{astropy \citep{2013A&A...558A..33A}
           }
@@
 
-Appendices can be broken into separate sections just like in the main text.
-The only difference is that each appendix section is indexed by a letter
-(A, B, C, etc.) instead of a number.  Likewise numbered equations have
-the section letter appended.  Here is an equation as an example.
-
-\begin{equation}
-I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
-\end{equation}
-
-Appendix tables and figures should not be numbered like equations. Instead
-they should continue the sequence from the main article body.
-
-\section{Author publication charges} \label{sec:pubcharge}
-
-Finally some information about the AAS Journal's publication charges.
-In April 2011 the traditional way of calculating author charges based on 
-the number of printed pages was changed.  The reason for the change
-was due to a recognition of the growing number of article items that could not 
-be represented in print. Now author charges are determined by a number of
-digital ``quanta''.  A single quantum is 350 words, one figure, one table,
-and one enhanced digital item.  For the latter this includes machine readable
-tables, figure sets, animations, and interactive figures.  The current cost
-is \$27 per word quantum and \$30 for all other quantum type.
-
-\section{Rotating tables} \label{sec:rotate}
-
-The process of rotating tables into landscape mode is slightly different in
-\aastex v6.2. Instead of the {\tt\string\rotate} command, a new environment
-has been created to handle this task. To place a single page table in a
-landscape mode start the table portion with
-{\tt\string\begin\{rotatetable\}} and end with
-{\tt\string\end\{rotatetable\}}.
-
-Tables that exceed a print page take a slightly different environment since
-both rotation and long table printing are required. In these cases start
-with {\tt\string\begin\{longrotatetable\}} and end with
-{\tt\string\end\{longrotatetable\}}. Table \ref{chartable} is an
-example of a multi-page, rotated table.
-
-\begin{longrotatetable}
-\begin{deluxetable*}{lllrrrrrrll}
-\tablecaption{Observable Characteristics of 
-Galactic/Magellanic Cloud novae with X-ray observations\label{chartable}}
-\tablewidth{700pt}
-\tabletypesize{\scriptsize}
-\tablehead{
-\colhead{Name} & \colhead{V$_{max}$} & 
-\colhead{Date} & \colhead{t$_2$} & 
-\colhead{FWHM} & \colhead{E(B-V)} & 
-\colhead{N$_H$} & \colhead{Period} & 
-\colhead{D} & \colhead{Dust?} & \colhead{RN?} \\ 
-\colhead{} & \colhead{(mag)} & \colhead{(JD)} & \colhead{(d)} & 
-\colhead{(km s$^{-1}$)} & \colhead{(mag)} & \colhead{(cm$^{-2}$)} &
-\colhead{(d)} & \colhead{(kpc)} & \colhead{} & \colhead{}
-} 
-\startdata
-CI Aql & 8.83 (1) & 2451665.5 (1) & 32 (2) & 2300 (3) & 0.8$\pm0.2$ (4) & 1.2e+22 & 0.62 (4) & 6.25$\pm5$ (4) & N & Y \\
-{\bf CSS081007} & \nodata & 2454596.5 & \nodata & \nodata & 0.146 & 1.1e+21 & 1.77 (5) & 4.45$\pm1.95$ (6) & \nodata & \nodata \\
-GQ Mus & 7.2 (7) & 2445352.5 (7) & 18 (7) & 1000 (8) & 0.45 (9) & 3.8e+21  & 0.059375 (10) & 4.8$\pm1$ (9) & N (7) & \nodata \\
-IM Nor & 7.84 (11) & 2452289 (2) & 50 (2) & 1150 (12) & 0.8$\pm0.2$ (4) & 8e+21 & 0.102 (13) & 4.25$\pm3.4$ (4) & N & Y \\
-{\bf KT Eri} & 5.42 (14) & 2455150.17 (14) & 6.6 (14) & 3000 (15) & 0.08 (15) & 5.5e+20 & \nodata & 6.5 (15) & N & M \\
-{\bf LMC 1995} & 10.7 (16) & 2449778.5 (16) & 15$\pm2$ (17) & \nodata & 0.15 (203) & 7.8e+20  & \nodata & 50 & \nodata & \nodata \\
-LMC 2000 & 11.45 (18) & 2451737.5 (18) & 9$\pm2$ (19) & 1700 (20) & 0.15 (203) & 7.8e+20  & \nodata & 50 & \nodata & \nodata \\
-{\bf LMC 2005} & 11.5 (21) & 2453700.5 (21) & 63 (22) & 900 (23) & 0.15 (203) & 1e+21 & \nodata & 50  & M (24) & \nodata \\
-{\bf LMC 2009a} & 10.6 (25) & 2454867.5 (25) & 4$\pm1$  & 3900 (25) & 0.15 (203)  & 5.7e+20 & 1.19 (26) & 50 & N & Y \\
-{\bf SMC 2005} & 10.4 (27) & 2453588.5 (27) & \nodata & 3200 (28) & \nodata & 5e+20  & \nodata & 61 & \nodata & \nodata \\
-{\bf QY Mus} & 8.1 (29) & 2454739.90 (29) & 60:  & \nodata & 0.71 (30) & 4.2e+21  & \nodata & \nodata & M & \nodata \\
-{\bf RS Oph} & 4.5 (31) & 2453779.44 (14) & 7.9 (14) & 3930 (31) & 0.73 (32) & 2.25e+21 & 456 (33) & 1.6$\pm0.3$ (33) & N (34) & Y \\
-{\bf U Sco} & 8.05 (35) & 2455224.94 (35) & 1.2 (36) & 7600 (37) & 0.2$\pm0.1$ (4) & 1.2e+21 & 1.23056 (36) & 12$\pm2$ (4) & N & Y \\
-{\bf V1047 Cen} & 8.5 (38) & 2453614.5 (39) & 6 (40) & 840 (38) & \nodata & 1.4e+22  & \nodata & \nodata & \nodata & \nodata \\
-{\bf V1065 Cen} & 8.2 (41) & 2454123.5 (41) & 11 (42) & 2700 (43) & 0.5$\pm0.1$ (42) & 3.75e+21 & \nodata & 9.05$\pm2.8$ (42) & Y (42) & \nodata \\
-V1187 Sco & 7.4 (44) & 2453220.5 (44) & 7: (45) & 3000 (44) & 1.56 (44) & 8.0e+21 & \nodata & 4.9$\pm0.5$ (44) & N & \nodata \\
-{\bf V1188 Sco} & 8.7 (46) & 2453577.5 (46) & 7 (40) & 1730 (47) & \nodata & 5.0e+21  & \nodata & 7.5 (39) & \nodata & \nodata \\
-{\bf V1213 Cen} & 8.53 (48) & 2454959.5 (48) & 11$\pm2$ (49) & 2300 (50) & 2.07 (30) & 1.0e+22 & \nodata & \nodata & \nodata & \nodata \\
-{\bf V1280 Sco} & 3.79 (51) & 2454147.65 (14) & 21 (52) & 640 (53) & 0.36 (54) & 1.6e+21  & \nodata & 1.6$\pm0.4$ (54) & Y (54) & \nodata \\
-{\bf V1281 Sco} & 8.8 (55) & 2454152.21 (55) & 15:& 1800 (56) & 0.7 (57) & 3.2e+21 & \nodata & \nodata & N & \nodata \\
-{\bf V1309 Sco} & 7.1 (58) & 2454714.5 (58) & 23$\pm2$ (59) & 670 (60) & 1.2 (30) & 4.0e+21 & \nodata & \nodata & \nodata & \nodata \\
-{\bf V1494 Aql} & 3.8 (61) & 2451515.5 (61) & 6.6$\pm0.5$ (61) & 1200 (62) & 0.6 (63) & 3.6e+21  & 0.13467 (64) & 1.6$\pm0.1$ (63) & N & \nodata \\
-{\bf V1663 Aql} & 10.5 (65) & 2453531.5 (65) & 17 (66) & 1900 (67) & 2: (68) & 1.6e+22  & \nodata & 8.9$\pm3.6$ (69) & N & \nodata \\
-V1974 Cyg & 4.3 (70) & 2448654.5 (70) & 17 (71) & 2000 (19) & 0.36$\pm0.04$ (71) & 2.7e+21  & 0.081263 (70) & 1.8$\pm0.1$ (72) & N & \nodata \\
-{\bf V2361 Cyg} & 9.3 (73) & 2453412.5 (73) & 6 (40) & 3200 (74) & 1.2: (75) & 7.0e+21 & \nodata & \nodata & Y (40) & \nodata \\
-{\bf V2362 Cyg} & 7.8 (76) & 2453831.5 (76) & 9 (77) & 1850 (78) & 0.575$\pm0.015$ (79) & 4.4e+21  & 0.06577 (80) & 7.75$\pm3$ (77) & Y (81) & \nodata \\
-{\bf V2467 Cyg} & 6.7 (82) & 2454176.27 (82) & 7 (83) & 950 (82) & 1.5 (84) & 1.4e+22  & 0.159 (85) & 3.1$\pm0.5$ (86) & M (87) & \nodata \\
-{\bf V2468 Cyg} & 7.4 (88) & 2454534.2 (88) & 10: & 1000 (88) & 0.77 (89) & 1.0e+22  & 0.242 (90) & \nodata & N & \nodata \\
-{\bf V2491 Cyg} & 7.54 (91) & 2454567.86 (91) & 4.6 (92) & 4860 (93) & 0.43 (94) & 4.7e+21  & 0.09580: (95) & 10.5 (96) & N & M \\
-V2487 Oph & 9.5 (97) & 2450979.5 (97) & 6.3 (98) & 10000 (98) & 0.38$\pm0.08$ (98) & 2.0e+21 & \nodata & 27.5$\pm3$ (99) & N (100) & Y (101) \\
-{\bf V2540 Oph} & 8.5 (102) & 2452295.5 (102) & \nodata & \nodata & \nodata & 2.3e+21 & 0.284781 (103) & 5.2$\pm0.8$ (103) & N & \nodata \\
-V2575 Oph & 11.1 (104) & 2453778.8 (104) & 20: & 560 (104) & 1.4 (105) & 3.3e+21 & \nodata & \nodata & N (105) & \nodata \\
-{\bf V2576 Oph} & 9.2 (106) & 2453832.5 (106) & 8: & 1470 (106) & 0.25 (107) & 2.6e+21  & \nodata & \nodata & N & \nodata \\
-{\bf V2615 Oph} & 8.52 (108) & 2454187.5 (108) & 26.5 (108) & 800 (109) & 0.9 (108) & 3.1e+21  & \nodata & 3.7$\pm0.2$ (108) & Y (110) & \nodata \\
-{\bf V2670 Oph} & 9.9 (111) & 2454613.11 (111) & 15: & 600 (112) & 1.3: (113) & 2.9e+21  & \nodata & \nodata & N (114) & \nodata \\
-{\bf V2671 Oph} & 11.1 (115) & 2454617.5 (115) & 8: & 1210 (116) & 2.0 (117) & 3.3e+21  & \nodata & \nodata & M (117) & \nodata \\
-{\bf V2672 Oph} & 10.0 (118) & 2455060.02 (118) & 2.3 (119) & 8000 (118) & 1.6$\pm0.1$ (119) & 4.0e+21  & \nodata & 19$\pm2$ (119) & \nodata & M \\
-V351 Pup & 6.5 (120) & 2448617.5 (120) & 16 (121) & \nodata & 0.72$\pm0.1$ (122) & 6.2e+21 & 0.1182 (123) & 2.7$\pm0.7$ (122) & N & \nodata \\
-{\bf V382 Nor} & 8.9 (124) & 2453447.5 (124) & 12 (40) & 1850 (23) & \nodata & 1.7e+22 & \nodata & \nodata & \nodata & \nodata \\
-V382 Vel & 2.85 (125) & 2451320.5 (125) & 4.5 (126) & 2400 (126) & 0.05: (126) & 3.4e+21  & 0.146126 (127) & 1.68$\pm0.3$ (126) & N & \nodata \\
-{\bf V407 Cyg} & 6.8 (128) & 2455266.314 (128) & 5.9 (129) & 2760 (129) & 0.5$\pm0.05$ (130) & 8.8e+21 & 15595 (131) & 2.7 (131) & \nodata & Y \\
-{\bf V458 Vul} & 8.24 (132) & 2454322.39 (132) & 7 (133) & 1750 (134) & 0.6 (135) & 3.6e+21 & 0.06812255 (136) & 8.5$\pm1.8$ (133) & N (135) & \nodata \\
-{\bf V459 Vul} & 7.57 (137) & 2454461.5 (137) & 18 (138) & 910 (139) & 1.0 (140) & 5.5e+21  & \nodata & 3.65$\pm1.35$ (138) & Y (140) & \nodata \\
-V4633 Sgr & 7.8 (141) & 2450895.5 (141) & 19$\pm3$ (142) & 1700 (143) & 0.21 (142) & 1.4e+21  & 0.125576 (144) & 8.9$\pm2.5$ (142) & N & \nodata \\
-{\bf V4643 Sgr} & 8.07 (145) & 2451965.867 (145) & 4.8 (146) & 4700 (147) & 1.67 (148) & 1.4e+22 & \nodata & 3 (148) & N & \nodata \\
-{\bf V4743 Sgr} & 5.0 (149) & 2452537.5 (149) & 9 (150) & 2400 (149) & 0.25 (151) & 1.2e+21 & 0.281 (152) & 3.9$\pm0.3$ (151) & N & \nodata \\
-{\bf V4745 Sgr} & 7.41 (153) & 2452747.5 (153) & 8.6 (154) & 1600 (155) & 0.1 (154) & 9.0e+20  & 0.20782 (156) & 14$\pm5$ (154) & \nodata & \nodata \\
-{\bf V476 Sct} & 10.3 (157) & 2453643.5 (157) & 15 (158) & \nodata & 1.9 (158) & 1.2e+22  & \nodata & 4$\pm1$ (158) & M (159) & \nodata \\
-{\bf V477 Sct} & 9.8 (160) & 2453655.5 (160) & 3 (160) & 2900 (161) & 1.2: (162) & 4e+21  & \nodata & \nodata & M (163) & \nodata \\
-{\bf V5114 Sgr} & 8.38 (164) & 2453081.5 (164) & 11 (165) & 2000 (23) & \nodata & 1.5e+21  & \nodata & 7.7$\pm0.7$ (165) & N (166) & \nodata \\
-{\bf V5115 Sgr} & 7.7 (167) & 2453459.5 (167) & 7 (40) & 1300 (168) & 0.53 (169) & 2.3e+21  & \nodata & \nodata & N (169) & \nodata \\
-{\bf V5116 Sgr} & 8.15 (170) & 2453556.91 (170) & 6.5 (171) & 970 (172) & 0.25 (173) & 1.5e+21 & 0.1238 (171) & 11$\pm3$ (173) & N (174) & \nodata \\
-{\bf V5558 Sgr} & 6.53 (175) & 2454291.5 (175) & 125 (176) & 1000 (177) & 0.80 (178) & 1.6e+22  & \nodata & 1.3$\pm0.3$ (176) & N (179) & \nodata \\
-{\bf V5579 Sgr} & 5.56 (180) & 2454579.62 (180) & 7: & 1500 (23) & 1.2 (181) & 3.3e+21 & \nodata & \nodata & Y (181) & \nodata \\
-{\bf V5583 Sgr} & 7.43 (182) & 2455051.07 (182) & 5: & 2300 (182) & 0.39 (30) & 2.0e+21 & \nodata & 10.5 & \nodata & \nodata \\
-{\bf V574 Pup} & 6.93 (183) & 2453332.22 (183) & 13 (184) & 2800 (184) & 0.5$\pm0.1$  & 6.2e+21 & \nodata & 6.5$\pm1$  & M (185) & \nodata \\
-{\bf V597 Pup} & 7.0 (186) & 2454418.75 (186) & 3: & 1800 (187) & 0.3 (188) & 5.0e+21  & 0.11119 (189) & \nodata & N (188) & \nodata \\
-{\bf V598 Pup} & 3.46 (14) & 2454257.79 (14) & 9$\pm1$ (190) & \nodata & 0.16 (190) & 1.4e+21 & \nodata & 2.95$\pm0.8$ (190) & \nodata & \nodata \\
-{\bf V679 Car} & 7.55 (191) & 2454797.77 (191) & 20: & \nodata & \nodata & 1.3e+22  & \nodata & \nodata & \nodata & \nodata \\
-{\bf V723 Cas} & 7.1 (192) & 2450069.0 (192) & 263 (2) & 600 (193) & 0.5 (194) & 2.35e+21  & 0.69 (195) & 3.86$\pm0.23$ (196) & N & \nodata \\
-V838 Her & 5 (197) & 2448340.5 (197) & 2 (198) & \nodata & 0.5$\pm0.1$ (198) & 2.6e+21  & 0.2975 (199) & 3$\pm1$ (198) & Y (200) & \nodata \\
-{\bf XMMSL1 J06} & 12 (201) & 2453643.5 (202) & 8$\pm2$ (202) & \nodata & 0.15 (203) & 8.7e+20 & \nodata & 50 & \nodata & \nodata \\
-\enddata
-\end{deluxetable*}
-\end{longrotatetable}
-
-A handy "cheat sheat" that provides the necessary LaTeX to produce 17 
-different types of tables is available at \url{http://journals.aas.org/authors/aastex/aasguide.html#table_cheat_sheet}.
-
-%% The reference list follows the main body and any appendices.
-%% Use LaTeX's thebibliography environment to mark up your reference list.
-%% Note \begin{thebibliography} is followed by an empty set of
-%% curly braces.  If you forget this, LaTeX will generate the error
-%% "Perhaps a missing \item?".
-%%
-%% thebibliography produces citations in the text using \bibitem-\cite
-%% cross-referencing. Each reference is preceded by a
-%% \bibitem command that defines in curly braces the KEY that corresponds
-%% to the KEY in the \cite commands (see the first section above).
-%% Make sure that you provide a unique KEY for every \bibitem or else the
-%% paper will not LaTeX. The square brackets should contain
-%% the citation text that LaTeX will insert in
-%% place of the \cite commands.
-
-%% We have used macros to produce journal name abbreviations.
-%% \aastex provides a number of these for the more frequently-cited journals.
-%% See the Author Guide for a list of them.
-
-%% Note that the style of the \bibitem labels (in []) is slightly
-%% different from previous examples.  The natbib system solves a host
-%% of citation expression problems, but it is necessary to clearly
-%% delimit the year from the author name used in the citation.
-%% See the natbib documentation for more details and options.
-
 \begin{thebibliography}{}
@@
 \bibitem[Astropy Collaboration et al.(2013)]{2013A&A...558A..33A} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, A33
-\bibitem[Bertin \& Arnouts(1996)]{1996A&AS..117..393B} Bertin, E., \& Arnouts, S.\ 1996, \aaps, 117, 393 
-\bibitem[Corrales(2015)]{2015ApJ...805...23C} Corrales, L.\ 2015, \apj, 805, 23
-\bibitem[Ferland et al.(2013)]{2013RMxAA..49..137F} Ferland, G.~J., Porter, R.~L., van Hoof, P.~A.~M., et al.\ 2013, \rmxaa, 49, 137
-\bibitem[Hanisch \& Biemesderfer(1989)]{1989BAAS...21..780H} Hanisch, R.~J., \& Biemesderfer, C.~D.\ 1989, \baas, 21, 780 
-\bibitem[Lamport(1994)]{lamport94} Lamport, L. 1994, LaTeX: A Document Preparation System, 2nd Edition (Boston, Addison-Wesley Professional)
-\bibitem[Schwarz et al.(2011)]{2011ApJS..197...31S} Schwarz, G.~J., Ness, J.-U., Osborne, J.~P., et al.\ 2011, \apjs, 197, 31  
-\bibitem[Vogt et al.(2014)]{2014ApJ...793..127V} Vogt, F.~P.~A., Dopita, M.~A., Kewley, L.~J., et al.\ 2014, \apj, 793, 127
 

### 2021-09-22 Paper1.tex
to github

@@
-\documentclass{aastex62}
+\documentclass[twocolumn]{aastex62}
 
@@
 %%
-%% There are other optional arguments one can envoke to allow other stylistic
+%% There are other optional arguments one can invoke to allow other stylistic
 %% actions. The available options are:
@@
 \newcommand\latex{La\TeX}
+\newcommand{\unit}[1]{\ensuremath{\, \mathrm{#1}}}
+\newcommand{\figref}[1]{Figure \ref{#1}}
+
+\newcommand{\code}[1]{\ensuremath{\textsf{#1}}}
+\newcommand{\lare}{\code{LARE}}
+\newcommand{\scipy}{\code{scipy}}
+\newcommand{\fnc}[1]{\code{#1}}
+\newcommand{\removecomment}[1]{\textcolor{red}{#1}}
+\newcommand{\secref}[1]{$\S$\ref{#1}}
+
+% IBIS fitting macros
+\newcommand{\halpha}{\ensuremath{H\alpha}}
+\newcommand{\hfit}{\ensuremath{\halpha_\mathit{fit} }}
+\newcommand{\linecenter}{\ensuremath{\lambda_0}}
+\newcommand{\linew}{\ensuremath{\delta \lambda}}
+\newcommand{\imin}{\ensuremath{I_\mathit{min}}}
+\newcommand{\ihalf}{\ensuremath{I_\mathit{half}}}
+
+% comments
+\newcommand{\latcomment}[1]{\textcolor{red}{LAT: #1}}
+\newcommand{\saj}[1]{\textcolor{cyan}{SAJ: #1}}
+\newcommand{\ark}[1]{\textcolor{purple}{ARK: #1}}
 
@@
 %% this information may be modified by the editorial offices.
-\shorttitle{The Kolsch of Data Sets}
+\shorttitle{The K\"{o}lsch of Data Sets}
 \shortauthors{Kobelski et al.}
@@
 \correspondingauthor{Adam R. Kobelski}
-\email{adam.kobelski@mail.wvu.edu, ltarr2@gmu.edu, sjaeggli@nso.edu, sabrina.savage@nasa.gov}
+\email{adam.kobelski@mail.wvu.edu}
 
-\author{Adam R. Kobelski}
+\author[0000-0002-4691-1729]{Adam R. Kobelski}
+\affiliation{NASA Marshall Space Flight Center}
 \affiliation{West Virginia University}
@@
 \author[0000-0002-8259-8303]{Lucas A. Tarr}
-\affiliation{George Mason University}
+\affiliation{National Solar Observatory}
+%\email{ltarr@nso.edu}
+\author[0000-0001-5459-2628]{Sarah Jaeggli}
+\affiliation{National Solar Observatory}
+%\email{sjaeggli@nso.edu}
+\author{Nicholas Luber}
+\affiliation{West Virginia University}
+%% The \author command can take an optional ORCID.
+\author[0000-0001-6102-6851]{Harry P. Warren}
+\affiliation{Naval Research Laboratory}
+%\email{harry.warren@nrl.navy.mil}
+\author[0000-0002-6172-0517]{Sabrina Savage}
+\affiliation{NASA Marshall Space Flight Center}
+%\email{sabrina.savage@nasa.gov}
 
-\author{Sarah Jaeggli}
-\affiliation{National Solar Observatory}
-
-%% The \author command can take an optional ORCID.
-\author{Sabrina Savage}
-\affiliation{NASA Marshall Space Flight Center}
 \begin{abstract}
-Here is our abstract.  We did work
+%Transient brightenings (TBs) are ubiquitous features of the solar atmosphere across many length and energy scales, the most energetic of which manifest as large-class solar flares.
+TBs typically originate in regions of enhanced magnetic flux and are observed as increased emission across wavelengths from X-ray to radio, with notable dynamics on timescales of seconds to hours.
+Coronal TBs are often studied using Extreme Ultravioliet (EUV) and X-ray imaging and spectra.
+TBs likely originate from photospheric activity such as flux emergence, but are proximately driven by energy transfer through the chromosphere, either by convective waves, direct ejection of chromospheric material, or reconnection.
+Chromospheric and transition region observations of these events have only become routine in the last decade.
+%Chromospheric and transition region observations of these events have not been routine for the last few decades. 
+New instruments sensitive to chromospheric radiation at X-ray, UV, Visible, IR, and sub-mm wavelengths have become available that significantly enhance our ability to understand the bi-directional flow of energy through the chromosphere.
+In this paper, we showcase and combine a new dataset utilizing a large number of these instruments to obtain multi-wavelength chromospheric observations capable of improving our understanding of the connectivity between the photosphere and the corona in the chromosphere via transient brightenings and wave signatures.
+This comprehensive study provides one of the most complete views of chromospheric activity related to small scale brightenings in the corona and chromosphere to date.
+SOME NUMBERS, SCIENCE CONCLUSIONS.
 
 \end{abstract}
-\keywords{The Sun, Radio, XRay, EUV}
+\keywords{The Sun, Radio, X-Ray, EUV}
 
 \section{Introduction} \label{sec:intro}
-Our work is awesome, here's why
-\section{Observations} \label{sec:Obs}
-\subsection{IBIS}
-The IBIS data was reduced primarily using the pipeline code provided by NSO\footnote{Version 1.4, available here: https://www.nso.edu/telescopes/dunn-solar-telescope/dst-pipelines/}
+The methods of transporting energy from the photosphere through the chromosphere to the million degree corona have been debated since the discovery of the hot corona \citep[][]{1933LyotMarshall, 1939Grotrian}.
+The underlying problem is that thermal conduction, which is very efficient in solar plasmas, will transport energy from the corona to the chromosphere, so the energy in the corona must constantly be resupplied.
+One of the early ideas for this transport of energy was via wave activity through hydrodynamic shocks \citep[][]{1949Schatzman} and later, once the central role of magnetic fields on the Sun was fully realized, by magnetoacoustic or Alfv\'en waves \citep{1961Osterbrock}.
+In this scenario, convective energy drives the waves which carry energy as they propagate upward through to the corona, and eventually deposit that energy as they cascade to small length-scales and heat the plasma through dissipation \citep{2014vanBallegooijenEA_FootpointMotion}.
 
+Coronal waves have been observed in many forms. 
+Large amplitude standing and propagating waves are caused by both confined flares and CMEs, and their properties are comparatively easy to detect and quantify \citep{2014LiuOfman_EUVwaves}. 
+At the same time, many quiescent coronal structures exhibit continuous oscillatory power, detectable using Fourier transform or wavelet methods of longer time series \citep{Tomczyk:2009}, indicating that a broad spectrum of waves are present throughout the chromosphere and corona.
+While the presence of waves is uncontested, where, by what mechanism, and how much wave energy may be dissipated to heat the coronal plasma is currently not well understood \citep{2014vanBallegooijenEA_FootpointMotion}.
+
+As an alternative to wave heating, it has been posited that small-scale magnetic reconnection via nanoflares \citep[][]{1983Parker} could be responsible for the heating of the corona. 
+It was thought that these nanoflares would manifest themselves as small scale brightenings in the corona, sometimes referred to as microflares or active region transient brightenings \citep[][]{1984LinEA_microflares, 1991Hudson, 1992ShimizuEA, 1995Shimizu}.
+\citet{1997GaryEA} determined that the small scale-brightenings exhibit the same signatures of particle acceleration as larger solar flares and concluded that many of the transient brightenings (TBs) were also products of magnetic reconnection.
+\latcomment{Reference some of the NuSTAR or Foxi work about this?}
+A key suggestion of the Parker nanoflare model was that the reconnection would occur due to substructure in the magnetic field lines, in which the observed loops consist of many unresolved braided magnetic strands.
+The concept of unresolved strands is in agreement with forward models of the observations \citep[e.g.][]{2012BrooksEA, 2014KobelskiEA_XRTTBs, 2014KobelskiMcKenzie_HiC}, and has been strongly suggested by direct observation in extreme ultraviolet (EUV) with the Hi-C sounding rocket \citep[][]{2013CirtainEA_HiC}.
+
+Microflare research has largely focused on observable transients, which implies ``low-frequency'' active region heating wherein a larger plasma element, such as an overlying coronal loop, is heated significantly enough to show enhanced emission compared to the background and then notably cools over time \citep[][]{2015Klimchuk_CHoverview}.
+This scenario is in contrast to ``high-frequency'' heating wherein the observable plasma elements experience heating events fast enough that they appear at a sustained temperature and density, i.e.
+they are not allowed to cool or drain between successive heating events.
+Sometimes assumed in this latter paradigm is that the individual microflares occur on unresolved spatial and temporal scales, such that while individual strands may cool and/or drain, the conglomerated strand appears to have a steady average density and temperature \citep[e.g.][]{2013BrooksEA_LoopSize, 2014SubramanianEA_LowAndHighFrequency, 2016SchmelzEA}.
+
+One of the best ways to follow how plasma flows through the chromosphere and corona is by using emission and absorption spectral measurements. 
+For stable loops, raster scans from the \textit{Hinode} EUV Imaging Spectrograph (EIS) and the Interface Region Imaging Spectrograph (IRIS) have been used to better constrain the rate of heating quiescent regions of the Sun \citep[e.g.][]{2016BrooksWarren_NTWidths,2016TestaEA_ARLoopsIRISEIS, 2017GhoshEA_LoopsIRISEIS}.
+To measure flows during transient events requires fortuitous pointing and specific observations with minimal rastering. 
+Here we present an ideal data set to study dynamic spectra of small scale, short lived coronal brightenings with coronal, chromospheric, and photospheric instrumentation. 
+Such studies are crucial to understanding the flow of energy into the corona, as well as provide statistical insight into this coupled system during solar flares.
+
+Much of the aforementioned work on TBs has focused on the \emph{coronal} observables, though recent instrumentation has shown evidence of chromospheric counterparts to microflaring \citep[][]{2016TestaEA_ARLoopsIRISEIS, 2017GhoshEA_LoopsIRISEIS}.
+The chromospheric response to large flares is well established in the form of chromospheric ablation from flare ribbons \citep[][]{2017Benz_LRSP}. 
+The wave-driven chromospheric response to large flares has also been detected and investigated \citep[][and references within]{2014LiuOfman_EUVwaves, 2016RussellEA_Sunquakes}. 
+What has eluded prior studies is a comprehensive insight into how wave motion through the chromosphere relates to the occurrence of small coronal flares, as well as how small flares drive chromospheric heating and waves.
+Evidence for this process is given by the partial temporal and spatial overlap of Ellerman bomb populations and UV burst populations, thought to be caused by energetic release at different heights \citep{2019Vissers, 2018Young}.
+This feedback loop between waves and transients can inform the bi-directional flow of energy between the chromosphere and the corona.
+
+In this paper, we present a unique, robust, and extensive data set with which to study the flow of energy through the chromosphere and the interplay between transients and wave activity. 
+Even though the data set is of a quiescent solar region, it displays notable dynamics from the photosphere to the corona. 
+This region is exemplary of the ubiquitous features found throughout the solar atmosphere during all phases of the solar cycle. 
+The type of analysis we propose has been performed for active regions and strong plage, \emph{but not quiescent regions}. 
+Since this data set probes each layer of the Sun in multiple wavelengths, heights, temperatures, and methodologies, it can provide multiple ground-truths and perspectives for which to compare to models of chromospheric energy flow and transfer in later papers.
+
+The data set includes photospheric magnetic field information from the Helioseismic and Magnetic Imager \citep[HMI,][]{2012SchouEA_HMI} as well as imaging from the Atmospheric Imaging Assembly \citep[AIA,][]{2012LemenEA_AIA} on board the Solar Dynamics Observatory \citep[SDO,][]{2012PesnellEA_SDO}; photospheric magnetic field data from the Solar Optical Telescope \citep[SOT,][]{2008TsunetaEA_SOT}, coronal X-ray imaging from the X-Ray Telescope \citep[XRT,][]{2007GolubEA_XRT}, and EUV spectra from EIS \citep{2007CulhaneEA_EIS} on board the {\it Hinode} spacecraft \citep[][]{2007KosugiEA_Hinode}; chromospheric images and spectra from IRIS \citep{2014DePontieuEA_IRIS}; spectral images from the  Interferometric BIdimensional Spectropolarimeter \citep[IBIS,][]{2006Cavallini_IBIS} and infrared spectropolarimetry from the Facility InfraRed Spectropolarimeter \citep[FIRS,][]{2010JaeggliEA_FIRS} at the Dunn Solar Telescope (DST); and millimeter wave information from the Atacama Large Millimeter Array \citep[ALMA,][]{2009WootenThompson_ALMA, 2010HillsEA_ALMA2}.
+
+In this paper, we describe the reduction of the imaging and spectral observations, as well as the co-alignment between instruments. 
+We then interpret and compare activity between atmospheric layers, though a more thorough analysis is forthcoming.  
+We give details of the observations in Section~\ref{sec:data}, their co-alignment in Section~\ref{sec:coalign} and their analysis in Section~\ref{sec:analysis}, with concluding remarks in \ref{sec:conclusion}.
+
+\section{Data} \label{sec:data}
+\subsection{Overview and Coordination}
+The data sets presented in this work resulted from a large coordination campaign that was keyed to the ALMA observations and encompassed a suite of ground- and space-based facilities operated by different organizations.
+The observations occurred during one of the first coordinated campaigns to support PI-led solar ALMA observations.
+Due to constraints in the ALMA scheduling, the exact timings and pointings could only be determined the day before the actual observations, with the result that there is not always complete temporal or spatial overlap between each facility.
+Given these constraints, the coverage is, in general, fairly good.
+
+\figref{fig:coordination} presents an overview the temporal and spatial overlap between the various instrument channels during the time of the ALMA observations. 
+In the upper panel we have ordered the instruments in the vertical direction roughly according to height in the solar atmosphere.
+In addition to the times shown here, SOT, EIS, and XRT took observations of this same region for several days leading up to the ALMA observing window.
+Fortuitously, NuSTAR also observed this region and detected two small flares around 19:00 and 19:30 UT \citep{2018Kuhar}.
+The lower left panels show the approximate fields-of-view (FOV) of the various instruments overlaid on an AIA 193\AA{} image using the same colors as the upper panel, with the left showing the full Sun and the right a zoomed in region.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\linewidth]{figures/obs_timing}
+    \includegraphics[width=0.48\linewidth]{figures/AIA193_FOVs.png}
+    \includegraphics[width=0.48\linewidth]{figures/AIA193_FOVs_zoom.png}
+    \caption{Overview of all observations around the ALMA observing window.
+Upper plot: timing information, where instruments are ordered vertically roughly according to height in the solar atmosphere.
+Gaps in each color band indicate data gaps in that data channel.
+Lower panels: approximate FOVs for each instrument using the same colors as in the upper panel, overlaid on an SDO/AIA-193\AA{} context image.}
+    \label{fig:coordination}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\linewidth]{figures/IBISimg0108.eps}
+    \caption{Representative sample of co-aligned images. The SOT data has been rotated to align with the coordinate time of the IBIS data. The ALMA data ranges from $\pm$some number of K}
+    \label{fig:coordination}
+\end{figure}
+
+\subsection{SDO/AIA}\label{sec:sdoaia}
+AIA obtains full-disk images of the Sun every 12 seconds with 0.6\arcsec{} spatial sampling in a variety of visible, UV, EUV channels.
+Observations from all AIA channels are available throughout the entire coordination period.
+The Level 1 AIA data was downloaded from the Joint Science Operations Center (JSOC)\footnote{\url{http://jsoc.stanford.edu/}}, updated to Level 1.5 using \fnc{aia\_prep.pro} as described in the SDO Analysis Guide.
+We also selected a subregion that fully encompassed the ALMA target using the SSW cutout service\footnote{\url{https://www.lmsal.com/get_aia_data/}; see also \S4.3 of the SDO Analysis Guide.} for a region approximately $300\arcsec\times300\arcsec$ for the duration of the other datasets (14:00-17:00 UT on 2017-03-21).
+The 193 \AA\ channel of AIA was primarily used for co-alignment and to provide full-disk context for the other observations.  
+The 193 \AA\ bandpass includes \ion{Fe}{12} and \ion{Fe}{24} lines which form in the corona and hot plasma at log(T)=6.2 and 7.3 respectively.
+
+\subsection{SDO/HMI}
+We used three days of intensity and line-of-site (LOS) magnetograms from the level 1.5 \texttt{hmi.M\_720s} and \texttt{hmi.Ic\_720s} series\footnote{JSOC query: \texttt{hmi.M\_720s[2017.03.19\_00:00:00\_TAI/3d]}, and similar for intensity.}.
+An area $\approx330\arcsec{}\times250\arcsec{}$ was tracked using solar rotation to understand the magnetic evolution of the region leading up to and throughout the coordinated observations.  
+To ease later analysis, we derotated all HMI data so that the solar North-South axis aligned with columns of the data array, with North pointing upward, but kept the spatial scaling of the original HMI data.
+The typical extra step of spatially-rescaling the data to match AIA  has little benefit for use given that our various datasets include many different spatial samplings.
+
+% Nick stuff, feel free to change at will, I was just getting my thoughts out.
 \subsection{ALMA}
+\paragraph{ALMA background} The Atacama Large Millimeter Array (ALMA) is a radio interferometer with current frequency coverage spanning 84 to 950 GHz.
+ALMA is constituted of 66 telescope dishes, 54 with a diameter of 12 meters, and 12 with a diameter of 7 meters.
+These 66 dishes are arranged as such to ensure that ALMA had suitable sensitivity to large scale diffuse emission, this is aided by the high density of centrally located dishes, and excellent resolution to small scale features, this is achieved with the dishes at high distance.
+The ALMA observations presented in this work were in the ALMA observing Band 3, which corresponds to a central frequency of 100 GHz, and a total bandwidth of 18 GHz about that central frequency.
+At this frequency and array configuration, our approximate resolution is 2$\arcsec$ on the sky.
+Our integration time used was 2 seconds and the entire observation, including the target field and calibrators, lasted for 1.03 hours.
 
-\subsection{Hinode}
+\paragraph{ALMA calibration}
+\paragraph{ALMA self-calibration}
+\paragraph{ALMA issues with phase-center}
 
-\section{Coalignment} \label{sec:coalign}
-Coaligning the various instruments was a challenge.  We did it like this:
+\subsection{DST/IBIS}
+IBIS is a dual Fabry-Perot interferometer- (FPI-) based imaging spectropolarimeter that was mounted at the Dunn Solar Telescope.
+The FPI cavity is tuned to transmit a narrow bandpass $(\approx 2.4\unit{pm})$, and the tuning is modulated to step the bandpass over the wavelength range of the line.
+We used IBIS in spectal-only mode (no polarimetry) with a circular field stop of approximately 90\arcsec{} diameter.
+We continuously sampled the \halpha{} line between 14:46-16:55 UT using 26 wavelength positions, with $\approx 12.5\unit{pm}$ spacing near line core and $\approx 19.1\unit{pm}$ spacing in the wings.  
+Each narrow band image is paired with a strictly cotemporally acquired broad band continuum image taken in a nearby wavelength band at $660\unit{nm}$.
+The broad band image is used for speckle reconstruction, self alignment of the narrow band images, and co-alignment between the IBIS data and other data series, e.g., to the HMI continua data series.
+\par
 
-\startlongtable
-\begin{deluxetable}{c|cc}
-\tablecaption{ApJ costs from 1991 to 2013\tablenotemark{a} \label{tab:table}}
-\tablehead{
-\colhead{Year} & \colhead{Subscription} & \colhead{Publication} \\
-\colhead{} & \colhead{cost} & \colhead{charges\tablenotemark{b}}\\
-\colhead{} & \colhead{(\$)} & \colhead{(\$/page)}
+The IBIS data was reduced primarily using the pipeline code provided by NSO\footnote{Version 1.4, available here: \url{https://www.nso.edu/telescopes/dunn-solar-telescope/dst-pipelines/}.}.  
+This process aligns the broad-band and narrow-band channels and accounts for detector dark counts, flat-fielding, and the spatially-dependent wavelength shift induced by the telecentric mount of the FPIs.
+Kevin Reardon provided several modified steps that better account for spatially- and spectrally-dependent fringes in the narrow band data due to the prefilter, as compared with the pipeline code\footnote{Reardon, private communication.
+See documentation at \url{https://github.com/kreardon/IBIS.git}.}, which resulted in an improved estimate of the gain for each spatial and spectral point throughout the narrow band datacube.
+As a final calibration step, we used the KISIP code \citep{2008WoegerSPIE,2008WoegerEA_Speckle} to perform a speckle reconstruction of the data using the IBIS broad band images that are taken strictly co-temporally with the narrow band images; the broad band data is specifically designed for this purpose\citep{2008Cauzzi}.\par
+
+We took several further steps for the IBIS preparation.  
+To correct for the several arcsecond inaccuracy of the DST blind-pointing, slight rotation of solar-North with respect to the CCD pixel arrays, and the slight difference in plate-scale between the CCD X and Y directions, we rotated, shifted, and stretched the IBIS broad band data to match the granulation pattern in nearly co-temporal HMI continuum data at time 2017-03-21 15:46:36.
+These parameters remained constant throughout the IBIS data series.
+\par
+
+\subsubsection{IBIS self alignment}\label{sec:ibisselfalign}
+IBIS data in the spectral dimension is not strictly co-temporal: the time difference between successive wavelength steps is about $0.167\unit{s}$ and the cadence between images at a given wavelength is about $4.2\unit{s}$.
+Our observations were taken during periods of moderate seeing, so the image sequence has some jitter, which became significant at times.  
+To correct for this effect and spatially co-align all the IBIS data with itself we used a cross-correlation technique outlined here\footnote{The \texttt{chi2\_shift} method from Adam Ginsburg's \texttt{image\_registration} python package.
+See \url{https://github.com/keflavich/image_registration}.}:
+\begin{enumerate}
+    {\item We manually determined ``bad frames'' when AO lock was lost or a frame became significantly distorted, by inspecting the strictly co-temporal broad band images; these frames were assumed bad for all wavelengths in a given scan of the line.}
+    {\item We generated a reference image by taking the running-average of the previous 5 registered ``good'' scans through the spectral line: at 26 images per scan, the average involves 130 broad band images.
+    The initial average reference image was taken to be the average of the first spectral scan from the dataset.}
+    {\item We used \texttt{chi2\_shift} to determine the spatial offset between each of the broad band images in a scan and the average reference image.}
+    {\item If the frame was labeled ``good,'' the final registered broad band image for each wavelength was appended to running average.}
+    {\item The measured offset was then saved, to be applied later to both the broad band image and the cotemporal narrow band image, which will co-align the entire data series (this last step has already been performed on the provided IBIS FITS files).}
+\end{enumerate}
+
+The above method allowed essentially all 46,800 frames to be co-aligned while being robust against the occasional loss of AO during brief periods of poor seeing.\par
+
+\subsection{DST/FIRS}
+During the coordinated observations, FIRS first conducted a raster observation from 14:46:47 to 15:00:54 UT (08:46:47 to 11:00:54 am MDT).
+Then sit-and-stare observations were run almost continuously from 15:02:36 to 16:57:42 UT with small gaps for adjustment of the adaptive optics system.
+During these observations, FIRS was configured to use the 40 $\mu$m single slit with the f/36 feed optics, which provide a slit width of 0.3 arcsec on the sky.
+The vertical extent of the slit covered approximately 74 arcsec.
+Only the 10830 \AA\ channel of FIRS was used, and the narrow band filter was removed to take advantage of the maximum wavelength coverage possible with the detector.
+In this configuration the spectrograph was able to cover a 40 \AA\ bandpass centered at 10834 \AA.
+This region contains the Si I and He I 1083 nm lines commonly used for spectropolarimetry, as well as several other solar and telluric lines.
+The spectral dispersion of 3.86 pm/pixel is approximately equal to the spectral resolution of the instrument at this wavelength, based on laser profile measurements \citep{2011Jaeggli_PHD}.
+An exposure time of 125 msec was used to keep counts within the range of linear behavior for the HgCdTe detector.
+The liquid crystal variable retarders ran two repeats of a 4-state modulation sequence, and the time to execute a complete polarization measurement was about 4 seconds.
+
+A camera was set up to reimage the light from the mirrored surface of the FIRS slit.
+These slit-jaw images were obtained to assist in co-alignment and cover a $185\times155$ arcsec$^2$ field of view with 0.153 arcsec/pixel sampling.
+The slit-jaw images were recorded from 14:46 to 16:58 UT with a cadence of 5 seconds to approximately match the cadence of the FIRS spectrograph, although the exposure time was only 200 msec.
+The wavelengths seen by the slit-jaw imager  were longer than about 700 nm due to the beamsplitter needed for the IBIS \halpha{} channel, and the sensitivity of the silicon-based detector for the slit-jaw imager extends out to about 900 nm.
+
+The data from FIRS was reduced using techniques similar to \citet{2012Jaegglietal}.
+First, calibration data were assembled.
+All images were first corrected for the non-linear response of the detector.
+All frames from a single dark calibration were averaged together, and the nearest dark calibration in time was applied to the frames with light.
+The lamp flat images were averaged together and dark-subtracted.
+A raster scan of the grid target at the telescope main focus was corrected using the dark and lamp flat.
+A frame from the center of the grid scan was used to determine the geometric correction to make the spectral and spatial coordinates orthogonal with linear dispersion, and match the coordinates between the dual beams for spectropolarimetry.
+
+A flat field for the science data was constructed using an observation of disk center with randomized motion to blur out spatial features.
+All of the images from this dataset were corrected for linearity, dark subtracted, and averaged together.
+The geometric correction was used to convert the spectrum between spatial/spectral and detector coordinates.
+The average spatial and spectral profiles were obtained.
+The hairlines crossing the slit were fit from the spatial profile and divided from the image so that these features would remain in the science observations.
+The spectral lines were fit from the spectral profile using a Voigt function and then divided from the flat field observation.
+
+A pixel-by-pixel polarimetric correction using the method of \cite{2013Schad} was attempted using a calibration sequence obtained with the ASP calibration linear polarizer and waveplate near the DST main focus.
+However, the derived solution did not seem to properly correct the science data, leaving large bias levels in the polarized states.
+This may be due to changes in the IR detector linearity that were not properly corrected for by the lookup table.
+Instead, a blind polarimetric demodulation was applied to the data, not correcting for instrumental polarization.
+The resulting polarized spectra contain mostly Stokes V signal.
+Application of ad-hoc techniques for determining and removing instrumental polarization, i.e.
+\citet{collados03}, would probably not be successful due to the lack of other polarized signal.
+Magnetogram-style maps of the net polarized signal in the Si I line appear similar to the SOT/SP maps.
+
+Fiducials crossing the slit provide common features for co-aligning the slit in the vertical and horizontal directions with respect to the solar image.
+During the reduction for the spectrograph data, the dark fiducial lines crossing the spectra were fit in each spectrum and then divided to remove them from the image.
+The slit and fiducials were fit in each slit-jaw image before application of the flat field.
+The fitted fiducial and slit positions were saved for the co-alignment step.
+
+\subsection{IRIS}
+During the period 13:00:07 to 19:26:15 UT on 2017-03-21, IRIS performed 530 repeats of a program taking coarse 8-step rasters using a medium field of view with the slit aligned north-south.
+The spectrograph field of view, of approximately 60 $\times$ 16 arcsec$^2$, was sampled in 2 arcsec steps by the 0.3 arcsec wide slit, while the silt-jaw imager had a 60 $\times$ 65 arcsec$^2$ instantaneous field of view centered on the spectrograph slit.
+The spectrograph took 4 sec exposures at a 5.4 sec cadence with both the FUV and NUV spectrograph channels.
+The slit-jaw imager obtained images every 11 sec using the Si IV 1400 \AA\ filter channel, and images with the 2832 \AA\ Mg II line wing filter channel were taken every 44 sec to provide photospheric context.
+IRIS observations were continuous in the time period and include several passages through the South Atlantic Anomaly, during which the observations show increased hot pixels due to particle strikes.
+
+IRIS Level 2 data was obtained from the IRIS website, which also provided cutouts of the co-temporal AIA data.
+Calibration of the IRIS data are described in \citet{wuelser18}.
+IRIS Level 2 data is already co-aligned with AIA to a high degree of accuracy, so further co-alignment steps were not necessary.
+An example of the IRIS SJI Si IV 1400 \AA\ image and NUV spectrum near the line core are shown in Figure \ref{fig:IRIS}.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=7in]{./figures/IRIS_example.eps}
+    \caption{An example of the IRIS Level 2 SJI and NUV spectrograph data near the time 15:47 UT.
+The slit-jaw image is a composite of 4 images taken from 15:46:57.57 to 15:47:30.35 on 2017-03-21 to show the full field of view during the raster.
+The slit positions for the 8-step coarse raster are shown over plotted on the SJI image in white.
+The red slit indicates the position at which the NUV spectrum on the right was taken at 15:47:25.03.
+The blue circle and crosshair shows the co-rotating ALMA field of view.}
+    \label{fig:IRIS}
+\end{figure*}
+
+\subsection{{\it Hinode} SOT}
+{\it Hinode} SOT Spectropolarimeter (SP) data was primarily taken from 14:00 UT to 18:46 UT with using 60 $\times$ 60 arcsec$^2$ fast maps with 0.3 arcsec spatial resolution with a $\sim$ 30 minute cadence.
+Additionally, the region of interest was observed sporadically over the 50 hours leading up to the coordinated observations, with FOVs of approximately $150\times160\unit{arcsec}^2$.
+%The data was calibrated to level 2  using the BLAH method, and further reduced using Sarah's awesome skills.
+In total, this provided 7 maps of the region over the 50 hours leading up to the observation, and 10 maps of the region during the 4 hours of coordination.
+The SP instrument performance is described in \citet{2013Litesetal}.
+
+The SP Level 2 data, reduced and inverted with the Milne-Eddington gRid Linear Inversion Network (MERLIN) code to produce maps of physical atmospheric parameters, including the vector magnetic field, were obtained from the Community Spectropolarimetric Analysis Center (CSAC, DOI:10.5065/D6JH3J8D).
+See \citet{2013Lites&Ichimoto} for a description of the data reduction routines.
+
+\subsection{{\it Hinode} EIS}
+EIS conducted observations for the coordinated campaign from 14:00 UT to 21:21 on 2017-03-21.
+This instrument provides a wide range of diagnostics as described in \citet{2007Young}.
+Context slot rasters approximately three minutes in duration were taken at the beginning and end of the observation.
+In between the slot rasters, EIS took sit-and-stare observations with 34 sec cadence.
+The sit-and-stare observations were interrupted by a 10 minute disk center synoptic observation at 19:40 UT.
+
+The EIS slot rasters covered a large region approximately $470\arcsec\times485\arcsec$ in 15 overlapping steps with spatial sampling of 1\arcsec\ per spatial pixel.
+The sit-and-stare observations consisted of a 20\,s exposures with the 2\arcsec\ wide slit.
+Again, the spatial sampling along the slit was 1\arcsec\ per pixel.
+The detector readout for the spectra included all of the available wavelength ranges, but was limited to 256\arcsec\ along the slit.
+\saj{Where did the EIS data come from?
+Harry probably got it from JSOC, I used VSO} The EIS data was processed using the default settings for the \verb+eis_prep+ routine in SSWIDL \citep{1998FreelandHandy_SSW}.
+Intensities for the \ion{Fe}{12} 195.119\,\AA\ and \ion{He}{2} 256.317\,\AA\ lines were computed using multi-Gaussian fits \saj{reference or ssw routine name?}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=3.5in]{figures/EIS_example.eps}
+    \caption{A reconstructed slot raster image from the EIS \ion{Fe}{12} 195 \AA\ channel.
+The slot raster started at 14:00 UT.
+The blue circle and crosshair show the ALMA co-rotating field of view.
+The black rectangle shows the extent of the region covered by the EIS slit during the sit and stare observations.}
+    \label{fig:EIS}
+\end{figure}
+
+\subsection{{\it Hinode} XRT}
+XRT observed the active area from 12:33:12.311 -  18:59:27.511 UT with the Al\_poly filter, allowing plasma observations above $\sim$3 MK.
+The Al\_poly filter is one of the thinnest filters on XRT which has not been prohibitively impaired by contamination \citep[][]{2011NarukageEA_XRT3}, though some features of the contamination are still apparent.
+While the intended cadence was 4s, automatic exposure control increased the exposure time, which slowed the cadence to 16s per image.
+This large data set was prepped \citep[][]{2014KobelskiEA_xrtprep} and the methods of \citet{2015YoshimuraMcKenzie_XRTcoalign} were used to estimate offsets for co-alignment to the data to other instruments.
+Cross-correlation techniques \citep[such as {\tt tr\_get\_disp.pro} in SolarSoft;][]{1998FreelandHandy_SSW} are used to remove instrumental jitter and to self-align the XRT data with itself.
+\begin{figure}[b]
+\centering
+\includegraphics[width=0.9\linewidth]{figures/img0070}
+\caption{Reverse color and scaled XRT Al\_poly image from 16:32:14.6, when all instruments were observing.
+The blue contours show locations where TBs were detected throughout the data set from 16:11:00 - 17:22:37.
+The black circle is the approximate FOV of IBIS, the purple lines the slit positions of IRIS, and the orange box the slit location of EIS.
+While the slits are not directly on the bulk of the detections, they are located near the footpoints of detected X-ray activity.}\label{fig:xrt}
+\end{figure}
+
+The XRT data allow us to see the brightest thermal features in the region, which can be seen in Figure~\ref{fig:xrt}.
+Similar to the methods discussed in \citet{2014KobelskiEA_XRTTBs} and \citet{2014KobelskiMcKenzie_HiC}, we have searched for small, dynamic brightenings in the data.
+We can then extract light curves for the brightenings.
+In this data set, over 30 individual brightenings were found, most of which were found within the FOVs (spatially and temporally) of the the other instruments.
+As seen in Figure~\ref{fig:xrt}, a few TBs appear to line up with the locations of the EIS and IRIS slits, though it is important to note that full co-alignment between instruments has not yet been performed.
+Further analysis will be able to better detect and connect the TB activity and to determine whether there is increased and co-located chromospheric activity before and/or after these events.
+
+\section{Co-alignment} \label{sec:coalign}
+Co-aligning the various instruments was a challenge.  \figref{fig:coalign} graphically depicts how each data set was coaligned.
+Our general approach was to use the broad wavelength and height coverage of the various HMI and AIA channels as a ``ground-truth'' mapping between solar coordinates and morphological features seen within each dataset.
+\begin{figure}[b]
+\centering
+\includegraphics[trim=200 100 100 100, clip, width=0.5\linewidth, angle=270]{figures/co-alignment.eps}
+\caption{Graphical representation of the coalignment process. SDO was utilized as the central coalignment reference, with other instruments co-aligned to it as possible. }\label{fig:coalign}
+\end{figure}
+The 2012 Venus transit allowed subarcsecond alignment of all the AIA and HMI channels\footnote{See the SDO Data Analysis Guide at \url{https://www.lmsal.com/sdodocs/doc/dcur/SDOD0060.zip/zip/entry/}, \S{}7.1 in the Sept 14, 2020 version of the document.}, which has since been maintained using Mercury transit observations, making SDO an excellent resource for this task.
+Alignment was then verified by checking against datasets that had not been explicitly aligned with each other.
+For example, the IBIS broadband images were aligned to HMI continuum data and then that alignment was verified by checking the correspondence of enhanced emission in the \halpha{} line wings to the HMI magnetograms, SOT magnetograms, and UV emission in the 1600 and 1700\AA{} AIA channels.
+
+Each data set has different temporal and spatial samplings and physical extent so no attempt was made to resample images from each instrument to a common temporoal/spatial grid.  
+Instead, the reduced and co-aligned datasets make use of the World Coordinate System (WCS) variant for solar physics defined in \citet{2006Thompson} and included in the FITS headers.  
+All data in this work uses helioprojective-cartesian coordinates, which can be transformed to any other coordinate system using standard routines in SSW, astropy, or sunpy.\par
+
+\subsection{DST/FIRS}
+FIRS data was co-aligned in two steps.
+First the FIRS slit-jaw images were co-aligned to HMI continuum intensity images from the 45s series, then the solar coordinates of the slit were mapped onto the spectrograph data.
+
+During the reduction of the FIRS slit-jaw images, the FIRS slit and hairlines crossing the slit were fit in each image before application of the flat field.
+The pixel coordinates of the slit/hairline pairs were saved for use during the co-alignment step.
+The dark hairlines also appear in the FIRS spectrograph images.
+During the reduction of the spectrograph data, the positions of these were also determined and saved for later use.
+
+The reduced FIRS slit-jaw images were co-aligned to SDO/HMI intensity images from the 45 second series.
+The approximate center coordinates of the FIRS slit-jaw were taken from the image headers which contain the telescope pointing near the time of the observation.
+The spatial dispersion was estimated based on observations of the grid target.
+The nearest HMI image in time was taken, and the coordinates were rotated to the time of the FIRS slit-jaw observation.
+Using interpolation based on the estimated slit-jaw coordinates, a subfield was extracted from the HMI image.
+X and Y shifts between the HMI sub-field and the slit-jaw image were determined using the SSW routine \verb+tr_get_disp+.
+The spatial dispersion and rotation of the first image was adjusted by hand to achieve a good match, then the co-alignment of the entire image sequence was done using the same scale and rotation parameters.
+The resulting coordinate mapping was used to transform the measured slit and hairline crossings into solar coordinates.
+The FIRS slit-jaw images were written to FITS files with their updated coordinate information using the WCS standard.
+
+To get the FIRS spectrograph data into the solar coordinate frame, the coordinates of the slit/hairline crossings for the slit-jaw data series were interpolated at the time of FIRS spectrograph observation.
+The slit/hairline solar coordinates were then used to determine the spatial dispersion along the slit, the solar X and Y coordinates at the center of the slit, and the rotation of the slit with respect to solar north assuming a linear mapping.
+Each set of polarized spectra was then written to a FITS file with the spatial and spectral coordinates in the WCS standard.
+The Stokes I spectrum was written in the main extension, and the Stokes Q, U, and V states were written to subsequent extensions with abbreviated headers.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=5in]{./figures/FIRS_example.eps}
+    \caption{co-aligned FIRS spectograph data from the beginning of the coordination taken between 14:46:48 and 15:00:55 UT on 2017-03-21.
+The top two panels show the reconstructed maps of continuum and He I 10830 line intensity (left and right respectively).
+The bottom panel shows the full Stokes I spectrum obtained with FIRS at 14:53:53 UT at the position indicated by the dashed line in each of the maps.
+The blue circle and crosshair shows the co-rotating ALMA field of view.}
+    \label{fig:FIRS}
+\end{figure*}
+
+\subsection{Hinode SOT}
+%The Hinode SOT/SP parameter maps were resampled to a uniform coordinate grid, then aligned with HMI.
+
+For each Level 2 raster scan of SOT/SP, the solar coordinates of the slit at each raster position were differentially rotated from the observed time to a common time at the center of the scan (using the SSW routine \verb+drot_xy+).
+The parameter maps were then resampled to a uniform coordinate grid.
+HMI intensity observations closest in time to the center of the SOT/SP scan were selected and interpolated onto the same coordinate grid and the relative shift between HMI and the SOT/SP continuum intensity map was determined (using \verb+tr_get_disp+).
+SOT/SP coordinates were updated with the corresponding shift.
+An ad-hoc rotation angle of CROTA2=-0.6 deg and x-y pixel scale of 0.315 arcsec/pixel were determined with respect to HMI and applied simultaneously with the coordinate shift.
+The resampled and co-aligned SOT/SP parameter maps were written to WCS-compliant FITS files where the main extension contains continuum intensity, and the inverted parameters are contained in additional FITS image extensions.
+Figure \ref{fig:SOTSP} shows an example of the continuum intensity and LOS magnetic field for the last large raster taken before the coordination with ALMA commenced.
+
+\begin{figure*}
+    \begin{center}
+        \includegraphics[width=7in]{./figures/SOTSP_example.eps}
+    \end{center}
+    \caption{The co-aligned continuum intensity and line of sight magnetic field from the co-aligned Level 2 SOT/SP data based on inversion of the 630.2 nm Fe I lines.
+The raster scan was run from 13:16:01 to 13:48:21 UT on 2017-03-21, and was the last large raster taken before the coordinated sequence began.
+The blue circle and crosshair shows the co-rotating ALMA field of view.}
+    \label{fig:SOTSP}
+\end{figure*}
+
+\subsection{Hinode EIS}
+The EIS slit data were co-aligned to 12\,s, $202\arcsec\times456\arcsec$ 193\,\AA\ AIA cutouts obtained from JSOC.
+For each EIS exposure we convolved the full CCD spectrum with the AIA effective area for the 193\,\AA\ channel.
+We also resampled the AIA images to better match the cadence and plate scale of the EIS data.
+We then cross correlated the EIS intensities along the slit with the the intensities in the resampled AIA image taken closest in time to the EIS exposure.
+We computed correlations over a range of positions close to the commanded pointing and recorded the position with the highest correlation.
+An example of co-aligned EIS and AIA intensities is shown in Figure \figref{fig:eis_aia}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.85\linewidth]{./figures/eis_aia_108.pdf}
+    \caption{Co-aligned EIS and AIA data.
+The left panel shows an AIA 193\,\AA\ image with the position of the EIS slit indicated by the black line.
+The center panel shows the EIS and AIA intensities along the slit.
+Note that the EIS intensities here are computed by convolving the spectrum with the AIA effective area.
+Intensities derived from Gaussian fits to the line profile were also computed.
+The right panel shows the EIS exposure in the vicinity of the \ion{Fe}{12} 195.119\,\AA\ line.
 }
-\colnumbers
-\startdata
-1991 & 600 & 100 \\
-1992 & 650 & 105 \\
-1993 & 550 & 103 \\
-1994 & 450 & 110 \\
-1995 & 410 & 112 \\
-1996 & 400 & 114 \\
-1997 & 525 & 115 \\
-1998 & 590 & 116 \\
-1999 & 575 & 115 \\
-2000 & 450 & 103 \\
-2001 & 490 &  90 \\
-2002 & 500 &  88 \\
-2003 & 450 &  90 \\
-2004 & 460 &  88 \\
-2005 & 440 &  79 \\
-2006 & 350 &  77 \\
-2007 & 325 &  70 \\
-2008 & 320 &  65 \\
-2009 & 190 &  68 \\
-2010 & 280 &  70 \\
-2011 & 275 &  68 \\
-2012 & 150 &  56 \\
-2013 & 140 &  55 \\
-\enddata
-\tablenotetext{a}{Adjusted for inflation}
-\tablenotetext{b}{Accounts for the change from page charges to digital quanta in April, 2011}
-\tablecomments{Note that {\tt \string \colnumbers} does not work with the 
-vertical line alignment token. If you want vertical lines in the headers you
-can not use this command at this time.}
-\end{deluxetable}
+    \label{fig:eis_aia}
+\end{figure}
 
-\section{Displaying mathematics} \label{sec:displaymath}
+The EIS slot rasters at the beginning and end of the observations were also co-aligned to AIA 193 \AA\ images, but using a slightly different technique.
+The EIS 195 \AA\ window was extracted for each slot position in the raster and the nearest AIA 193 \AA\ image in time was taken.
+The EIS metadata values for rotation and spatial sampling of the EIS slot were adjusted, to $1^\circ$ and $1.00 \times 0.99$ arcsec respectively, for all slot data, and the center field position of each slot pointing was determined by eye to achieve a good match.
+This rough pointing information was used to generate 2D helioprojective Cartesian coordinate arrays for the x and y coordinates of the image.
+The AIA data was interpolated to the EIS coordinates, then the SSW routine \verb+tr_get_disp+ was used to determine the residual shift between the EIS and AIA images in an automated way.
+These pixel shifts were then used to update the EIS coordinate arrays.
 
-\section{Revision tracking and color highlighting} \label{sec:highlight}
+FITS files containing the EIS slot raster and spectrograph sit-and-stare co-aligned coordinates arrays are available with the data release accompanying this publication.
+These co-aligned coordinates are only valid for the EIS 195 \AA\ wavelength because EIS has a systematic vertical shift with wavelength due to a small tilt of the grating \citep[e.g.][]{young09}.
+Coordinate shifts relative to this wavelength should be applied based on the \verb+eis_ccd_offset+ routine in SSW.
+Interested users are encouraged to obtain the original EIS data from JSOC or other sources and prep it with the latest routines for further for analysis.
 
-Authors sometimes use color to highlight changes to their manuscript in
-response to editor and referee comments.  In \aastex\ new commands
-have been introduced to make this easier and formalize the process.
+\subsection{DST/IBIS}
+The IBIS broad band images were aligned to HMI continuum images in order to determine the final IBIS coordinates.
+All co-alignment steps used the \code{chi2\_shift} cross correlation routine and then were independently verified using the \code{phase\_cross\_correlation} routine from the \code{skimage.registration} Python package.
+The co-alignment process found a $1.08^\circ$ rotation of the IBIS data to align the pixel array with the solar North-South axis, while the coordinates of the center IBIS pixel were determined to be $(-76.041, -52.032)$ at time 2017-03-21 14:47:05.164.
+The center-pixel coordinates for all other times were then calculated from that $(x,y,t)$ triplet using the \code{solar\_rotate\_coordinate} routine from SunPy 2.0.3.
+The final offsets from the IBIS self-alignment described in \secref{sec:ibisselfalign} and the rotation to align pixel axes with solar X-Y axes were simultaneously applied to both the broad band and narrow band data using the \code{affine\_transform} interpolation routine from Sunpy.
 
-The first method is through a new set of editing mark up commands that
-specifically identify what has been changed.  These commands are
-{\tt\string\added\{<text>\}}, {\tt\string\deleted\{<text>\}}, and
-{\tt\string\replaced\{<old text>\}\{<replaced text>\}}. To activate these
-commands the {\tt\string trackchanges} option must be used in the
-{\tt\string\documentclass} call.  When compiled this will produce the
-marked text in red.  The {\tt\string\explain\{<text>\}} can be used to add
-text to provide information to the reader describing the change.  Its
-output is purple italic font. To see how {\tt\string\added\{<important
-added info>\}}, {\tt\string\deleted\{<this can be deleted text>\}},
-{\tt\string\replaced\{<old data>\}\{<replaced data>\}}, and \break
-{\tt\string\explain\{<text explaining the change>\}} commands will produce
-\added{important added information}\deleted{, deleted text, and }
-\replaced{old data}{and replaced data,} toggle between versions compiled with
-and without the {\tt\string trackchanges} option.\explain{text explaining
-the change}
+Each IBIS FITS file contains data from a single exposure time, e.g., a single broad band and narrow band image pair.
+The final coordinates were saved in the WCS compliant CRVAL1 and CRVAL2 fields of the FITS header for each IBIS data file, which apply to both the broad band and narrow band images, as part of the primary FITS header.
+The broad band and narrow band data are saved in the first and second Image FITS extensions, respectively, along with additional header fields pertinent to each.
+Because of the limited FOV, disk-center location, and short duration $(\sim 2\unit{hr})$ of these data, we did not consider image distortion due to the curved surface of the Sun, as such corrections would enter at sub-pixel scales.\par
 
-A summary list of all these tracking commands can be produced at the end of
-the article by adding the {\tt\string\listofchanges} just before the
-{\tt\string\end\{document\}} call.  The page number for each change will be
-provided. If the {\tt\string linenumbers} option is also included in the
-documentcall call then not only will all the lines in the article be
-numbered for handy reference but the summary list will also include the
-line number for each change.
+The IBIS filenames have the format \texttt{IBIS.6563.YYYYMMDD\_HHMMSS\_NN.fits}, where the time information corresponds to the beginning of each spectral scan and the \code{\_NN} refers to the wavelength step of the file.
+This convention eases the analysis of data from specific wavelengths.
+\figref{fig:IBISgrid} shows representative IBIS data, including a broad band image of the solar granulation pattern and a subset of the wavelengths from the narrow band data.
+The blue circle and cross shows the ALMA FOV at this time.
 
-The second method does not have the ability to highlight the specific
-nature of the changes but does allow the author to document changes over
-multiple revisions.  The commands are {\tt\string\edit1\{<text>\}},
-{\tt\string\edit2\{<text>\}} and {\tt\string\edit3\{<text>\}} and they
-produce {\tt\string<text>} that is highlighted in bold red, italic blue and
-underlined purple, respectively.  Authors should use the first command to
-\edit1{indicated which text has been changed from the first revision.}  The
-second command is to highlight \edit2{new or modified text from a second
-revision}.  If a third revision is needed then the last command should be used 
-\edit3{to show this changed text}.  Since over 90\% of all manuscripts are
-accepted after the 3rd revision these commands make it easy to identify
-what text has been added and when.  Once the article is accepted all the
-highlight color can be turned off simply by adding the
-{\tt\string\turnoffediting} command in the preamble. Likewise, the new commands
-{\tt\string\turnoffeditone}, {\tt\string\turnoffedittwo}, and
-{\tt\string\turnoffeditthree} can be used to only turn off the 
-{\tt\string\edit1\{<text>\}}, {\tt\string\edit2\{<text>\}} and 
-{\tt\string\edit3\{<text>\}}, respectively.
+\begin{figure*}
+    \centering
+    \includegraphics[width=7in]{./figures/IBIS_ALMAcirc_grid}
+    \caption{Co-aligned IBIS data for a partial scan through the \halpha{} line.
+The scan began at 15:47:11.133UT and and lasted until 15:47:15.123, with approximately 0.165s between each narrow band image.
+The broad band data is in the upper left while remaining panels show a subset of the narrow band images.
+The blue circle and crosshair shows the ALMA field of view at 15:47:13 UT.}
+    \label{fig:IBISgrid}
+\end{figure*}
 
-Similar to marking editing changes with the {\tt\string\edit} options there
-are also the {\tt\string\authorcomments1\{<text>\}}, 
-{\tt\string\authorcomments2\{<text>\}} and
-{\tt\string\authorcomments3\{<text>\}} commands.  These produce the same
-bold red, italic blue and underlined purple text but when the
-{\tt\string\turnoffediting} command is present the {\tt\string<text>}
-material does not appear in the manuscript.  Authors can use these commands
-to mark up text that they are not sure should appear in the final
-manuscript or as a way to communicate comments between co-authors when
-writing the article.
+\subsection{ALMA}\label{sec:almaalign}
+As explained by \citet{2019Molnar}, variations in the Band-3 ALMA brightness temperature track variations in \halpha{} linewidth.
+We therefore co-aligned the ALMA data to the \halpha{} linewidths calculated using the method described in Section \secref{sec:linewidth}.
+The ALMA data were shifted and rotated to center the beam at the center of the pixel array and align solar north-south axis aligned with pixel columns.  
+The FOV center coordinates were then varied such that levelsets of the cotemporal ALMA and IBIS-\halpha{} data aligned at beginning of the ALMA data series at time 2017-03-21 15:42:13.  
+As with the IBIS data, the WCS compliant coordinate values `CRVAL1' and `CRVAL2' at all other times were calculated by rotating the co-aligned center pixel coordinates from the initial time using the Sunpy's \code{sunpy.physics.differential\_rotation.solar\_rotate\_coordinate()} routine.
 
-\section{Software and third party data repository citations} \label{sec:cite}
+\section{Analysis}\label{sec:analysis}
+\subsection{Overview}
+To get a baseline qualitative understanding of how the active area evolved leading up to our primary observations we applied the segmentation and feature tracking algorithms described in \citet{2012Tarr} to the $\approx330\times250\arcsec{}$ cutout of HMI data between 2017-03-19 00:00 and 2017-03-21 23:46UT.
+This analysis revealed fairly standard network behavior.
+Throughout the entire FOV, magnetic concentrations cyclically coalesce and fragment.
+On short timescales (several hours) the motion of flux concentrations appears coherent, but on longer time scales ($\sim1$ day) movement appears random.
 
-The AAS Journals would like to encourage authors to change software and
-third party data repository references from the current standard of a
-footnote to a first class citation in the bibliography.  As a bibliographic
-citation these important references will be more easily captured and credit
-will be given to the appropriate people.
+However, the observed motions are not completely random.
+Our observations are centered on the bipolar grouping (positive magnetic fields to the West, negative to the East) shown in Figure \ref{fig:SOTSP} right.
+Despite the continual fragmentation and coalescence, the bipole is present for the duration of the HMI data and is associated with persistent, short, bright coronal loops in the EUV and X-Ray data.
+As described below, it is likely that the bipole emerged as a cohesive unit that is well into the decay phase, but it may simply be a long-lasting random bipolar concentration. 
+For ease of language we will refer to it as ``the bipole.''
 
-The first step to making this happen is to have the data or software in
-a long term repository that has made these items available via a persistent
-identifier like a Digital Object Identifier (DOI).  A list of repositories
-that satisfy this criteria plus each one's pros and cons are given at \break
-\url{https://github.com/AASJournals/Tutorials/tree/master/Repositories}.
+Considered from a global perspective, the positive polarity is parasitic within a roughly circular medium-scale ($\sim250\arcsec{}$ diameter) negative polarity region. 
+The medium scale negative polarity region is itself surrounded by a larger scale, predominantly positive polarity region that extends across both sides of the solar equator.
+This magnetic configuration makes the bipole topologically isolated from larger scale features: magnetic domains are layered somewhat like shells in an onion and we are interested in the dynamics of the inner layers.
+This larger-scale configuration will inform MHD simulations to be presented in future work.
 
-In the bibliography the format for data or code follows this format: \\
+The pattern of a medium-scale dominant negative polarity surrounded by a larger scale positive polarity persisted for several solar rotations prior to our observations.
+The bipole we are looking at is likely the decaying remains of AR 12639 which emerged around 2017-02-24 at $\approx$(10S, 30W).
 
-\noindent author year, title, version, publisher, prefix:identifier\\
+Returning to the local scale of the bipole, overall during our observations it appears to be decaying, both by apparent direct cancellation between the two polarities and by fragmentation and separation of each polarity individually.
+The general decay of the bipole is complicated by two other factors: (1) nearby small-scale emergence, for example, around $(-475,-50)\arcsec{}$ at time 2017-03-19 13:45UT, acts to replenish the decaying flux of each polarity, and (2) surrounding network concentrations that do not seem associated with emergence also random-walk into the bipolar region and replenish lost flux.
 
-%% If you wish to include an acknowledgments section in your paper,
-%% separate it off from the body of the text using the \acknowledgments
-%% command.
+Finally, we note that immediately preceding our coordinated observations the parasitic positive polarity region of the bipole began an extended cycle of combined fragmentation and cancellation with the negative polarity of the bipole.
+This activity continued throughout our observations and likely drives some of the dynamics we observe.
+
+\subsection{IBIS Linewidths}
+\label{sec:linewidth}
+We characterized the spectral profile of \halpha{} at every spatial and temporal point of the IBIS data.
+Figure \ref{fig:linefitexample} shows a typical example of the spectral data (green crosses), including the Telluric oxygen line $\approx1.4\AA{}$ reward of the \halpha{} line center.
+Fitting the spectral line serves dual purposes.
+First, as stated above in \secref{sec:almaalign} and reported on by \citet{2019Molnar}, the \halpha{} linewidth is extremely useful for aligning the ALMA Band 3 data; we discuss this at length in the following subsections.
+Second, the fitting produces several interesting plasma diagnostics of its own, including Doppler shifts and opacity fluctuations.
+
+Our characterization followed the method of \citet{2009Cauzzi}.
+First, we created a smooth model, $\hfit[\lambda]$ of the normalized spectra\footnote{Spectra at each spatial pixel at a given time were normalized to the intensity of the first measured wavelength position averaged over the central $600\times600$ pixels.
+That wavelength is $6560.832$\AA{}, or $-1.9944$\AA{} relative to the center of the prefilter bandpass.} using the \scipy{} \fnc{interpolate} package, based on FITPACK.
+Second, we determine the location of the line center by fitting a 3-parameter Gaussian absorption profile to the central 11 points in the line core, spanning -0.7505 to 0.5687 \AA{} from the center of the IBIS prefilter:
+\begin{equation}
+    G[\lambda; b, \linecenter, a] = b- \sqrt{\frac{\log2}{\pi a^2}}\exp\Bigl(-\frac{(\lambda - \linecenter)^2}{a^2\log2}\Bigr)
+\end{equation}
+where $b$ is the continuum level, $\linecenter$ is the line center, and $a$ is the half-width-at-half-max value.  
+We only use the line center value $\lambda_0$ of this fit because the fit to the line center is fairly good even though the \halpha{} line profile is poorly represented by a Gaussian.  \par
+
+We combine the fitted line center and the spline model to define the remaining characteristics of the line.  
+The value of the spline model at line center defines the minimum line intensity, $\imin{}=\hfit[\linecenter{}]$.  
+Next, the line intensity at half the line depth is defined as the halfway point between the minimum intensity and average of the intensities at $\pm0.75$\AA{} from \linecenter{}: 
+\begin{equation}
+    \ihalf = \frac{1}{2}\Bigl(\frac{\hfit[\linecenter-0.75\text{\AA{}}]+\hfit[\linecenter+0.75\text{\AA{}}]}{2}+\imin \Bigr).
+\end{equation}
+Finally, the line width \linew{} is defined to be the difference between roots of the equation \mbox{$\hfit[\lambda]-\ihalf = 0$}, that is, the width of the line at intensity \ihalf.
+\figref{fig:linefitexample} shows an example of the fitting method applied to a single profile.\par
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figures/line-fit-example-figure.pdf}
+    \caption{An example of the line fitting method, applied to the spectra at pixel $ix,iy=400,550$ at time 14:47:07.
+The blue line with '+' symbols show the normalized spectra.
+The green dashed line shows the spline interpolation to the data.
+The orange line shows the gaussian fit to the spline model between $\approx-0.894$\AA{} and $0.8369$\AA{}.
+\imin{} is marked by a red $\times$, the line intensities at $\linecenter\pm0.75$\AA{} by the green and purple dots, their average by the multi-color dot, the width--defining intensity level by the red stars, and the resulting line width by the dashed red line.}
+    \label{fig:linefitexample}
+\end{figure}
+
+We have verified the correlation between \halpha{} line widths and ALMA Band-3 brightness temperature, as reported by \citet{2019Molnar}.
+\figref{fig:almaibis} shows an example, while an animation spanning the duration of the ALMA observations is available in the supplementary online material.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figures/IBIS_wdth_ALMA_tb_0100.png}
+    \caption{\halpha{} line-core widths from IBIS (left) and the ALMA band 3 brightness temperature (right) at time 2017-03-21 15:45:34.
+Contours of the ALMA brightness temperature are overlaid on both panels.
+The white dashed circle shows the effective extent of ALMA's FOV.
+An animation of this figure is available in the supplementary online material.}
+    \label{fig:almaibis}
+\end{figure*}
+
+\citet{2019Molnar} synthesized the radiative emission from a range of model atmospheres, representative of quiet-Sun to strong plage conditions, using the RH code \citep{2001Uitenbroek}.
+Those results suggest that the broadening of \halpha{} as the chromospheric temperature rises is primarily an opacity effect due to an enhanced number density of H atoms in the $n=2$ quantum state, as opposed to broadening by thermal effects.
+They explained this behavior, extensively referencing \citet{2012Leenaarts}, as follows \saj{colon?}.
+The \halpha{} source function is nearly uniform throughout the chromosphere.
+This feature gives \halpha{} its characteristic flat bottom, with fairly uniform intensity in wavelength moving away from line center, until a wavelength is reached at which the source function becomes sensitive to the photosphere, giving rise the the steep line wings.
+As the formation height of the line core increases, the transition to photospheric-dominated emission occurs further in wavelength from the line center.
+
+Now consider how this behavior changes as one varies the temperature of an atmospheric model.
+Moving from cooler to hotter models, two important things happen simultaneously \citep[see][Fig.~5]{2019Molnar}: (1) the $\tau=1$ surfaces for the \halpha{} line core and the ALMA Band 3 emission begin to coincide; and (2) the contribution functions for each line become more spatially localized higher in the atmosphere.
+Thus, in the hotter models, which produce the largest \halpha{} linewidths and highest ALMA Band 3 brightness temperatures, essentially all the \halpha{} absorption occurs in a thin range of heights at the interface between the chromosphere and transition region, and coincides with the ALMA Band 3 millimeter emission.
+However, the above \halpha{} formation behavior, and the resulting correspondence between \halpha{} and ALMA millimeter emission, eventually breaks down for the hottest models that are most similar to active-regions, when the \halpha{} source function is no longer flat.
+We do not expect this break down to occur for the region of enhanced network we have targeted in this data set, with the result that we find good correspondence between the \halpha{} line width and ALMA brightness temperature throughout our observations.
+\subsection{Interpretation of \halpha{} Doppler Shifts}
+
+The above argument explains the correlation between high brightness temperature ALMA Band 3 data and enhanced \halpha{} line widths, and the relation of both to enhanced photospheric magnetic concentrations.
+It also shows how broader linewidths and greater brightness temperatures correspond to greater heights in the solar atmosphere, and how the line formation affects our understanding of the plasma properties.
+The measured doppler velocities for regions with narrow linewidths should be systematically lower than doppler velocities from regions with greater linewidths.
+The narrower lines form over a broad range of heights, allowing for effective canceling of coherent doppler signals, while the broader lines form over a narrower range of heights, so the doppler signal better represents coherent mass motions from localized regions.
+
+My by-eye correlation between the doppler maps and the line-width maps seems to support this, but I haven’t done anything further with it.
+\latcomment{see email exchange 2020-02-20 between Tarr/Reardon/Uitenbroc/Momchil}.
+
+Also, I find a nearly gaussian distribution of doppler shifts of order $\pm0.05$\AA{} around the peak (FWHM), compared to line widths ranging from 0.9 to 1.3\AA{}.
+The width distribution is odd, but I could see it as two very roughly peaked gaussians, centered at 1 and 1.2\AA{}, both with FWHM $\pm0.05$\AA{}.
+That also makes for a consistent picture.
+
+We now turn to analyzing the temporal variations of these radiative diagnostics.
+
+\section{Conclusions}\label{sec:conclusion}
+The end
+
+\section{Noted dynamic events}
+We see numerous propagating disurbances in the \halpha{} linewidth.
+
+ALMA shows lots of oscillations, difficult to say if these are impulsive or not (ALMA is both low resolution and radiatively thick).
+
+Many brightenings in XRT. A few can be connected through to IBIS.
+\begin{description}
+    {\item[NuSTAR]-potential events}
+    \begin{itemize}
+        {\item 19:04}
+        {\item 19:30}
+    \end{itemize}
+    {\item[IBIS]-potential events}
+        \begin{itemize}
+            {\item 14:53-14:58: propagating linewidth enhancement (-75,-40), (scan 158 )}
+            {\item 15:15-15:18: likely bogus, I think data is too poor to tell}
+            {\item 15:589-16:02: inflow to center of region (-55,-55).  See $d\lambda$ = 0.0320$\rightarrow$0.069}
+            {\item 16:20-16:22: propagating wavetrain outward from center around (-50,-40).
+See running difference $d\lambda$ = -0.089, -0.075,0.057, 0.069.
+Shows up especially well blue-wing intensity images at $d\lambda = -0.1, -0.089\unit{nm}$.
+May start as early as 16:10?
+Go from 16:10-16:30}
+        \end{itemize}
+    {\item[XRT] blah}
+    {\item[ALMA] blah}
+    {\item[IRIS] blah}
+\end{description}
+
+The 16:10 to 16:30 event appears to show energy transfer between the chromosphere to the corona and back along two different paths.
+The even starts as a strong dimming the \halpha{} blue wing, see especially the $-0.089\unit{nm}$ channel.  
+The dimming progresses roughly from SE to NW along the filament channel between the polarities of the bipole.
+The ALMA data show cospatial enhanced temperatures during this time.
+The dynamic event then becomes visible the hotter and higher data channels, especially AIA 304\AA{} and 193\AA{} followed by XRT.
+In all of these the brightenings again progress from SE to NW along the filament channel.
+The hotter channels then show a second loop brightening that partially overlaps the first but then extends southward from the negative concentration of the bipole towards a small flux concentration near the edge of the ALMA field of view.
+Finally we see a co-spatial and -temporal dimming in the \halpha{} blue wing and enhanced temperatures in ALMA at the southern terminus of the secondary loop.
+
 \acknowledgments
+%DST
+The National Solar Observatory (NSO) is operated by the Association of Universities for Research in Astronomy, Inc. (AURA), under cooperative agreement with the National Science Foundation.  
+%IRIS
+IRIS is a NASA small explorer mission developed and operated by LMSAL with mission operations executed at NASA Ames Research center and major contributions to downlink communications funded by ESA and the Norwegian Space Center.
+%Hinode SOT/SP done in text
 
-We thank all the people that have made this AASTeX what it is today.  This
-includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
-Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
-Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
-for the new "modern" style design. Considerable help was provided via bug
-reports and hacks from numerous people including Patricio Cubillos, Alex
-Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
-Gagne.
+%ALMA
 
@@
 \vspace{5mm}
-\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
-CTIO:1.5m,CXO}
+\facilities{ALMA, Dunn(FIRS, IBIS), IRIS, SDO(AIA, HMI)}
 
@@
 %% authors a place to specify which programs were used during the creation of 
-%% the manusscript. Authors should list each code and include either a
+%% the manuscript. Authors should list each code and include either a
 %% citation or url to the code inside ()s when available.
 
-\software{astropy \citep{2013A&A...558A..33A}
-          }
+\software{astropy \citep{2013astropy,2018astropy} SHOULD INCLUDE: SUNPY, NUMPY, ADS, SSW}
 
@@
 
-\appendix
+\bibliographystyle{yahapj}
+\bibliography{references}
+%\comment{
+%\begin{thebibliography}{}
 
-\section{Appendix information}
+%\bibitem[Astropy Collaboration et al.(2013)]{2013A&A...558A..33A} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, A33
 
-\begin{thebibliography}{}
-
-\bibitem[Astropy Collaboration et al.(2013)]{2013A&A...558A..33A} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, A33
-
-\end{thebibliography}
-
+%\end{thebibliography}
+%}
 %% This command is needed to show the entire author+affilation list when

### 2021-09-22 figures/line_fit_example_figure.py

@@ -1,0 +1,70 @@
+import numpy as np
+import matplotlib.pyplot as plt
+#import matplotlib.animation as animation
+import os
+import sys
+import glob
+from scipy.interpolate import InterpolatedUnivariateSpline 
+from scipy.optimize import curve_fit 
+from scipy.optimize import fsolve       
+sys.path.append(os.path.expanduser('~/work/python_tools/'))       
+from read_ibis_rec import read_ibis_rec
+
+
+## gaussian
+def G(x,alpha):
+    ## alpha is the FWHM
+    return np.sqrt(np.log(2)/np.pi)/alpha*np.exp(-(x/alpha)**2*np.log(2))
+
+## gaussian fit
+def gf(x, b, x0, alpha):
+    # b: bias (we don't measure continua)
+    # x0: center
+    # alpha: width
+    return b-G(x-x0,alpha)
+
+idat = read_ibis_rec('/Users/lucastarr/DST_DRIVE/201703_DST/21_march_2017/ibis_tmp/results_000/6563_nb734.sav') 
+ix = 400
+iy = 400
+
+tfiles = glob.glob('/Users/lucastarr/DST_DRIVE/201703_DST/21_march_2017/ibis_tmp/results_000/original_datetime/s???.ScienceObservation_datetime_nb.npy')
+time = np.load(tfiles[734])[13][1]
+DST_date_str='%Y-%m-%dT%H:%M:%S.%f'
+dt_obj = datetime.datetime.strptime(time, DST_date_str)
+
+halphaline = idat[0].img[:,iy,ix]/idat[0].img[0,0,0] 
+s = InterpolatedUnivariateSpline(idat[0].relwave, halphaline)
+gopt, gcov = curve_fit(gf, idat[0].relwave[6:20],halphaline[6:20],p0 = [1.,0.0,0.5])
+
+new_lam = np.linspace(idat[0].relwave[0],idat[0].relwave[-1],200)
+
+fig,ax = plt.subplots(figsize=(6,6))
+
+ax.plot(idat[0].relwave, halphaline,'+-')
+ax.plot(new_lam, s(new_lam), 'g--')
+ax.plot(idat[0].relwave, gf(idat[0].relwave,gopt[0],gopt[1],gopt[2])) 
+i_lmin = s(gopt[1])
[…]

### 2021-11-01 Paper1.tex
Updates from Overleaf

@@
 
-% Nick stuff, feel free to change at will, I was just getting my thoughts out.
 \subsection{ALMA}
-\paragraph{ALMA background} The Atacama Large Millimeter Array (ALMA) is a radio interferometer with current frequency coverage spanning 84 to 950 GHz.
+\paragraph{ALMA background} The Atacama Large Millimeter Array (ALMA) is a radio interferometer with current frequency coverage spanning 84 to 950 GHz \citep{2009WootenThompson_ALMA}.
 ALMA is constituted of 66 telescope dishes, 54 with a diameter of 12 meters, and 12 with a diameter of 7 meters.
-These 66 dishes are arranged as such to ensure that ALMA had suitable sensitivity to large scale diffuse emission, this is aided by the high density of centrally located dishes, and excellent resolution to small scale features, this is achieved with the dishes at high distance.
+These 66 dishes are arranged as such to ensure that ALMA has suitable sensitivity to large-scale diffuse emission, achieved by the high density of centrally located dishes, and excellent resolution to small scale features, achieved with the dishes at long distance.
 The ALMA observations presented in this work were in the ALMA observing Band 3, which corresponds to a central frequency of 100 GHz, and a total bandwidth of 18 GHz about that central frequency.
 At this frequency and array configuration, our approximate resolution is 2$\arcsec$ on the sky.
-Our integration time used was 2 seconds and the entire observation, including the target field and calibrators, lasted for 1.03 hours.
+Our integration time is 2 seconds, and the entire observation, including the target field and calibrators, had a duration of 1.03 hours.
 
-\paragraph{ALMA calibration}
-\paragraph{ALMA self-calibration}
+\paragraph{ALMA calibration} The ALMA Band 3 data were cross-calibrated using the standard ALMA pipeline Cycle 4 version\footnote{For a thorough description of the tasks and philosophy see: ALMA Pipeline Team, 2017, ALMA Science Pipeline User’s Guide, ALMA Doc 4.13v2.0}.
+in CASA version 4.7.2 \citep{casa}.
+The observations were taken with the strong millimeter source, J2253+1608, approximately 6.5 Jy in ALMA Band 3, used for the bandpass and flux calibration, and the strong millimeter source, QSO\_B0003-066, approximately 2 Jy in ALMA Band 3, used for the phase cross calibration.
+The initial cross-calibration eliminated 4 dishes due to unreasonably elevated system temperatures, and produced images of a reasonable quality, but still suffering from some poor calibration artifacts.
+
+\paragraph{ALMA self-calibration} In order to improve the fidelity of our images, we then phase-only self-calibrate the data.
+The phase-only self-calibration is an iterative process in which we took the following steps.
+We first produce a cleaned map of the data, but we clean only to a relatively modest level, to ensure all flux captured in the clean model is real.
+We then do a phase-only gaincal over a large time-range, in the first iteration this was a scan length (5 minutes), using the clean model, and apply this calibration to the data.
+We do this process iteratively, where in each iteration we clean to a lower flux threshold, and shorten the time-range used in the phase-only self calibration.
+We terminate the process when there is no decrease in out-of-field r.m.s.
+noise, and the image shows little-to-no improvement.
+The improvements caused by this process are the elimination of PSF pattern relics in the image, and the sharpening of the image, which is why this process if often compared to the effect of focusing a telescope or microscope.
+
 \paragraph{ALMA issues with phase-center}

### 2021-12-23 Paper1.tex
update Dec 23 2021

@@
 \documentclass[twocolumn]{aastex62}
-
+\usepackage{amssymb,amsmath,amsopn}
 %% The default is a single spaced, 10 point font, single spaced article.
@@
 %% Reintroduced the \received and \accepted commands from AASTeX v5.2
-\received{January 1, 2018}
-\revised{January 7, 2018}
+\received{January 1, 2022}
+\revised{January 7, 2022}
 \accepted{\today}
@@
 
-\title{Transient brightenings observed with multiple instruments}
+\title{A publicly available multi-observatory data set of an enhanced network patch from the Photosphere to Corona}
 \correspondingauthor{Adam R. Kobelski}
-\email{adam.kobelski@mail.wvu.edu}
+\email{adam.kobelski@nasa.wvu.edu}
 
@@
 %\email{ltarr@nso.edu}
-\author[0000-0001-5459-2628]{Sarah Jaeggli}
+\author[0000-0001-5459-2628]{Sarah A. Jaeggli}
 \affiliation{National Solar Observatory}
@@
 New instruments sensitive to chromospheric radiation at X-ray, UV, Visible, IR, and sub-mm wavelengths have become available that significantly enhance our ability to understand the bi-directional flow of energy through the chromosphere.
-In this paper, we showcase and combine a new dataset utilizing a large number of these instruments to obtain multi-wavelength chromospheric observations capable of improving our understanding of the connectivity between the photosphere and the corona in the chromosphere via transient brightenings and wave signatures.
-This comprehensive study provides one of the most complete views of chromospheric activity related to small scale brightenings in the corona and chromosphere to date.
-SOME NUMBERS, SCIENCE CONCLUSIONS.
-
+We describe the calibration, coalignment, initial results, and public release of a new data set combining a large number of these instruments to obtain multi-wavelength photospheric, chromospheric, and coronal observations capable of improving our understanding of the connectivity between the photosphere and the corona via transient brightenings and wave signatures.
+The observations center on a bipolar region of enhanced network magnetic flux near disk center on SOL2017-03-17T14:00-17:00.
+The comprehensive data set provides one of the most complete views of chromospheric activity related to small scale brightenings in the corona and chromosphere to date.
+Our initial analysis shows strong spatial correspondence between the areas of broadest width of the Hydrogen$\alpha$ spectral line and the hottest temperatures observed in ALMA Band 3 radio data.
+The correspondence persists for the duration of cotemporal obserations ($\approx 60\unit{m}$).
+Numerous transient brightenings were observed in multiple data series.
+We highlight a single well observed transient brightening along a set of thin filamentary features with a duration of 20 minutes.
+The timing of the peak intensity transitions from the cooler (ALMA, 7000K) to hotter (XRT, 3MK) data series.
 \end{abstract}
@@
 The methods of transporting energy from the photosphere through the chromosphere to the million degree corona have been debated since the discovery of the hot corona \citep[][]{1933LyotMarshall, 1939Grotrian}.
-The underlying problem is that thermal conduction, which is very efficient in solar plasmas, will transport energy from the corona to the chromosphere, so the energy in the corona must constantly be resupplied.
+The underlying problem is that thermal conduction, which is very efficient in solar plasmas, will transport energy from the hot corona to the cool chromosphere from which it rapidly radiates away, so the energy in the corona must constantly be resupplied.
 One of the early ideas for this transport of energy was via wave activity through hydrodynamic shocks \citep[][]{1949Schatzman} and later, once the central role of magnetic fields on the Sun was fully realized, by magnetoacoustic or Alfv\'en waves \citep{1961Osterbrock}.
@@
 \citet{1997GaryEA} determined that the small scale-brightenings exhibit the same signatures of particle acceleration as larger solar flares and concluded that many of the transient brightenings (TBs) were also products of magnetic reconnection.
-\latcomment{Reference some of the NuSTAR or Foxi work about this?}
+The details of this connection could have important ramifications for some coronal heating theories,nand is thust still under active study (as seen by the work of Hannah et al, NuStar and MAGIXs, FOXSI among others).
 A key suggestion of the Parker nanoflare model was that the reconnection would occur due to substructure in the magnetic field lines, in which the observed loops consist of many unresolved braided magnetic strands.
@@
 In this paper, we present a unique, robust, and extensive data set with which to study the flow of energy through the chromosphere and the interplay between transients and wave activity.
+Calibrated and coaligned data in FITS format with WCS compliant coordinates are available through a publicly accessible archive hosted at the National Solar Observatory \url{https://share.nso.edu/shared/dkist/ltarr/kolsch/}.
 Even though the data set is of a quiescent solar region, it displays notable dynamics from the photosphere to the corona. 
@@
 The type of analysis we propose has been performed for active regions and strong plage, \emph{but not quiescent regions}. 
-Since this data set probes each layer of the Sun in multiple wavelengths, heights, temperatures, and methodologies, it can provide multiple ground-truths and perspectives for which to compare to models of chromospheric energy flow and transfer in later papers.
+Since this data set probes each layer of the Sun in multiple wavelengths, heights, and temperatures, it can be studied with distinct methodologies, and can provide multiple ground-truths and perspectives for which to compare to models of chromospheric energy flow and transfer in later papers.
 
 The data set includes photospheric magnetic field information from the Helioseismic and Magnetic Imager \citep[HMI,][]{2012SchouEA_HMI} as well as imaging from the Atmospheric Imaging Assembly \citep[AIA,][]{2012LemenEA_AIA} on board the Solar Dynamics Observatory \citep[SDO,][]{2012PesnellEA_SDO}; photospheric magnetic field data from the Solar Optical Telescope \citep[SOT,][]{2008TsunetaEA_SOT}, coronal X-ray imaging from the X-Ray Telescope \citep[XRT,][]{2007GolubEA_XRT}, and EUV spectra from EIS \citep{2007CulhaneEA_EIS} on board the {\it Hinode} spacecraft \citep[][]{2007KosugiEA_Hinode}; chromospheric images and spectra from IRIS \citep{2014DePontieuEA_IRIS}; spectral images from the  Interferometric BIdimensional Spectropolarimeter \citep[IBIS,][]{2006Cavallini_IBIS} and infrared spectropolarimetry from the Facility InfraRed Spectropolarimeter \citep[FIRS,][]{2010JaeggliEA_FIRS} at the Dunn Solar Telescope (DST); and millimeter wave information from the Atacama Large Millimeter Array \citep[ALMA,][]{2009WootenThompson_ALMA, 2010HillsEA_ALMA2}.
+For consistency, we refer each individual instrument's collected data as a \emph{data series} and the full collection of data series as the data set.
 
 In this paper, we describe the reduction of the imaging and spectral observations, as well as the co-alignment between instruments. 
-We then interpret and compare activity between atmospheric layers, though a more thorough analysis is forthcoming.  
-We give details of the observations in Section~\ref{sec:data}, their co-alignment in Section~\ref{sec:coalign} and their analysis in Section~\ref{sec:analysis}, with concluding remarks in \ref{sec:conclusion}.
+We then compare activity between atmospheric layers and provide a preliminary interpretation. 
+More thorough analyses are forthcoming. 
+We give details of the observations in Section~\ref{sec:data}, their co-alignment in Section~\ref{sec:coalign}, some preliminary analysis in Section~\ref{sec:analysis}, and concluding remarks in \ref{sec:conclusion}.
 
@@
 \subsection{Overview and Coordination}
-The data sets presented in this work resulted from a large coordination campaign that was keyed to the ALMA observations and encompassed a suite of ground- and space-based facilities operated by different organizations.
-The observations occurred during one of the first coordinated campaigns to support PI-led solar ALMA observations.
-Due to constraints in the ALMA scheduling, the exact timings and pointings could only be determined the day before the actual observations, with the result that there is not always complete temporal or spatial overlap between each facility.
-Given these constraints, the coverage is, in general, fairly good.
-
-\figref{fig:coordination} presents an overview the temporal and spatial overlap between the various instrument channels during the time of the ALMA observations. 
-In the upper panel we have ordered the instruments in the vertical direction roughly according to height in the solar atmosphere.
-In addition to the times shown here, SOT, EIS, and XRT took observations of this same region for several days leading up to the ALMA observing window.
-Fortuitously, NuSTAR also observed this region and detected two small flares around 19:00 and 19:30 UT \citep{2018Kuhar}.
-The lower left panels show the approximate fields-of-view (FOV) of the various instruments overlaid on an AIA 193\AA{} image using the same colors as the upper panel, with the left showing the full Sun and the right a zoomed in region.
 \begin{figure}
@@
 \end{figure}
+The data series presented in this work resulted from a large coordination campaign that was keyed to the ALMA observations and encompassed a suite of ground- and space-based facilities operated by different organizations.
+The observations occurred during one of the first coordinated campaigns to support PI-led solar ALMA observations.
+Due to constraints in the ALMA scheduling, the exact timings and pointings could only be determined the day before the actual observations, with the result that there is not always complete temporal or spatial overlap between each facility.
+Given these constraints, the coverage is, in general, fairly good.
+
+Figure \ref{fig:coordination} presents an overview the temporal and spatial overlap between the various instrument channels during the time of the ALMA observations. 
+In the upper panel we have ordered the instruments in the vertical direction roughly according to height in the solar atmosphere.
+In addition to the times shown here, SOT, EIS, and XRT took observations of this same region for several days leading up to the ALMA observing window, while SDO and AIA provide near-continuous observations in a variety of wavelengths, as always.
+The lower left panels show the approximate fields-of-view (FOV) of the various instruments overlaid on an AIA 193\AA{} image using the same colors as the upper panel, with the left showing the full Sun and the right a zoomed in region.
+
+Figure \ref{fig:coordination2} shows a representative sample of coaligned images from each of the data channels and provides an overview of the target region on the Sun.
+The images are approximately co-temporal at 16:27UT and are taken partway though a transient brightening event.
+From left to right and top to bottom (and roughly moving from the photosphere through the chromosphere and into the corona) the panels show: 
+\begin{itemize}
+    {\item (SOT) The photospheric magnetic field including a bipolar region of enhanced network flux}
+    {\item (SOT) The solar granulation pattern, including some minor disruptions by the enhanced network concentrations}
+    {\item (ALMA) Plasma temperature variations, with hotter/brighter areas roughly coincident with the photospheric magnetic field concentrations}
+    {\item (IBIS) \halpha{} blue wing, which shows some dynamic spicules (dark) and the magnetic concentrations (bright)}
+    {\item (IBIS) \halpha{} line center, which shows a central sigmoidal filament above the magnetic polarity inversion line}
+    {\item (IRIS) Si IV intensity, which shows transient brightenings throughout the FOV, yet mostly concentrated above the enhanced network flux}
+    {\item (AIA) 304\AA{} emission, which shows multiple loop brightenings against background of structured emission}
+    {\item (AIA) 193\AA{} emission showing multiple loop brightenings}
+    {\item (XRT) X-ray emission showing multiple transient strands}
+\end{itemize}
+We discuss this event in more detail in Section~\ref{sec:analysis} below.
+NuSTAR also observed this region and detected two small flares around 19:00 and 19:30 UT \citep{2018Kuhar}, confirming continued X-ray activity after the end of our primary coordinated observations, although we do not condsider the NuSTAR observations in the current study.
+The remaining subsections describe each data series from the coordinated observations.
 \begin{figure}
@@
     \caption{Representative sample of co-aligned images. The SOT data has been rotated to align with the coordinate time of the IBIS data. The ALMA data ranges from $\pm$some number of K}
-    \label{fig:coordination}
+    \label{fig:coordination2}
 \end{figure}
@@
 The Level 1 AIA data was downloaded from the Joint Science Operations Center (JSOC)\footnote{\url{http://jsoc.stanford.edu/}}, updated to Level 1.5 using \fnc{aia\_prep.pro} as described in the SDO Analysis Guide.
-We also selected a subregion that fully encompassed the ALMA target using the SSW cutout service\footnote{\url{https://www.lmsal.com/get_aia_data/}; see also \S4.3 of the SDO Analysis Guide.} for a region approximately $300\arcsec\times300\arcsec$ for the duration of the other datasets (14:00-17:00 UT on 2017-03-21).
+We also selected a subregion that fully encompassed the ALMA target using the SSW cutout service\footnote{\url{https://www.lmsal.com/get_aia_data/}; see also \S4.3 of the SDO Analysis Guide.} for a region approximately $300\arcsec\times300\arcsec$ for the duration of the other data series (14:00-17:00 UT on 2017-03-21).
 The 193 \AA\ channel of AIA was primarily used for co-alignment and to provide full-disk context for the other observations.  
-The 193 \AA\ bandpass includes \ion{Fe}{12} and \ion{Fe}{24} lines which form in the corona and hot plasma at log(T)=6.2 and 7.3 respectively.
+The 193 \AA\ bandpass includes \ion{Fe}{12} and \ion{Fe}{24} lines which form in the corona and hot plasma at log(T)=6.2 and 7.3 respectively, as described in \citet{2012Boerner} and \citet{2014Boerner}.
 
@@
 To ease later analysis, we derotated all HMI data so that the solar North-South axis aligned with columns of the data array, with North pointing upward, but kept the spatial scaling of the original HMI data.
-The typical extra step of spatially-rescaling the data to match AIA  has little benefit for use given that our various datasets include many different spatial samplings.
+The typical extra step of spatially-rescaling the data to match AIA  has little benefit in the present context given that our various data series include many different spatial samplings.
 
@@
 \paragraph{ALMA background} The Atacama Large Millimeter Array (ALMA) is a radio interferometer with current frequency coverage spanning 84 to 950 GHz \citep{2009WootenThompson_ALMA}. 
-ALMA is constituted of 66 telescope dishes, 54 with a diameter of 12 meters, and 12 with a diameter of 7 meters.
-These 66 dishes are arranged as such to ensure that ALMA has suitable sensitivity to large-scale diffuse emission, achieved by the high density of centrally located dishes, and excellent resolution to small scale features, achieved with the dishes at long distance.
+ALMA is constituted of 66 telescope dishes: 54 with a diameter of 12 meters, and 12 with a diameter of 7 meters. 
+These 66 dishes are arranged to ensure that ALMA has suitable sensitivity to large-scale diffuse emission, achieved by the high density of centrally located dishes, and excellent resolution to small scale features, achieved with the dishes at long distance.
+For this particular observation, ALMA was in its most compact configuration (C43-1), which limits the small scale resolution, but provides the best available resolution on larger scales, and also minimizes issues caused by water vapor in the Earth's atmosphere above the telescope.
 The ALMA observations presented in this work were in the ALMA observing Band 3, which corresponds to a central frequency of 100 GHz, and a total bandwidth of 18 GHz about that central frequency. 
@@
 in CASA version 4.7.2 \citep{casa}.
-The observations were taken with the strong millimeter source, J2253+1608, approximately 6.5 Jy in ALMA Band 3, used for the bandpass and flux calibration, and the strong millimeter source, QSO\_B0003-066, approximately 2 Jy in ALMA Band 3, used for the phase cross calibration.
+The observations were flux calibrated with the strong millimeter source, J2253+1608, approximately 6.5 Jy in ALMA Band 3, used for the bandpass and flux calibration, and the strong millimeter source, QSO\_B0003-066, approximately 2 Jy in ALMA Band 3, used for the phase cross calibration.
 The initial cross-calibration eliminated 4 dishes due to unreasonably elevated system temperatures, and produced images of a reasonable quality, but still suffering from some poor calibration artifacts.
+More details on the specifics of ALMA solar calibration are described in \citet{2017ShimojoEA_ALMASolarInt} and \citet{2017WhiteEA_ALMASD}.
+\paragraph{ALMA self-calibration} In order to improve the fidelity of our images we then phase-only self-calibrate the data. 
+The phase-only self-calibration is an iterative process. 
+We first produce a cleaned map of the data, but we clean only to a relatively modest level, to ensure all flux captured in the clean model is real. 
+We then do a phase-only \fnc{gaincal} over a large time-range, in the first iteration this was a scan length (5 minutes), using the \fnc{clean} model, and apply this calibration to the data. 
+We perform this process iteratively, where in each iteration we clean to a lower flux threshold and shorten the time-range used in the phase-only self calibration. 
+We terminate the process when there is no decrease in out-of-field r.m.s. noise and the image shows little-to-no improvement. 
+The improvements caused by this process are the elimination of PSF pattern relics in the image and sharpening of the image, which is why this process if often compared to the effect of focusing a telescope or microscope.\par
 
-\paragraph{ALMA self-calibration} In order to improve the fidelity of our images, we then phase-only self-calibrate the data.
-The phase-only self-calibration is an iterative process in which we took the following steps.
-We first produce a cleaned map of the data, but we clean only to a relatively modest level, to ensure all flux captured in the clean model is real.
-We then do a phase-only gaincal over a large time-range, in the first iteration this was a scan length (5 minutes), using the clean model, and apply this calibration to the data.
-We do this process iteratively, where in each iteration we clean to a lower flux threshold, and shorten the time-range used in the phase-only self calibration.
-We terminate the process when there is no decrease in out-of-field r.m.s.
-noise, and the image shows little-to-no improvement.
-The improvements caused by this process are the elimination of PSF pattern relics in the image, and the sharpening of the image, which is why this process if often compared to the effect of focusing a telescope or microscope.
-
-\paragraph{ALMA issues with phase-center}
+For unknown reasons, the phase-center of these specific observations were shifted from the expected beam center, causing an apparent misalignment between the center of the field of view of and the contrast center of the observation.
+Due to the co-alignment methods described below, this is not of particular concern, but is relevant in case of re-calibration.\par
 
@@
 IBIS is a dual Fabry-Perot interferometer- (FPI-) based imaging spectropolarimeter that was mounted at the Dunn Solar Telescope.
-The FPI cavity is tuned to transmit a narrow bandpass $(\approx 2.4\unit{pm})$, and the tuning is modulated to step the bandpass over the wavelength range of the line.
+The FPI cavity is tuned to transmit a narrow bandpass $(\approx 2.4\unit{pm})$, and the tuning is modulated to step the bandpass over the wavelength range of the spectral line, in this case the Hydrogen-alpha line (\halpha{}) at $656.3\unit{nm}$.
 We used IBIS in spectal-only mode (no polarimetry) with a circular field stop of approximately 90\arcsec{} diameter.
@@
 See documentation at \url{https://github.com/kreardon/IBIS.git}.}, which resulted in an improved estimate of the gain for each spatial and spectral point throughout the narrow band datacube.
-As a final calibration step, we used the KISIP code \citep{2008WoegerSPIE,2008WoegerEA_Speckle} to perform a speckle reconstruction of the data using the IBIS broad band images that are taken strictly co-temporally with the narrow band images; the broad band data is specifically designed for this purpose\citep{2008Cauzzi}.\par
+As a final calibration step, we used the KISIP code \citep{2008WoegerSPIE,2008WoegerEA_Speckle} to perform a speckle reconstruction of the data using the IBIS broad band images that are taken strictly co-temporally with the narrow band images; the broad band data is specifically designed for this purpose \citep{2008Cauzzi}.\par
 
@@
     {\item We generated a reference image by taking the running-average of the previous 5 registered ``good'' scans through the spectral line: at 26 images per scan, the average involves 130 broad band images.
-    The initial average reference image was taken to be the average of the first spectral scan from the dataset.}
+    The initial average reference image was taken to be the average of the first spectral scan from the data series.}
     {\item We used \texttt{chi2\_shift} to determine the spatial offset between each of the broad band images in a scan and the average reference image.}
@@
 
-The above method allowed essentially all 46,800 frames to be co-aligned while being robust against the occasional loss of AO during brief periods of poor seeing.\par
+The above method allowed essentially all 46,800 frames to be co-aligned while being robust against the occasional loss of AO during periods of poor seeing.\par
 
 \subsection{DST/FIRS}
+FIRS is a high dispersion dual-beam spectropolarimeter with the ability to operate simultaneously at visible (6302 \AA) and infrared (10830 or 15650 \AA) wavelengths.
+FIRS has a scanning mirror and a variety of reflective slit units that can provide optional multi-slit capability for highly efficient raster scans of the solar surface.
+The light reflected from the mirrored slit unit can be reimaged to provide context during observations.
+As a facility instrument at the Dunn Solar Telescope, FIRS can receive a seeing-stabilized image provided by the high-order adaptive optics system.
+
 During the coordinated observations, FIRS first conducted a raster observation from 14:46:47 to 15:00:54 UT (08:46:47 to 11:00:54 am MDT).
@@
 In this configuration the spectrograph was able to cover a 40 \AA\ bandpass centered at 10834 \AA.
-This region contains the Si I and He I 1083 nm lines commonly used for spectropolarimetry, as well as several other solar and telluric lines.
-The spectral dispersion of 3.86 pm/pixel is approximately equal to the spectral resolution of the instrument at this wavelength, based on laser profile measurements \citep{2011Jaeggli_PHD}.
+This region contains the Si I and triplet He I lines commonly used for photospheric and chromospheric  spectropolarimetry, as well as several other solar and telluric lines.
+The spectral sampling of 3.86 pm/pixel is approximately equal to the spectral resolution of the instrument at this wavelength, based on laser profile measurements \citep{2011Jaeggli_PHD}.
 An exposure time of 125 msec was used to keep counts within the range of linear behavior for the HgCdTe detector.
@@
 A flat field for the science data was constructed using an observation of disk center with randomized motion to blur out spatial features.
-All of the images from this dataset were corrected for linearity, dark subtracted, and averaged together.
+All of the images from this data series were corrected for linearity, dark subtracted, and averaged together.
 The geometric correction was used to convert the spectrum between spatial/spectral and detector coordinates.
@@
 While the intended cadence was 4s, automatic exposure control increased the exposure time, which slowed the cadence to 16s per image.
-This large data set was prepped \citep[][]{2014KobelskiEA_xrtprep} and the methods of \citet{2015YoshimuraMcKenzie_XRTcoalign} were used to estimate offsets for co-alignment to the data to other instruments.
-Cross-correlation techniques \citep[such as {\tt tr\_get\_disp.pro} in SolarSoft;][]{1998FreelandHandy_SSW} are used to remove instrumental jitter and to self-align the XRT data with itself.
-\begin{figure}[b]
-\centering
-\includegraphics[width=0.9\linewidth]{figures/img0070}
-\caption{Reverse color and scaled XRT Al\_poly image from 16:32:14.6, when all instruments were observing.
-The blue contours show locations where TBs were detected throughout the data set from 16:11:00 - 17:22:37.
-The black circle is the approximate FOV of IBIS, the purple lines the slit positions of IRIS, and the orange box the slit location of EIS.
-While the slits are not directly on the bulk of the detections, they are located near the footpoints of detected X-ray activity.}\label{fig:xrt}
-\end{figure}
-
-The XRT data allow us to see the brightest thermal features in the region, which can be seen in Figure~\ref{fig:xrt}.
-Similar to the methods discussed in \citet{2014KobelskiEA_XRTTBs} and \citet{2014KobelskiMcKenzie_HiC}, we have searched for small, dynamic brightenings in the data.
-We can then extract light curves for the brightenings.
-In this data set, over 30 individual brightenings were found, most of which were found within the FOVs (spatially and temporally) of the the other instruments.
-As seen in Figure~\ref{fig:xrt}, a few TBs appear to line up with the locations of the EIS and IRIS slits, though it is important to note that full co-alignment between instruments has not yet been performed.
-Further analysis will be able to better detect and connect the TB activity and to determine whether there is increased and co-located chromospheric activity before and/or after these events.
+This large data series was prepped \citep[][]{2014KobelskiEA_xrtprep} and the methods of \citet{2015YoshimuraMcKenzie_XRTcoalign} were used to estimate offsets for co-alignment to the data to other instruments.
+Cross-correlation techniques \citep[such as {\tt tr\_get\_disp.pro} in SolarSoft;][]{1998FreelandHandy_SSW} were utilized to further remove instrumental jitter and to self-align the XRT data with itself.
 
 \section{Co-alignment} \label{sec:coalign}
-Co-aligning the various instruments was a challenge.  \figref{fig:coalign} graphically depicts how each data set was coaligned.
-Our general approach was to use the broad wavelength and height coverage of the various HMI and AIA channels as a ``ground-truth'' mapping between solar coordinates and morphological features seen within each dataset.
 \begin{figure}[b]
@@
 \end{figure}
+
+Co-aligning the various instruments was a challenge.  
+\figref{fig:coalign} graphically depicts how each data series was coaligned.
+Our general approach was to use the broad wavelength and height coverage of the various HMI and AIA channels as a ``ground-truth'' mapping between solar coordinates and morphological features seen within each data series.
 The 2012 Venus transit allowed subarcsecond alignment of all the AIA and HMI channels\footnote{See the SDO Data Analysis Guide at \url{https://www.lmsal.com/sdodocs/doc/dcur/SDOD0060.zip/zip/entry/}, \S{}7.1 in the Sept 14, 2020 version of the document.}, which has since been maintained using Mercury transit observations, making SDO an excellent resource for this task.
-Alignment was then verified by checking against datasets that had not been explicitly aligned with each other.
+Alignment was then verified by checking against data series that had not been explicitly aligned with each other.
 For example, the IBIS broadband images were aligned to HMI continuum data and then that alignment was verified by checking the correspondence of enhanced emission in the \halpha{} line wings to the HMI magnetograms, SOT magnetograms, and UV emission in the 1600 and 1700\AA{} AIA channels.
 
-Each data set has different temporal and spatial samplings and physical extent so no attempt was made to resample images from each instrument to a common temporoal/spatial grid.  
-Instead, the reduced and co-aligned datasets make use of the World Coordinate System (WCS) variant for solar physics defined in \citet{2006Thompson} and included in the FITS headers.  
-All data in this work uses helioprojective-cartesian coordinates, which can be transformed to any other coordinate system using standard routines in SSW, astropy, or sunpy.\par
+Each data series has different temporal and spatial samplings and physical extent so no attempt was made to resample images from each instrument to a common temporoal/spatial grid.  
+Instead, the reduced and co-aligned data series make use of the World Coordinate System (WCS) variant for solar physics defined in \citet{2006Thompson} and included in the FITS headers.  
+All data in this work uses helioprojective-cartesian coordinates, which can be transformed to any other coordinate system using standard routines in \fnc{SSW}, \fnc{astropy}, or \fnc{sunpy}.\par
 
@@
 The left panel shows an AIA 193\,\AA\ image with the position of the EIS slit indicated by the black line.
+The AIA image was taken at 14:21:16:840, and the EIS image from 14:21:28:000.
 The center panel shows the EIS and AIA intensities along the slit.
@@
 
-The IBIS filenames have the format \texttt{IBIS.6563.YYYYMMDD\_HHMMSS\_NN.fits}, where the time information corresponds to the beginning of each spectral scan and the \code{\_NN} refers to the wavelength step of the file.
-This convention eases the analysis of data from specific wavelengths.
 \figref{fig:IBISgrid} shows representative IBIS data, including a broad band image of the solar granulation pattern and a subset of the wavelengths from the narrow band data.
@@
 As explained by \citet{2019Molnar}, variations in the Band-3 ALMA brightness temperature track variations in \halpha{} linewidth.
-We therefore co-aligned the ALMA data to the \halpha{} linewidths calculated using the method described in Section \secref{sec:linewidth}.
+We therefore co-aligned the ALMA data to the IBIS-\halpha{} linewidths calculated using the method described in Section \secref{sec:linewidth}.
 The ALMA data were shifted and rotated to center the beam at the center of the pixel array and align solar north-south axis aligned with pixel columns.  
-The FOV center coordinates were then varied such that levelsets of the cotemporal ALMA and IBIS-\halpha{} data aligned at beginning of the ALMA data series at time 2017-03-21 15:42:13.  
-As with the IBIS data, the WCS compliant coordinate values `CRVAL1' and `CRVAL2' at all other times were calculated by rotating the co-aligned center pixel coordinates from the initial time using the Sunpy's \code{sunpy.physics.differential\_rotation.solar\_rotate\_coordinate()} routine.
+The FOV center coordinates were then varied such that levelsets of the cotemporal ALMA and \halpha{} data aligned at beginning of the ALMA data series at time 2017-03-21 15:42:13.  
+As with the IBIS data, the WCS compliant coordinate values `CRVAL1' and `CRVAL2' at all other times were calculated by rotating the co-aligned center pixel coordinates from the initial time using the \code{solar\_rotate\_coordinate()} routine from \code{Sunpy}.
 
 \section{Analysis}\label{sec:analysis}
-\subsection{Overview}
+\subsection{Target Overview}
 To get a baseline qualitative understanding of how the active area evolved leading up to our primary observations we applied the segmentation and feature tracking algorithms described in \citet{2012Tarr} to the $\approx330\times250\arcsec{}$ cutout of HMI data between 2017-03-19 00:00 and 2017-03-21 23:46UT.
@@
 Finally, we note that immediately preceding our coordinated observations the parasitic positive polarity region of the bipole began an extended cycle of combined fragmentation and cancellation with the negative polarity of the bipole.
-This activity continued throughout our observations and likely drives some of the dynamics we observe.
+All of the processes describe above at the photospheric level likely drive both wave activity and continual reconnection higher in the atmosphere, resulting in the transient brightenings we describe below.
 
@@
 \label{sec:linewidth}
-We characterized the spectral profile of \halpha{} at every spatial and temporal point of the IBIS data.
-Figure \ref{fig:linefitexample} shows a typical example of the spectral data (green crosses), including the Telluric oxygen line $\approx1.4\AA{}$ reward of the \halpha{} line center.
+We characterized the spectral profile of \halpha{} at every spatial and temporal point of the IBIS data series.
+Figure \ref{fig:linefitexample} shows a typical example of the spectral data (green crosses), including the Telluric oxygen line $\approx1.4\AA{}$ redward of the \halpha{} line center, pulled from a single pixel.
 Fitting the spectral line serves dual purposes.
 First, as stated above in \secref{sec:almaalign} and reported on by \citet{2019Molnar}, the \halpha{} linewidth is extremely useful for aligning the ALMA Band 3 data; we discuss this at length in the following subsections.
-Second, the fitting produces several interesting plasma diagnostics of its own, including Doppler shifts and opacity fluctuations.
+Second, the fitting produces several interesting plasma diagnostics of its own, including Doppler shifts and opacity fluctuations, which will be discussed in later publications.
 
-Our characterization followed the method of \citet{2009Cauzzi}.
+Our spectral characterization followed the method of \citet{2009Cauzzi}.
 First, we created a smooth model, $\hfit[\lambda]$ of the normalized spectra\footnote{Spectra at each spatial pixel at a given time were normalized to the intensity of the first measured wavelength position averaged over the central $600\times600$ pixels.
@@
 
-We have verified the correlation between \halpha{} line widths and ALMA Band-3 brightness temperature, as reported by \citet{2019Molnar}.
-\figref{fig:almaibis} shows an example, while an animation spanning the duration of the ALMA observations is available in the supplementary online material.
+\subsection{Comparison of \halpha{} linewidth to ALMA brightness temperature}
 
@@
 Contours of the ALMA brightness temperature are overlaid on both panels.
-The white dashed circle shows the effective extent of ALMA's FOV.
-An animation of this figure is available in the supplementary online material.}
+The white dashed circle shows the effective extent of ALMA's FOV.}
     \label{fig:almaibis}
@@
 
+The left panel of \figref{fig:almaibis} shows a spatial map of the \halpha{} linewidth at 15:45UT and the right panel shows the ALMA brightness temperature map from the same time.
+The dashed circles in both panels show the approximate ALMA reconstruction FOV of $\sim60\arcsec{}$.
+The contours in both panels are of the ALMA brightness temperature and clearly show the good correspondence between the \halpha{} line width and the ALMA brightness temperature.
+It is also clear that the correspondence extends somewhat outside of the ALMA effective FOV before fading into the background noise level; this is as expected.
+We have therefore verified the correlation between \halpha{} line widths and ALMA Band-3 brightness temperature, as reported by \citet{2019Molnar}.
+An animation of \figref{fig:almaibis} shows good correlation over the entire 60mins of cotemporal observation, but full temporal analysis is outside the scope of the present discussion.
+
 \citet{2019Molnar} synthesized the radiative emission from a range of model atmospheres, representative of quiet-Sun to strong plage conditions, using the RH code \citep{2001Uitenbroek}.  
 Those results suggest that the broadening of \halpha{} as the chromospheric temperature rises is primarily an opacity effect due to an enhanced number density of H atoms in the $n=2$ quantum state, as opposed to broadening by thermal effects.
-They explained this behavior, extensively referencing \citet{2012Leenaarts}, as follows \saj{colon?}.
-The \halpha{} source function is nearly uniform throughout the chromosphere.
+They explained this behavior, extensively referencing \citet{2012Leenaarts}, as follows.  The \halpha{} source function is nearly uniform throughout the chromosphere.  
 This feature gives \halpha{} its characteristic flat bottom, with fairly uniform intensity in wavelength moving away from line center, until a wavelength is reached at which the source function becomes sensitive to the photosphere, giving rise the the steep line wings.
@@
 We do not expect this break down to occur for the region of enhanced network we have targeted in this data set, with the result that we find good correspondence between the \halpha{} line width and ALMA brightness temperature throughout our observations.
-\subsection{Interpretation of \halpha{} Doppler Shifts}
 
-The above argument explains the correlation between high brightness temperature ALMA Band 3 data and enhanced \halpha{} line widths, and the relation of both to enhanced photospheric magnetic concentrations.
-It also shows how broader linewidths and greater brightness temperatures correspond to greater heights in the solar atmosphere, and how the line formation affects our understanding of the plasma properties.
-The measured doppler velocities for regions with narrow linewidths should be systematically lower than doppler velocities from regions with greater linewidths.
-The narrower lines form over a broad range of heights, allowing for effective canceling of coherent doppler signals, while the broader lines form over a narrower range of heights, so the doppler signal better represents coherent mass motions from localized regions.
+The main result of this analysis is that we have verified the correspondence found by \citet{2019Molnar}.
+Further, we have done so for a region of only slight enhanced network, rather than for an area of strong, active region plage.
+If the radiative modeling described above is correct then we would expect stronger correlation of temporal dynamics in the hotter-ALMA/broader-\halpha{} than in the cooler-ALMA/narrower-\halpha{} regions.
+Details of that temporal analysis will be presented in a forthcoming paper.
 
-My by-eye correlation between the doppler maps and the line-width maps seems to support this, but I haven’t done anything further with it.
-\latcomment{see email exchange 2020-02-20 between Tarr/Reardon/Uitenbroc/Momchil}.
+\subsection{Transient brightening detections}
 
-Also, I find a nearly gaussian distribution of doppler shifts of order $\pm0.05$\AA{} around the peak (FWHM), compared to line widths ranging from 0.9 to 1.3\AA{}.
-The width distribution is odd, but I could see it as two very roughly peaked gaussians, centered at 1 and 1.2\AA{}, both with FWHM $\pm0.05$\AA{}.
-That also makes for a consistent picture.
+In this data series, over 30 individual brightenings were detected in just XRT using the techniques of \citet{2014KobelskiEA_XRTTBs}.
+Most of the detections were found within overlapping fields of view (spatially and temporally) with the other instruments.
+A few brightenings overlap with EIS and IRIS slits, but we have not yet interpreted these specific features.
+These brightenings will be discussed in future work, with analysis that will be able to better detect and connect the transient activity and to determine whether there is increased and co-located chromospheric activity before and/or after these events.
+For now, we focus on a single example dynamic event, which was readily observed in most of the imaging data.
 
-We now turn to analyzing the temporal variations of these radiative diagnostics.
+\subsection{Transient brightening at 16:10-16:30}
+We find evidence of a transient event in multiple data channels that appears to show energy transfer between the chromosphere to the corona and back along two different paths, between 16:10 and 16:30UT.
+\figref{fig:coordination2} shows nine of our data channels near the end of the event.
+
+The event starts as a strong, elongated dimming the \halpha{} blue wing, see especially the $-0.089\unit{nm}$ channel.
+The dimming progresses roughly from SE to NW along the filament channel between the polarities of the bipole.
+The ALMA data show cospatial enhanced temperatures during this time. A subset of these images is shown in Figure~\ref{fig:subset}.
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figures/IBISsubset_img0106.png}
+    \caption{Subimage of the brightening event.}
+    \label{fig:subset}
+\end{figure*}
+
+Small scale sympathetic event.
+
+After brightening in ALMA the dynamic event then becomes visible in the hotter and higher data channels, especially AIA 304\AA{} and 193\AA{}, followed by XRT. 
+The closeness with which the AIA light curves track each other suggests an initial brightening in the lower temperature component of the 193\AA{} which is then followed by brightening due to plasma heating the hotter component \citep[see details of the two 193\AA{} components shown in Figure~11 of ]{2012Boerner}, and followed in turn by the brightening observed with XRT.
+This strongly suggest that we are observing a direct heating event of the loop. 
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figures/evt01_lc_bb.eps}
+    \caption{Sub-regions  shown in Figure~\ref{fig:lightcurves}.
+The bounding boxes were chosen from the AIA 304\AA image, and made wide enough to cover any lingering instrumental drifts and variations between wavelengths.
+The reference time is chosen to highlight the coronal counterpart, so occurs after the peak ALMA brightening.
+The XRT image has been reverse scaled to improve visibility.
+The wishbone feature is the prominent region of interest for this example.
+The brightening follows much of the same shape in all upper chromospheric and coronal wavelengths.}
+    \label{fig:wishbonezoom}
+\end{figure*}
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figures/evt01_lc_v2.eps}
+    \caption{Light curves from sub-regions (will update figure~\ref{fig:subset} to outline) shown in Figure~\ref{fig:subset}.
+Here you can see that the brightening is initiated in the low chromosphere as shown with ALMA.
+The EUV data then brightens next, with the AIA 304\AA brightening slightly before the AIA 193\AA, though these brightenings follow much of the same shape.}
+    \label{fig:lightcurves}
+\end{figure}
+
+Each the brightenings in the EUV and X-ray data follow the same progression from SE to NW along the filament channel, just as in the IBIS and ALMA data series.
+The hotter channels then show a second loop brightening that partially overlaps the first but then extends southward from the negative concentration of the bipole towards a small flux concentration near the Southern edge of the ALMA field of view.
+Finally we see a co-spatial and -temporal dimming in the \halpha{} blue wing and enhanced temperatures in ALMA at the Southern terminus of the secondary loop. 
+The XRT data allow us to see the brightest thermal features in the region, which can be seen in the lower right panel of Figure~\ref{fig:coordination2} and in Figure~\ref{fig:wishbonezoom}. 
+One of the most apparent features in the region during this time period, is the brightening along a new loop channel in the southern portion of the field of view.
+This wishbone like loop feature is readily seen and outlined in the upper chromospheric and coronal channels and is shown Figure~\ref{fig:wishbonezoom}.
+Lightcurves of the bounded region of the wishbone feature are shown in Figure~\ref{lightcurves}. 
+The light curves clearly show the pre-brightening in the low chromosphere with ALMA, followed by the hotter channels.
+Similar to the methods discussed in \citet{2014KobelskiEA_XRTTBs} and \citet{2014KobelskiMcKenzie_HiC}, we have searched for small, dynamic brightenings in the data.
 
 \section{Conclusions}\label{sec:conclusion}
-The end
+We have presented an extensive coordinated data set that includes data series from multiple facilities and, in some cases, multiple instruments from each facility.
+We describe the calibration and self-alignment of each data series and the coalignment of all data series within the data set.
+The fully calibrated and aligned data are publicly available at \url{https://share.nso.edu/shared/dkist/ltarr/kolsch/}.
+The coordination was keyed to our ALMA Cycle 4 observations which targeted a bipolar region of enhanced network for approximately one hour starting at 14:42 UT on 2017-03-21.
+The target was situated close to disk center, approximately $(-70,-50\arcsec{})$ at the center of the ALMA data series. 
+The other data series cover a variety of fields-of-view, start times, and durations.
 
-\section{Noted dynamic events}
-We see numerous propagating disurbances in the \halpha{} linewidth.
+We found that the spatial areas of broadest line width of the \halpha{} spectral line as observed by IBIS were cospatial to the hottest regions as measured by ALMA Band 3 $(\gtrsim 7500\unit{K})$.
+This correspondence held for the entire duration of the ALMA observations.
+This result extends the findings of \citet{2019Molnar}, who analyzed a single time frame of active region plage, to quiescent solar regions and extended time durations.
+A future work will discuss the statistics of temporal dynamics between the two data series.
 
-ALMA shows lots of oscillations, difficult to say if these are impulsive or not (ALMA is both low resolution and radiatively thick).
-
-Many brightenings in XRT. A few can be connected through to IBIS.
-\begin{description}
-    {\item[NuSTAR]-potential events}
-    \begin{itemize}
-        {\item 19:04}
-        {\item 19:30}
-    \end{itemize}
-    {\item[IBIS]-potential events}
-        \begin{itemize}
-            {\item 14:53-14:58: propagating linewidth enhancement (-75,-40), (scan 158 )}
-            {\item 15:15-15:18: likely bogus, I think data is too poor to tell}
-            {\item 15:589-16:02: inflow to center of region (-55,-55).  See $d\lambda$ = 0.0320$\rightarrow$0.069}
-            {\item 16:20-16:22: propagating wavetrain outward from center around (-50,-40).
-See running difference $d\lambda$ = -0.089, -0.075,0.057, 0.069.
-Shows up especially well blue-wing intensity images at $d\lambda = -0.1, -0.089\unit{nm}$.
-May start as early as 16:10?
-Go from 16:10-16:30}
-        \end{itemize}
-    {\item[XRT] blah}
-    {\item[ALMA] blah}
-    {\item[IRIS] blah}
-\end{description}
-
-The 16:10 to 16:30 event appears to show energy transfer between the chromosphere to the corona and back along two different paths.
-The even starts as a strong dimming the \halpha{} blue wing, see especially the $-0.089\unit{nm}$ channel.  
-The dimming progresses roughly from SE to NW along the filament channel between the polarities of the bipole.
-The ALMA data show cospatial enhanced temperatures during this time.
-The dynamic event then becomes visible the hotter and higher data channels, especially AIA 304\AA{} and 193\AA{} followed by XRT.
-In all of these the brightenings again progress from SE to NW along the filament channel.
-The hotter channels then show a second loop brightening that partially overlaps the first but then extends southward from the negative concentration of the bipole towards a small flux concentration near the edge of the ALMA field of view.
-Finally we see a co-spatial and -temporal dimming in the \halpha{} blue wing and enhanced temperatures in ALMA at the southern terminus of the secondary loop.
+Preliminary analysis found multiple transient brightenings throughout the data set, some of which span multiple data series.
+We highlight one particularly well observed example lasting approximately 20 minutes starting at 16:10 UT.
+Lightcurves of the event show a clear transition from lower to higher temperature data series, starting in the chromospheric ALMA data ($\sim7000\unit{K}$) and progressing up to our hottest observed thermal series in \textsl{Hinode}/XRT ($\sim3\unit{MK}$).
+Spatially, the event shows a propagation first along a filamentary feature above the central polarity inversion line of the bipole and then a secondary Y-shaped extension to another network concentration approximately $15\arcsec$ to the South.
+\ark{potentially also add SALSA info}.
+What this data demonstrates is that these small scale events with large wavelength coverage are interesting, and cover some of the same dynamic features as seen in larger events.
+We hope the community is able to further utilize this small but robust data set.
 
 \acknowledgments
+%ALMA
+This paper makes use of the following ALMA data: ADS/JAO.ALMA$\#$2016.1.00788.S.
+ALMA is a partnership of ESO (representing its member states), NSF (USA) and NINS (Japan), together with NRC (Canada), MOST and ASIAA (Taiwan), and KASI (Republic of Korea), in cooperation with the Republic of Chile.
+The Joint ALMA Observatory is operated by ESO, AUI/NRAO and NAOJ.
+
 %DST
-The National Solar Observatory (NSO) is operated by the Association of Universities for Research in Astronomy, Inc. (AURA), under cooperative agreement with the National Science Foundation.  
+Data in this publication were obtained with the Dunn Solar Telescope of the National Solar Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.
+
 %IRIS
 IRIS is a NASA small explorer mission developed and operated by LMSAL with mission operations executed at NASA Ames Research center and major contributions to downlink communications funded by ESA and the Norwegian Space Center.
+The authors thank K.~Reardon for help calibrating the IBIS data.
+
 %Hinode SOT/SP done in text
+Hinode is a Japanese mission developed and launched by ISAS/JAXA, collaborating with NAOJ as a domestic partner, NASA and STFC (UK) as international partners.
+Scientific operation of the Hinode mission is conducted by the Hinode science team organized at ISAS/JAXA.
+This team mainly consists of scientists from institutes in the partner countries.
+Support for the post-launch operation is provided by JAXA and NAOJ(Japan), STFC (U.K.), NASA, ESA, and NSC (Norway).
 
-%ALMA
-
+This research has made use of NASA’s Astrophysics Data System.
 %% To help institutions obtain information on the effectiveness of their 
@@
 \vspace{5mm}
-\facilities{ALMA, Dunn(FIRS, IBIS), IRIS, SDO(AIA, HMI)}
+\facilities{ALMA, Dunn(FIRS, IBIS), IRIS, SDO(AIA, HMI), Hinode(EIS, SOT, XRT)}
 
@@
 
-\software{astropy \citep{2013astropy,2018astropy} SHOULD INCLUDE: SUNPY, NUMPY, ADS, SSW}
+\software{\code{astropy} \citep{2013astropy,2018astropy}, \code{sunpy} \citep{2020sunpy}, \code{numpy} \citep{2020Harris}, \code{sswidl} \citep{1998FreelandHandy_SSW}}
 

### 2021-12-23 old_notes.tex
update Dec 23 2021

\section{Noted dynamic events}
We see numerous propagating disurbances in the \halpha{} linewidth.

ALMA shows lots of oscillations, difficult to say if these are impulsive or not (ALMA is both low resolution and radiatively thick).

Many brightenings in XRT. A few can be connected through to IBIS.
\begin{description}
    {\item[NuSTAR]-potential events}
    \begin{itemize}
        {\item 19:04}
        {\item 19:30}
    \end{itemize}
    {\item[IBIS]-potential events}
        \begin{itemize}
            {\item 14:53-14:58: propagating linewidth enhancement (-75,-40), (scan 158 )}
            {\item 15:15-15:18: likely bogus, I think data is too poor to tell}
            {\item 15:589-16:02: inflow to center of region (-55,-55).  See $d\lambda$ = 0.0320$\rightarrow$0.069}
            {\item 16:20-16:22: propagating wavetrain outward from center around (-50,-40).  See running difference $d\lambda$ = -0.089, -0.075,0.057, 0.069.  Shows up especially well blue-wing intensity images at $d\lambda = -0.1, -0.089\unit{nm}$.  May start as early as 16:10?  Go from 16:10-16:30}
        \end{itemize}
    {\item[XRT] blah}
    {\item[ALMA] blah}
    {\item[IRIS] blah}
\end{description}
